---
title: "AB"
author: "Jacqueline Erens"
date: "4/11/2022"
output:
  pdf_document: NULL
editor_options: 
  markdown: 
    wrap: 100
classoption: landscape, a3paper
fontsize: 7pt
geometry: margin=0.2cm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

table function
```{r}
make_nice_table <- function(m, file_name){
  stats.table <- as.data.frame(summary(m)$coefficients)
  stats.table <- cbind(row.names(stats.table), stats.table)
  names(stats.table) <- c("Term", "B", "SE", "df", "t", "p")
  n_terms <-length(summary(m)$coefficients[,1])
  stats.table <- nice_table(stats.table)
  stats.table<- stats.table %>%
    align(i = 1:n_terms, j = 1, align = "left", part = "body") %>%
    align(j = 1, align = "left", part = "header") %>%
    set_table_properties(width = 1, layout = "autofit") %>%
    autofit(add_w = -1, add_h = 0, part = c("body", "header"), unit = "in") %>%
    bold(bold = TRUE, part = "header") %>%
    fontsize(size = 12, part = "body") %>%
    fontsize(size = 12, part = "header") %>%
    italic(italic = FALSE, part = "header")
  print(stats.table)
  save_as_docx(stats.table, path = file_name)

}

stats.table <- as.data.frame(LookupTable)
n_terms <- nrow(LookupTable)
stats.table <- nice_table(stats.table)
stats.table<- stats.table %>%
  align(i = 1:n_terms, j = 1, align = "left", part = "body") %>%
  align(j = 1, align = "left", part = "header") %>%
  set_table_properties(width = 1, layout = "autofit") %>%
  autofit(add_w = -1, add_h = 0, part = c("body", "header"), unit = "in") %>%
  bold(bold = TRUE, part = "header") %>%
  fontsize(size = 12, part = "body") %>%
  fontsize(size = 12, part = "header") %>%
  italic(italic = FALSE, part = "header")
print(stats.table)
save_as_docx(stats.table, path = "LookupTable.docx")

```

Load in and process data, exclude participants who did not meet criteria

```{r}
library(lme4)
library(ggplot2)
library(dplyr)
library(brms)
library(sjPlot)
library(sjmisc)
library(rempsyc)
#lme4::glmer() #gives you easy way to see parameters 
setwd("~/Desktop/projects/FYP/")
DataAB <- read.csv(file = 'AB_Data_51_done_v2.csv')

Data_useableAB <- DataAB %>% filter(DataAB$Useable_Labels == 1 & DataAB$Useable_Timing == 1)
Data_useableAB <- Data_useableAB %>% 
  filter(is.na(Data_useableAB$DUR_NP1) == FALSE & is.na(Data_useableAB$DUR_NP2) == FALSE & is.na(Data_useableAB$DUR_NP3) == FALSE & is.na(Data_useableAB$DUR_AND) == FALSE)
Data_useableAB$ParticipantNum <- as.factor(Data_useableAB$ParticipantNum)
Data_useableAB$Condition <- as.factor(Data_useableAB$Condition)
Data_useableAB$ListNum <- as.factor(Data_useableAB$ListNum)
           
EXCLUDE_AB <- c()                          
useables_AB <- c()
lists_vec <- c()
#participant 1 had 0 useable responses and thus was removed at the stop on line 20 - so start with participant 2 but add 1 to the number of participants it counts
for(i in 1:length(unique(DataAB$ParticipantNum))){
  print(i)
  useables_AB<-append(useables_AB,length(which(Data_useableAB$ParticipantNum == i)))
  #cat("participant", i, ":", length(which(Data_useableAB$ParticipantNum == i)), "useable responses \n")
  cat("participant", i, ": List", unique(Data_useableAB$ListNum[which(Data_useableAB$ParticipantNum == i)]), "\n")
  if(length(which(Data_useableAB$ParticipantNum == i)) < 10){
    cat("participant", i, ":", length(which(Data_useableAB$ParticipantNum == i)), "useable responses, excluded \n")
    EXCLUDE_AB <- append(EXCLUDE_AB, i)
  }
  if(length(which(Data_useableAB$ParticipantNum == i)) >= 10){
    cat("participant", i, ":", length(which(Data_useableAB$ParticipantNum == i)), "useable responses \n")
    lists_vec <- append(lists_vec, unique(Data_useableAB$ListNum[which(Data_useableAB$ParticipantNum == i)]))
  }
  
}
print(EXCLUDE_AB) 
#1  6 19 20 40 50
#This is also the reason they all have a 1 in the "other reasons to exclude column"
Data_useableAB <- Data_useableAB %>% filter(Data_useableAB$ParticipantNum %in% EXCLUDE_AB == FALSE) 

print(length(lists_vec[which(lists_vec == 1)]))
print(length(lists_vec[which(lists_vec == 2)]))
print(length(lists_vec[which(lists_vec == 3)]))
print(length(lists_vec[which(lists_vec == 4)]))
print(length(lists_vec[which(lists_vec == 5)]))
print(length(lists_vec[which(lists_vec == 6)]))
print(length(lists_vec[which(lists_vec == 7)]))
print(length(lists_vec[which(lists_vec == 8)]))

cat("So far, number of participants = ",sum(length(lists_vec[which(lists_vec == 1)]), length(lists_vec[which(lists_vec == 2)]), length(lists_vec[which(lists_vec == 3)]), length(lists_vec[which(lists_vec == 4)]),length(lists_vec[which(lists_vec == 5)]),length(lists_vec[which(lists_vec == 6)]),length(lists_vec[which(lists_vec == 7)]),length(lists_vec[which(lists_vec == 8)])))

hist(useables_AB, breaks = 20, xlim = c(0,20))
hist(useables_AB[which(useables_AB > 10)], breaks = 10, xlim = c(10,20))
nrow(Data_useableAB)
1-nrow(Data_useableAB)/(45*20)
```

Pairing up data with cos, cooc statistics because I didn't trust myself to copy paste accurately

```{r}
A2 <- c("rope_farmer_corn","shrimp_fairy_surfer","book_swimmer_lifeguard","bed_gymnast_ballerina","fork_singer_drummer","comb_astronaut_bowl","door_chef_mime","sponge_nun_church","sun_magician_viking","rope_farmer_ninja","comb_astronaut_moon","shrimp_fairy_angel","bed_gymnast_baseball","sponge_nun_cowboy","fork_singer_umbrella","book_swimmer_sock","sun_magician_wizard","door_chef_waiter","tie_sheriff_fire","shrimp_fairy_ring","bed_gymnast_janitor","tie_sheriff_detective","comb_astronaut_pilot","sun_magician_hat","book_swimmer_hippie","rope_farmer_bell","sponge_nun_football","door_chef_sushi","fork_singer_scientist","tie_sheriff_monster","sponge_nun_monk","rope_farmer_fisherman","sun_magician_watch","fork_singer_microphone","bed_gymnast_medal","comb_astronaut_plumber","book_swimmer_goggles","shrimp_fairy_trophy","door_chef_pillow","rose_witch_spoon","glove_princess_hammer","fan_doctor_heart","knife_sailor_clown","car_skier_mountain","tooth_painter_sculptor","scarf_vampire_zombie","jar_king_judge","sink_bride_axe","cloud_dragon_sword","sink_bride_groom","fan_doctor_iron","jar_king_crown","scarf_vampire_maid","tooth_painter_robot","car_skier_table","cloud_dragon_apple","glove_princess_mermaid","knife_sailor_boat","rose_witch_ghost","cloud_dragon_knight","car_skier_snowboarder","knife_sailor_tree","rose_witch_coach","sink_bride_genie","fan_doctor_nurse","tooth_painter_vase","glove_princess_alien","scarf_vampire_bat","glove_princess_dress","rose_witch_broom","knife_sailor_pirate","car_skier_cheerleader","cloud_dragon_golfer","sink_bride_cake","jar_king_queen","scarf_vampire_clock","fan_doctor_boxer","tooth_painter_kite","tie_sheriff_box","jar_king_key")
length(unique(A2))==80     

flipped<- c("glove_hammer_princess","rose_spoon_witch","cloud_sword_dragon","fan_heart_doctor","sink_axe_bride","knife_clown_sailor","scarf_zombie_vampire","car_mountain_skier","jar_judge_king","fan_boxer_doctor","sink_cake_bride","scarf_clock_vampire","rose_broom_witch","tooth_kite_painter","car_cheerleader_skier","cloud_golfer_dragon","knife_pirate_sailor","jar_queen_king","glove_dress_princess","tooth_robot_painter","knife_boat_sailor","fan_iron_doctor","jar_crown_king","rose_ghost_witch","scarf_maid_vampire","cloud_apple_dragon","glove_mermaid_princess","sink_groom_bride","car_table_skier","jar_key_king","scarf_bat_vampire","glove_alien_princess","sink_genie_bride","knife_tree_sailor","rose_coach_witch","tooth_vase_painter","cloud_knight_dragon","fan_nurse_doctor","car_snowboarder_skier","book_lifeguard_swimmer","door_mime_chef","bed_ballerina_gymnast","fork_drummer_singer","comb_bowl_astronaut","shrimp_surfer_fairy","rope_corn_farmer","sponge_church_nun","sun_viking_magician","tie_box_sheriff","sponge_football_nun","sun_hat_magician","bed_janitor_gymnast","shrimp_ring_fairy","rope_bell_farmer","book_hippie_swimmer","door_sushi_chef","fork_scientist_singer","tie_detective_sheriff","comb_pilot_astronaut","door_pillow_chef","comb_plumber_astronaut","bed_medal_gymnast","sun_watch_magician","sponge_monk_nun","tie_monster_sheriff","book_goggles_swimmer","rope_fisherman_farmer","fork_microphone_singer","shrimp_trophy_fairy","sun_wizard_magician","book_sock_swimmer","shrimp_angel_fairy","door_waiter_chef","fork_umbrella_singer","comb_moon_astronaut","tie_fire_sheriff","rope_ninja_farmer","sponge_cowboy_nun","bed_baseball_gymnast","tooth_sculptor_painter")
length(unique(flipped))==80


LookupTable <- read.csv("~/Desktop/projects/FYP/NLP_Lookup_Table.csv")

freq_A_vecAB <- c()
freq_2_vecAB <- c()

cooc_vecAB <- c()
cos_people_vecAB <- c()
PMI_vecAB <- c()

nsyl_vec_P2 <- c()
nsyl_vec_P3 <- c()

NA_1_vec <- c()
NA_2_vec <- c()

item_ordering_vec <- c()

condsAB <- c("RP", "RI", "UI", "UP")

RIcAB <- 0
RPcAB <- 0
UIcAB <- 0
UPcAB <- 0

RIgAB <- length(which(Data_useableAB$Condition == "RI"))
RPgAB <- length(which(Data_useableAB$Condition == "RP"))
UIgAB <- length(which(Data_useableAB$Condition == "UI"))
UPgAB <- length(which(Data_useableAB$Condition == "UP"))

for(i in 1:nrow(Data_useableAB)){
  row_to_useAB <- which(LookupTable$Anchor == Data_useableAB$Anchor[i]) #get the row with the info for the specific stimuli item
  freq_A_vecAB <- append(freq_A_vecAB, LookupTable[which(LookupTable$Anchor == Data_useableAB$Anchor[i]),13])
  item_ordering_vec <- append(item_ordering_vec, if_else(Data_useableAB[i,5] %in% A2, .5,-.5)) #handles whether items ordered A-2 or 2-A
  
  if(Data_useableAB[i,5] %in% A2 == TRUE){
    nsyl_vec_P2 <- append(nsyl_vec_P2,LookupTable[row_to_useAB,22]) #if the anchor comes first, add the n_syl for the anchor to the vector for p2
    NA_1_vec <- append(NA_1_vec,LookupTable[row_to_useAB,27]) #and add the name agreement for anchor to the vector for the first item (in bottom row) name agreement
  }else{
    nsyl_vec_P3 <- append(nsyl_vec_P3,LookupTable[row_to_useAB,22])
    NA_2_vec <- append(NA_2_vec,LookupTable[row_to_useAB,27]) 
    } #if the anchor comes second, add the n_syl for the anchor to the vector for p3 - can use if-else because anchor always present in item set

  if (Data_useableAB$Condition[i]=="RP") {
    PMI_vecAB <- append(PMI_vecAB, LookupTable[row_to_useAB, 18])
    cooc_vecAB <- append(cooc_vecAB, LookupTable[row_to_useAB, 8])
    cos_people_vecAB <- append(cos_people_vecAB, LookupTable[row_to_useAB, 6])
    freq_2_vecAB <- append(freq_2_vecAB, LookupTable[row_to_useAB, 14])
    RPcAB <- RPcAB + 1
    if(Data_useableAB[i,5] %in% A2 == TRUE){
      #if the anchor comes first, add the n_syl for the anchor to the vector
      nsyl_vec_P3 <- append(nsyl_vec_P3,LookupTable[row_to_useAB,23])
      NA_2_vec <- append(NA_2_vec,LookupTable[row_to_useAB,28]) }
    else{nsyl_vec_P2 <- append(nsyl_vec_P2,LookupTable[row_to_useAB,23])
    NA_1_vec <- append(NA_1_vec,LookupTable[row_to_useAB,28])}
    
    } else if (Data_useableAB$Condition[i]=="RI") {
    PMI_vecAB <- append(PMI_vecAB, LookupTable[row_to_useAB, 20])
    cooc_vecAB <- append(cooc_vecAB, LookupTable[row_to_useAB, 9])
    freq_2_vecAB <- append(freq_2_vecAB, LookupTable[row_to_useAB, 16])
    RIcAB <- RIcAB + 1

    cos_people_vecAB <- append(cos_people_vecAB, NA)
    if(Data_useableAB[i,5] %in% A2 == TRUE){
      #if the anchor comes first, add the n_syl for the anchor to the vector
      nsyl_vec_P3 <- append(nsyl_vec_P3,LookupTable[row_to_useAB,24]) 
      NA_2_vec <- append(NA_2_vec,LookupTable[row_to_useAB,30])}
    else{nsyl_vec_P2 <- append(nsyl_vec_P2,LookupTable[row_to_useAB,24])
    NA_1_vec <- append(NA_1_vec,LookupTable[row_to_useAB,30])}
    
    } else if  (Data_useableAB$Condition[i]=="UP") {
    PMI_vecAB <- append(PMI_vecAB, LookupTable[row_to_useAB, 19])
    cooc_vecAB <- append(cooc_vecAB, LookupTable[row_to_useAB, 10])
    freq_2_vecAB <- append(freq_2_vecAB, LookupTable[row_to_useAB, 15])
    cos_people_vecAB <- append(cos_people_vecAB, LookupTable[row_to_useAB, 7])

    UPcAB <- UPcAB + 1
    if(Data_useableAB[i,5] %in% A2 == TRUE){
      #if the anchor comes first, add the n_syl for the anchor to the vector
      nsyl_vec_P3 <- append(nsyl_vec_P3,LookupTable[row_to_useAB,25]) 
      NA_2_vec <- append(NA_2_vec,LookupTable[row_to_useAB,29])}
    else{nsyl_vec_P2 <- append(nsyl_vec_P2,LookupTable[row_to_useAB,25])
    NA_1_vec <- append(NA_1_vec,LookupTable[row_to_useAB,29])}

    } else if(Data_useableAB$Condition[i]=="UI") {
    PMI_vecAB <- append(PMI_vecAB, LookupTable[row_to_useAB, 21])
    cooc_vecAB <- append(cooc_vecAB, LookupTable[row_to_useAB, 11])
    freq_2_vecAB <- append(freq_2_vecAB, LookupTable[row_to_useAB, 17])
    UIcAB <- UIcAB + 1
    cos_people_vecAB <- append(cos_people_vecAB, NA)
    if(Data_useableAB[i,5] %in% A2 == TRUE){
      #if the anchor comes first, add the n_syl for the anchor to the vector
      nsyl_vec_P3 <- append(nsyl_vec_P3,LookupTable[row_to_useAB,26]) 
      NA_2_vec <- append(NA_2_vec,LookupTable[row_to_useAB,31])}
    else{nsyl_vec_P2 <- append(nsyl_vec_P2,LookupTable[row_to_useAB,26])
    NA_1_vec <- append(NA_1_vec,LookupTable[row_to_useAB,31])}
    
    }else{
      print("ran else")
    }
}

RIcAB == RIgAB
RPcAB == RPgAB
UIcAB == UIgAB
UPcAB == UPgAB

length(unique(Data_useableAB$SecondThing))
length(freq_A_vecAB)
nrow(Data_useableAB)

length(freq_A_vecAB)
length(freq_2_vecAB)
length(cooc_vecAB)
length(PMI_vecAB)
length(unique(Data_useableAB$Anchor))
#Put in data for frequencies, co-occurrences, PMI, for all items in dataframe
Data_useableAB$AnchorFreq <- freq_A_vecAB
Data_useableAB$SecondFreq <- freq_2_vecAB
Data_useableAB$Cooc <- cooc_vecAB
Data_useableAB$PMI <- PMI_vecAB
Data_useableAB$Nsyl_P2 <- nsyl_vec_P2
Data_useableAB$Nsyl_P3 <- nsyl_vec_P3
Data_useableAB$item_order <- item_ordering_vec
Data_useableAB$Cos <- cos_people_vecAB
Data_useableAB$NA1 <- NA_1_vec
Data_useableAB$NA2 <- NA_2_vec
```

Some basic data wrangling/subsetting by conditions, all centering/scaling stuff

```{r}
Data_useable_with_animacyAB <- Data_useableAB %>% mutate(Animate = ifelse((Data_useableAB$Condition == "RP" | Data_useableAB$Condition == "UP"), .5, -.5)) %>% mutate(related_yes = ifelse((Data_useableAB$Condition == "RP" | Data_useableAB$Condition == "RI"), .5, -.5)) %>% mutate(Freq1 = ifelse(Data_useableAB$item_order == .5, Data_useableAB$AnchorFreq, Data_useableAB$SecondFreq)) %>% mutate(Freq2 = ifelse(Data_useableAB$item_order == -.5,  Data_useableAB$SecondFreq,Data_useableAB$AnchorFreq))

#Lmer recommended rescaling so doing that
Data_useable_with_animacyAB$cPMI <- Data_useable_with_animacyAB$PMI - mean(Data_useable_with_animacyAB$PMI)
Data_useable_with_animacyAB$xcPMI <- Data_useable_with_animacyAB$cPMI /sd(Data_useable_with_animacyAB$PMI)

Data_useable_with_animacyAB$cAnchorFreq <- Data_useable_with_animacyAB$AnchorFreq - mean(Data_useable_with_animacyAB$AnchorFreq)
Data_useable_with_animacyAB$xcAnchorFreq <- Data_useable_with_animacyAB$cAnchorFreq / sd(Data_useable_with_animacyAB$AnchorFreq)

Data_useable_with_animacyAB$cSecondFreq <- Data_useable_with_animacyAB$SecondFreq - mean(Data_useable_with_animacyAB$SecondFreq)
Data_useable_with_animacyAB$xcSecondFreq <- Data_useable_with_animacyAB$cSecondFreq / sd(Data_useable_with_animacyAB$SecondFreq)

Data_useable_with_animacyAB$cFreq1 <- Data_useable_with_animacyAB$Freq1 - mean(Data_useable_with_animacyAB$Freq1)
Data_useable_with_animacyAB$xcFreq1 <- Data_useable_with_animacyAB$cFreq1 / sd(Data_useable_with_animacyAB$Freq1)

Data_useable_with_animacyAB$cFreq2 <- Data_useable_with_animacyAB$Freq2 - mean(Data_useable_with_animacyAB$Freq2)
Data_useable_with_animacyAB$xcFreq2 <- Data_useable_with_animacyAB$cFreq2 / sd(Data_useable_with_animacyAB$Freq2)

Data_useable_with_animacyAB$cNA1 <- Data_useable_with_animacyAB$NA1 - mean(Data_useable_with_animacyAB$NA1)
Data_useable_with_animacyAB$xcNA1 <- Data_useable_with_animacyAB$cNA1 / sd(Data_useable_with_animacyAB$NA1)

Data_useable_with_animacyAB$cNA2 <- Data_useable_with_animacyAB$NA2 - mean(Data_useable_with_animacyAB$NA2)
Data_useable_with_animacyAB$xcNA2 <- Data_useable_with_animacyAB$cNA2 / sd(Data_useable_with_animacyAB$NA2)

Data_useable_with_animacyAB$cCooc <- Data_useable_with_animacyAB$Cooc - mean(Data_useable_with_animacyAB$Cooc)
Data_useable_with_animacyAB$xcCooc <- Data_useable_with_animacyAB$cCooc / sd(Data_useable_with_animacyAB$Cooc)

Data_useable_with_animacyAB$cNsyl_P2 <- Data_useable_with_animacyAB$Nsyl_P2 - mean(Data_useable_with_animacyAB$Nsyl_P2)
Data_useable_with_animacyAB$xcNsyl_P2 <- Data_useable_with_animacyAB$cNsyl_P2 / sd(Data_useable_with_animacyAB$Nsyl_P2)

Data_useable_with_animacyAB$cNsyl_P3 <- Data_useable_with_animacyAB$Nsyl_P3 - mean(Data_useable_with_animacyAB$Nsyl_P3)
Data_useable_with_animacyAB$xcNsyl_P3 <- Data_useable_with_animacyAB$cNsyl_P3 / sd(Data_useable_with_animacyAB$Nsyl_P3)

#Data_useable_with_animacyAB$cCos <- Data_useable_with_animacyAB$Cos - mean(Data_useable_with_animacyAB$Cos)
#Data_useable_with_animacyAB$xcCos <- Data_useable_with_animacyAB$cCos / sd(Data_useable_with_animacyAB$Cos)
```

Subsetting for items and people

```{r}
#Subset for items and people, then code relatedness as 1 and unrelatedness as -1 for both sets, and code actives as 0 and passives as 1
Data_useable_itemsAB <- Data_useable_with_animacyAB %>% filter((Data_useable_with_animacyAB$Condition == "RI"|Data_useable_with_animacyAB$Condition == "UI")) 
Data_useable_itemsAB <- Data_useable_itemsAB %>% mutate(related_yes = ifelse(Data_useable_itemsAB$Condition == "RI", .5, -.5)) 

Data_useable_peopleAB <- Data_useable_with_animacyAB %>% filter((Data_useable_with_animacyAB$Condition == "RP"|Data_useable_with_animacyAB$Condition == "UP")) 
Data_useable_peopleAB <- Data_useable_peopleAB %>% mutate(related_yes = ifelse(Data_useable_peopleAB$Condition == "RP", .5, -.5))
Data_useable_peopleAB$cCos <- Data_useable_peopleAB$Cos - mean(Data_useable_peopleAB$Cos)
Data_useable_peopleAB$xcCos <- Data_useable_peopleAB$cCos / sd(Data_useable_peopleAB$Cos)

mean(Data_useable_with_animacyAB$Nsyl_P3)
mean(Data_useable_with_animacyAB$Nsyl_P2)

Data_useable_peopleAB <- Data_useable_peopleAB %>% mutate(DUR_AND_plus_NP3 = NP3_end-NP2_End)
Data_useable_itemsAB <- Data_useable_itemsAB %>% mutate(DUR_AND_plus_NP3 = NP3_end-NP2_End)
```

Means and sds of condition durations

```{r}
cat("The number of sentences in the entire dataset: ",nrow(Data_useable_with_animacyAB),"\n")
cat("The number of sentences in the people-only dataset: ",nrow(Data_useable_peopleAB),"\n")
cat("The number of sentences in the items-only dataset: ",nrow(Data_useable_itemsAB),"\n")

items_vec <- ifelse(Data_useable_with_animacyAB$Condition == "UP" | Data_useable_with_animacyAB$Condition == "RP", 0, 1)
ppl_vec <- ifelse(Data_useable_with_animacyAB$Condition == "UP" | Data_useable_with_animacyAB$Condition == "RP", 1, 0)

t.test(x = items_vec,y = ppl_vec)


cat("The mean of all data Duration NP1: ",mean(Data_useable_with_animacyAB$DUR_NP1),"The sd of all data Duration NP1: ",sd(Data_useable_with_animacyAB$DUR_NP1),"\n")
cat("The mean of all data Duration NP2: ",mean(Data_useable_with_animacyAB$DUR_NP2),"The sd of all data Duration NP2: ",sd(Data_useable_with_animacyAB$DUR_NP2),"\n")
cat("The mean of all data Duration AND: ",mean(Data_useable_with_animacyAB$DUR_AND),"The sd of all data Duration AND: ",sd(Data_useable_with_animacyAB$DUR_AND),"\n")
cat("The mean of all data Duration NP3: ",mean(Data_useable_with_animacyAB$DUR_NP3),"The sd of all data Duration NP3: ",sd(Data_useable_with_animacyAB$DUR_NP3),"\n")

cat("The mean of people only data Duration NP1: ",mean(Data_useable_peopleAB$DUR_NP1),"The sd of people only data Duration NP1: ",sd(Data_useable_peopleAB$DUR_NP1),"\n")
cat("The mean of people only data Duration NP2: ",mean(Data_useable_peopleAB$DUR_NP2),"The sd of people only data Duration NP2: ",sd(Data_useable_peopleAB$DUR_NP2),"\n")
cat("The mean of people only data Duration AND: ",mean(Data_useable_peopleAB$DUR_AND),"The sd of people only data Duration AND: ",sd(Data_useable_peopleAB$DUR_AND),"\n")
cat("The mean of people only data Duration NP3: ",mean(Data_useable_peopleAB$DUR_NP3),"The sd of people only data Duration NP1: ",sd(Data_useable_peopleAB$DUR_NP3),"\n")

cat("The mean of item only data Duration NP1: ",mean(Data_useable_itemsAB$DUR_NP1),"The sd of item only data Duration NP1: ",sd(Data_useable_itemsAB$DUR_NP1),"\n")
cat("The mean of item only data Duration NP2: ",mean(Data_useable_itemsAB$DUR_NP2),"The sd of item only data Duration NP2: ",sd(Data_useable_itemsAB$DUR_NP2),"\n")
cat("The mean of item only data Duration AND: ",mean(Data_useable_itemsAB$DUR_AND),"The sd of item only data Duration AND: ",sd(Data_useable_itemsAB$DUR_AND),"\n")
cat("The mean of item only data Duration NP3: ",mean(Data_useable_itemsAB$DUR_NP3),"The sd of item only data Duration NP1: ",sd(Data_useable_itemsAB$DUR_NP3),"\n")

hist(Data_useable_with_animacyAB$DUR_NP1,breaks = 100)
hist(Data_useable_with_animacyAB$DUR_NP2,breaks = 100)
hist(Data_useable_with_animacyAB$DUR_AND,breaks = 100)
hist(Data_useable_with_animacyAB$DUR_NP3,breaks = 100)

hist(Data_useable_peopleAB$DUR_NP1,breaks = 100)
hist(Data_useable_peopleAB$DUR_NP2,breaks = 100)
hist(Data_useable_peopleAB$DUR_AND,breaks = 100)
min(Data_useable_peopleAB$DUR_AND)
hist(Data_useable_peopleAB$DUR_NP3,breaks = 100)

hist(Data_useable_itemsAB$DUR_NP1,breaks = 100)
hist(Data_useable_itemsAB$DUR_NP2,breaks = 100)
hist(Data_useable_itemsAB$DUR_AND,breaks = 100)
hist(Data_useable_itemsAB$DUR_NP3,breaks = 100)

hist(log(Data_useable_with_animacyAB$DUR_NP1),breaks = 100)
hist(log(Data_useable_with_animacyAB$DUR_NP2),breaks = 100)
hist(log(Data_useable_with_animacyAB$DUR_AND),breaks = 100)
hist(log(Data_useable_with_animacyAB$DUR_NP3),breaks = 100)

hist(log(Data_useable_peopleAB$DUR_NP1),breaks = 100)
hist(log(Data_useable_peopleAB$DUR_NP2),breaks = 100)
hist(log(Data_useable_peopleAB$DUR_AND),breaks = 100)
hist(log(Data_useable_peopleAB$DUR_NP3),breaks = 100)

hist(log(Data_useable_itemsAB$DUR_NP1),breaks = 100)
hist(log(Data_useable_itemsAB$DUR_NP2),breaks = 100)
hist(log(Data_useable_itemsAB$DUR_AND),breaks = 100)
hist(log(Data_useable_itemsAB$DUR_NP3),breaks = 100)

Data_usable_with_animacyAB_RP <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'RP')
Data_usable_with_animacyAB_RI <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'RI')
Data_usable_with_animacyAB_UP <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'UP')
Data_usable_with_animacyAB_UI <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'UI')

cat("The mean of RP Duration NP1: ",mean(Data_usable_with_animacyAB_RP$DUR_NP1),"The sd of RP Duration NP1: ",sd(Data_usable_with_animacyAB_RP$DUR_NP1),"\n")
cat("The mean of RP Duration NP2: ",mean(Data_usable_with_animacyAB_RP$DUR_NP2),"The sd of RP Duration NP2: ",sd(Data_usable_with_animacyAB_RP$DUR_NP2),"\n")
cat("The mean of RP Duration AND: ",mean(Data_usable_with_animacyAB_RP$DUR_AND),"The sd of RP Duration AND: ",sd(Data_usable_with_animacyAB_RP$DUR_AND),"\n")
cat("The mean of RP Duration NP3: ",mean(Data_usable_with_animacyAB_RP$DUR_NP3),"The sd of RP Duration NP3: ",sd(Data_usable_with_animacyAB_RP$DUR_NP3),"\n")

cat("The mean of UP Duration NP1: ",mean(Data_usable_with_animacyAB_UP$DUR_NP1),"The sd of UP Duration NP1: ",sd(Data_usable_with_animacyAB_UP$DUR_NP1),"\n")
cat("The mean of UP Duration NP2: ",mean(Data_usable_with_animacyAB_UP$DUR_NP2),"The sd of UP Duration NP2: ",sd(Data_usable_with_animacyAB_UP$DUR_NP2),"\n")
cat("The mean of UP Duration AND: ",mean(Data_usable_with_animacyAB_UP$DUR_AND),"The sd of UP Duration AND: ",sd(Data_usable_with_animacyAB_UP$DUR_AND),"\n")
cat("The mean of UP Duration NP3: ",mean(Data_usable_with_animacyAB_UP$DUR_NP3),"The sd of UP Duration NP3: ",sd(Data_usable_with_animacyAB_UP$DUR_NP3),"\n")

cat("The mean of RI Duration NP1: ",mean(Data_usable_with_animacyAB_RI$DUR_NP1),"The sd of RI Duration NP1: ",sd(Data_usable_with_animacyAB_RI$DUR_NP1),"\n")
cat("The mean of RI Duration NP2: ",mean(Data_usable_with_animacyAB_RI$DUR_NP2),"The sd of RI Duration NP2: ",sd(Data_usable_with_animacyAB_RI$DUR_NP2),"\n")
cat("The mean of RI Duration AND: ",mean(Data_usable_with_animacyAB_RI$DUR_AND),"The sd of RI Duration AND: ",sd(Data_usable_with_animacyAB_RI$DUR_AND),"\n")
cat("The mean of RI Duration NP3: ",mean(Data_usable_with_animacyAB_RI$DUR_NP3),"The sd of RI Duration NP3: ",sd(Data_usable_with_animacyAB_RI$DUR_NP3),"\n")

cat("The mean of UI Duration NP1: ",mean(Data_usable_with_animacyAB_UI$DUR_NP1),"The sd of UI Duration NP1: ",sd(Data_usable_with_animacyAB_UI$DUR_NP1),"\n")
cat("The mean of UI Duration NP2: ",mean(Data_usable_with_animacyAB_UI$DUR_NP2),"The sd of UI Duration NP2: ",sd(Data_usable_with_animacyAB_UI$DUR_NP2),"\n")
cat("The mean of UI Duration AND: ",mean(Data_usable_with_animacyAB_UI$DUR_AND),"The sd of UI Duration AND: ",sd(Data_usable_with_animacyAB_UI$DUR_AND),"\n")
cat("The mean of UI Duration NP3: ",mean(Data_usable_with_animacyAB_UI$DUR_NP3),"The sd of UI Duration NP3: ",sd(Data_usable_with_animacyAB_UI$DUR_NP3),"\n")
```

NP1 durations hist

```{r}
par(mfrow=c(2,2)) 
hist(Data_usable_with_animacyAB_RP$DUR_NP1,breaks = 100, main = "RP NP1")
abline(v = mean(Data_usable_with_animacyAB_RP$DUR_NP1)) # 1.799586, 0.6892917
hist(Data_usable_with_animacyAB_UP$DUR_NP1,breaks = 100, main = "UP NP1")
abline(v = mean(Data_usable_with_animacyAB_UP$DUR_NP1)) #1.848721, 0.7671986
hist(Data_usable_with_animacyAB_RI$DUR_NP1,breaks = 100, main = "RI NP1")
abline(v =mean(Data_usable_with_animacyAB_RI$DUR_NP1)) #1.74989, 0.644129
hist(Data_usable_with_animacyAB_UI$DUR_NP1,breaks = 100, main = "UI NP1")
abline(v =mean(Data_usable_with_animacyAB_UI$DUR_NP1)) #1.751337, 0.6967944

t.test(Data_usable_with_animacyAB_RP$DUR_NP1,Data_usable_with_animacyAB_UP$DUR_NP1) #NS
t.test(Data_usable_with_animacyAB_RI$DUR_NP1,Data_usable_with_animacyAB_UI$DUR_NP1) #NS
```

NP2 durations hist

```{r}
par(mfrow=c(2,2)) 
hist(Data_usable_with_animacyAB_RP$DUR_NP2,breaks = 100, main = "RP NP2")
abline(v = mean(Data_usable_with_animacyAB_RP$DUR_NP2)) #0.8946746, 0.4034244
hist(Data_usable_with_animacyAB_UP$DUR_NP2,breaks = 100, main = "UP NP2")
abline(v = mean(Data_usable_with_animacyAB_UP$DUR_NP2)) #0.9034302, 0.4397785
hist(Data_usable_with_animacyAB_RI$DUR_NP2,breaks = 100, main = "RI NP2")
abline(v = mean(Data_usable_with_animacyAB_RI$DUR_NP2)) #0.7835912, 0.3240402
hist(Data_usable_with_animacyAB_UI$DUR_NP2,breaks = 100, main = "UI NP2")
abline(v = mean(Data_usable_with_animacyAB_UI$DUR_NP2)) # 0.8313904, 0.3429884

t.test(Data_usable_with_animacyAB_RP$DUR_NP2,Data_usable_with_animacyAB_UP$DUR_NP2) #NS
t.test(Data_usable_with_animacyAB_RI$DUR_NP2,Data_usable_with_animacyAB_UI$DUR_NP2) #NS
```

AND durations hist

```{r}
par(mfrow=c(2,2)) 
hist(Data_usable_with_animacyAB_RP$DUR_AND,breaks = 100, main = "RP AND")
abline(v = mean(Data_usable_with_animacyAB_RP$DUR_AND)) #0.3525444, 0.3421519
hist(Data_usable_with_animacyAB_UP$DUR_AND,breaks = 100, main = "UP AND")
abline(v = mean(Data_usable_with_animacyAB_UP$DUR_AND)) #0.3676744, 0.3403101
hist(Data_usable_with_animacyAB_RI$DUR_AND,breaks = 100, main = "RI AND")
abline(v = mean(Data_usable_with_animacyAB_RI$DUR_AND)) #0.3226519, 0.2766961
hist(Data_usable_with_animacyAB_UI$DUR_AND,breaks = 100, main = "UI AND")
abline(v = mean(Data_usable_with_animacyAB_UI$DUR_AND)) #0.299893, 0.2532541

t.test(Data_usable_with_animacyAB_RP$DUR_AND,Data_usable_with_animacyAB_UP$DUR_AND) #NS
t.test(Data_usable_with_animacyAB_RI$DUR_AND,Data_usable_with_animacyAB_UI$DUR_AND) #NS
```

NP3 durations hist

```{r}
par(mfrow=c(2,2)) 
hist(Data_usable_with_animacyAB_RP$DUR_NP3,breaks = 100, main = "RP NP3")
abline(v = mean(Data_usable_with_animacyAB_RP$DUR_NP3)) #0.7882249, 0.2654653
hist(Data_usable_with_animacyAB_UP$DUR_NP3,breaks = 100, main = "UP NP3")
abline(v = mean(Data_usable_with_animacyAB_UP$DUR_NP3)) # 0.8959302, 0.4688767
hist(Data_usable_with_animacyAB_RI$DUR_NP3,breaks = 100, main = "RI NP3")
abline(v = mean(Data_usable_with_animacyAB_RI$DUR_NP3)) #0.7849171, 0.3982512
hist(Data_usable_with_animacyAB_UI$DUR_NP3,breaks = 100, main = "UI NP3")
abline(v = mean(Data_usable_with_animacyAB_UI$DUR_NP3)) #0.8534759, 0.5403913

t.test(Data_usable_with_animacyAB_RP$DUR_NP3,Data_usable_with_animacyAB_UP$DUR_NP3) #SIG
t.test(Data_usable_with_animacyAB_RI$DUR_NP3,Data_usable_with_animacyAB_UI$DUR_NP3) #NS
```

basic means, sds, t tests for related vs unrelated in people and items

```{r}
#means for related vs unrelated & some basic t tests
Data_usable_with_animacyAB_RP <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'RP')
Data_usable_with_animacyAB_RI <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'RI')
Data_usable_with_animacyAB_UP <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'UP')
Data_usable_with_animacyAB_UI <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'UI')

Data_usable_with_animacyAB_R <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'RP'|Data_useable_with_animacyAB$Condition == 'RI')
Data_usable_with_animacyAB_U <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'UP'|Data_useable_with_animacyAB$Condition == 'UI')
Data_usable_with_animacyAB_P <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'RP'|Data_useable_with_animacyAB$Condition == 'UP')
Data_usable_with_animacyAB_I <- Data_useable_with_animacyAB %>% filter(Data_useable_with_animacyAB$Condition == 'RI'|Data_useable_with_animacyAB$Condition == 'UI')

#checking duration of first noun phrase stuff
print("Related people vs unrelated people \n")
cat(mean(Data_usable_with_animacyAB_RP$DUR_NP1), sd(Data_usable_with_animacyAB_RP$DUR_NP1), "\n")
cat(mean(Data_usable_with_animacyAB_UP$DUR_NP1), sd(Data_usable_with_animacyAB_UP$DUR_NP1), "\n")

#t-tests for if differences in Duration to start exist b/w related & unrelated people & related & unrelated items
t.test(Data_usable_with_animacyAB_RP$DUR_NP1,Data_usable_with_animacyAB_UP$DUR_NP1)
t.test(Data_usable_with_animacyAB_RI$DUR_NP1,Data_usable_with_animacyAB_UI$DUR_NP1)

#t-tests for if differences in Duration to start exist b/w people & items, and related vs unrelated
t.test(Data_usable_with_animacyAB_P$DUR_NP1,Data_usable_with_animacyAB_I$DUR_NP1)
t.test(Data_usable_with_animacyAB_R$DUR_NP1,Data_usable_with_animacyAB_U$DUR_NP1)

#means and sds for the related and unrelated items - duration of the second noun phrase
print("related items vs unrelated items \n")
cat(mean(Data_usable_with_animacyAB_RI$DUR_NP1), sd(Data_usable_with_animacyAB_RI$DUR_NP1), "\n")
cat(mean(Data_usable_with_animacyAB_UI$DUR_NP1), sd(Data_usable_with_animacyAB_UI$DUR_NP1), "\n")

#means and sds for related and unrelated people - duration of the 2nd noun phrase
print("DURATION NP2\n")
print("Related people vs unrelated people \n")
cat(mean(Data_usable_with_animacyAB_RP$DUR_NP2), sd(Data_usable_with_animacyAB_RP$DUR_NP2), "\n") #mean & sd related people NP2
cat(mean(Data_usable_with_animacyAB_UP$DUR_NP2), sd(Data_usable_with_animacyAB_UP$DUR_NP2), "\n") #mean & sd runelated people NP2

#means and sds for the related and unrelated items - duration of the second noun phrase
print("DURATION NP2 \n")
print("Related items vs unrelated items \n")
cat(mean(Data_usable_with_animacyAB_RI$DUR_NP2), sd(Data_usable_with_animacyAB_RI$DUR_NP2), "\n") #mean & sd related items NP2
cat(mean(Data_usable_with_animacyAB_UI$DUR_NP2), sd(Data_usable_with_animacyAB_UI$DUR_NP2), "\n") #mean & sd unrelated items NP2

#means for people and items overall for duration NP2
print("DURATION NP2 \n")
print("people vs items \n")
cat(mean(Data_usable_with_animacyAB_P$DUR_NP2), sd(Data_usable_with_animacyAB_P$DUR_NP2), "\n")
cat(mean(Data_usable_with_animacyAB_I$DUR_NP2), sd(Data_usable_with_animacyAB_I$DUR_NP2), "\n")

#means for related and unrelated overall for duration NP2
print("DURATION NP2 \n")
print("Related vs unrelated \n")
cat(mean(Data_usable_with_animacyAB_R$DUR_NP2), sd(Data_usable_with_animacyAB_R$DUR_NP2), "\n")
cat(mean(Data_usable_with_animacyAB_U$DUR_NP2), sd(Data_usable_with_animacyAB_U$DUR_NP2), "\n")

#means and sds for related and unrelated people - duration of the 'and'
print("DURATION AND \n")
print("Related people vs unrelated people \n")
cat(mean(Data_usable_with_animacyAB_RP$DUR_AND), sd(Data_usable_with_animacyAB_RP$DUR_AND), "\n") #mean & sd related people AND
cat(mean(Data_usable_with_animacyAB_UP$DUR_AND), sd(Data_usable_with_animacyAB_UP$DUR_AND), "\n") #mean & sd unrelated people AND

#means and sds for the related and unrelated items - duration of the 'and'
print("DURATION AND \n")
print("Related items vs unrelated items \n")
cat(mean(Data_usable_with_animacyAB_RI$DUR_AND), sd(Data_usable_with_animacyAB_RI$DUR_AND), "\n") #mean & sd related items AND
cat(mean(Data_usable_with_animacyAB_UI$DUR_AND), sd(Data_usable_with_animacyAB_UI$DUR_AND), "\n") #mean & sd unrelated items AND

#means for people and items overall for duration AND
print("DURATION NP2 \n")
print("people vs items \n")
cat(mean(Data_usable_with_animacyAB_P$DUR_AND), sd(Data_usable_with_animacyAB_P$DUR_AND), "\n")
cat(mean(Data_usable_with_animacyAB_I$DUR_AND), sd(Data_usable_with_animacyAB_I$DUR_AND), "\n")

#means for related and unrelated overall for duration AND
print("DURATION NP2 \n")
print("Related vs unrelated \n")
cat(mean(Data_usable_with_animacyAB_R$DUR_AND), sd(Data_usable_with_animacyAB_R$DUR_AND), "\n")
cat(mean(Data_usable_with_animacyAB_U$DUR_AND), sd(Data_usable_with_animacyAB_U$DUR_AND), "\n")

#means and sds for related and unrelated people - duration of the 3rd noun phrase
print("DURATION NP3 \n")
print("Related people vs unrelated people \n")
cat(mean(Data_usable_with_animacyAB_RP$DUR_NP3), sd(Data_usable_with_animacyAB_RP$DUR_NP3), "\n") #mean & sd related people NP3
cat(mean(Data_usable_with_animacyAB_UP$DUR_NP3), sd(Data_usable_with_animacyAB_UP$DUR_NP3), "\n") #mean & sd unrelated people NP3

#means and sds for the related and unrelated items - duration of the 3rd noun phrase
print("DURATION NP3 \n")
print("Related items vs unrelated items \n")
cat(mean(Data_usable_with_animacyAB_RI$DUR_NP3), sd(Data_usable_with_animacyAB_RI$DUR_NP3), "\n") #mean & sd related items NP3
cat(mean(Data_usable_with_animacyAB_UI$DUR_NP3), sd(Data_usable_with_animacyAB_UI$DUR_NP3), "\n") #mean & sd unrelated items NP3

#means for people and items overall for duration NP3
print("DURATION NP3 \n")
print("People vs items \n")
cat(mean(Data_usable_with_animacyAB_P$DUR_NP3), sd(Data_usable_with_animacyAB_P$DUR_NP3), "\n")
cat(mean(Data_usable_with_animacyAB_I$DUR_NP3), sd(Data_usable_with_animacyAB_I$DUR_NP3), "\n")

#means for related and unrelated overall for duration NP3
print("DURATION NP3 \n")
print("Related vs unrelated \n")
cat(mean(Data_usable_with_animacyAB_R$DUR_NP3), sd(Data_usable_with_animacyAB_R$DUR_NP3), "\n")
cat(mean(Data_usable_with_animacyAB_U$DUR_NP3), sd(Data_usable_with_animacyAB_U$DUR_NP3), "\n")

itemsdur3<-glm(Data_useable_itemsAB$DUR_NP3 ~ Data_useable_itemsAB$Nsyl_P3 + Data_useable_itemsAB$xcPMI + Data_useable_itemsAB$xcFreq2 + Data_useable_itemsAB$xcNA2 + Data_useable_itemsAB$item_order, family = gaussian(link='log'))
peopledur3<-glm(Data_useable_peopleAB$DUR_NP3 ~ Data_useable_peopleAB$Nsyl_P3 + Data_useable_peopleAB$xcPMI +Data_useable_peopleAB$xcCos + Data_useable_peopleAB$xcFreq2 + Data_useable_peopleAB$xcNA2 + Data_useable_peopleAB$item_order, family = gaussian(link='log'))

summary(itemsdur3)
summary(peopledur3)

itemsdurAnd<-glm(Data_useable_itemsAB$DUR_AND ~ Data_useable_itemsAB$Nsyl_P3 + Data_useable_itemsAB$xcPMI + Data_useable_itemsAB$xcFreq2 + Data_useable_itemsAB$xcNA2 + Data_useable_itemsAB$item_order, family = gaussian(link='log'))
peopledurAND<-glm(Data_useable_peopleAB$DUR_AND ~ Data_useable_peopleAB$Nsyl_P3 + Data_useable_peopleAB$xcPMI +Data_useable_peopleAB$xcCos + Data_useable_peopleAB$xcFreq2 + Data_useable_peopleAB$xcNA2 + Data_useable_peopleAB$item_order, family = gaussian(link='log'))

summary(itemsdurAnd)
summary(peopledurAND)

itemsdur2<-glm(Data_useable_itemsAB$DUR_NP2 ~ Data_useable_itemsAB$Nsyl_P2 + Data_useable_itemsAB$xcPMI + Data_useable_itemsAB$xcFreq1 + Data_useable_itemsAB$xcNA1 + Data_useable_itemsAB$item_order, family = gaussian(link='log'))
peopledur2<-glm(Data_useable_peopleAB$DUR_NP2 ~ Data_useable_peopleAB$Nsyl_P2 + Data_useable_peopleAB$xcPMI +Data_useable_peopleAB$xcCos + Data_useable_peopleAB$xcFreq1 + Data_useable_peopleAB$xcNA1 + Data_useable_peopleAB$item_order, family = gaussian(link='log'))

summary(itemsdur2)
summary(peopledur2)
```

Break up means by animacy : duration 2 for related people vs unrelated people when the person came first vs when the item was first

```{r}
people_first_RP <- Data_usable_with_animacyAB_RP %>% filter(Data_usable_with_animacyAB_RP$item_order == .5)
people_first_UP <- Data_usable_with_animacyAB_UP %>% filter(Data_usable_with_animacyAB_UP$item_order == .5)
people_first_RI <- Data_usable_with_animacyAB_RI %>% filter(Data_usable_with_animacyAB_RI$item_order == .5)
people_first_UI <- Data_usable_with_animacyAB_UI %>% filter(Data_usable_with_animacyAB_UI$item_order == .5)

item_first_RP <- Data_usable_with_animacyAB_RP %>% filter(Data_usable_with_animacyAB_RP$item_order == -.5)
item_first_UP <- Data_usable_with_animacyAB_UP %>% filter(Data_usable_with_animacyAB_UP$item_order == -.5)
item_first_RI <- Data_usable_with_animacyAB_RI %>% filter(Data_usable_with_animacyAB_RI$item_order == -.5)
item_first_UI <- Data_usable_with_animacyAB_UI %>% filter(Data_usable_with_animacyAB_UI$item_order == -.5)

cat("The mean of anchor-first RP DUR_NP1: ",mean(people_first_RP$DUR_NP1), "and sd: ",sd(people_first_RP$DUR_NP1),"\n")
cat("The mean of anchor-first UP DUR_NP1: ",mean(people_first_UP$DUR_NP1), "and sd: ",sd(people_first_UP$DUR_NP1),"\n")
cat("The mean of anchor-first RI DUR_NP1: ",mean(people_first_RI$DUR_NP1), "and sd: ",sd(people_first_RI$DUR_NP1),"\n")
cat("The mean of anchor-first UI DUR_NP1: ",mean(people_first_UI$DUR_NP1), "and sd: ",sd(people_first_UI$DUR_NP1),"\n")

NP1_anchor_person_RP_mean <- mean(people_first_RP$DUR_NP1)
NP1_anchor_person_UP_mean <- mean(people_first_UP$DUR_NP1)
NP1_anchor_person_RI_mean <- mean(people_first_RI$DUR_NP1)
NP1_anchor_person_UI_mean <- mean(people_first_UI$DUR_NP1)

NP1_related_person_RP_mean <- mean(item_first_RP$DUR_NP1)
NP1_unrelated_person_UP_mean <- mean(item_first_UP$DUR_NP1)
NP1_related_item_RI_mean <- mean(item_first_RI$DUR_NP1)
NP1_unrelated_item_UI_mean <- mean(item_first_UI$DUR_NP1)

cat("The mean of anchor-first RP DUR_NP2: ",mean(people_first_RP$DUR_NP2), "and sd: ",sd(people_first_RP$DUR_NP2),"\n")
cat("The mean of anchor-first UP DUR_NP2: ",mean(people_first_UP$DUR_NP2), "and sd: ",sd(people_first_UP$DUR_NP2),"\n")
cat("The mean of anchor-first RI DUR_NP2: ",mean(people_first_RI$DUR_NP2), "and sd: ",sd(people_first_RI$DUR_NP2),"\n")
cat("The mean of anchor-first UI DUR_NP2: ",mean(people_first_UI$DUR_NP2), "and sd: ",sd(people_first_UI$DUR_NP2),"\n")

NP2_anchor_person_RP_mean <- mean(people_first_RP$DUR_NP2)
NP2_anchor_person_UP_mean <- mean(people_first_UP$DUR_NP2)
NP2_anchor_person_RI_mean <- mean(people_first_RI$DUR_NP2)
NP2_anchor_person_UI_mean <- mean(people_first_UI$DUR_NP2)

NP2_related_person_RP_mean <- mean(item_first_RP$DUR_NP2)
NP2_unrelated_person_UP_mean <- mean(item_first_UP$DUR_NP2)
NP2_related_item_RI_mean <- mean(item_first_RI$DUR_NP2)
NP2_unrelated_item_UI_mean <- mean(item_first_UI$DUR_NP2)

cat("The mean of anchor-first RP: ",mean(people_first_RP$DUR_AND), "and sd: ",sd(people_first_RP$DUR_AND),"\n")
cat("The mean of anchor-first UP: ",mean(people_first_UP$DUR_AND), "and sd: ",sd(people_first_UP$DUR_AND),"\n")
cat("The mean of anchor-first RI: ",mean(people_first_RI$DUR_AND), "and sd: ",sd(people_first_RI$DUR_AND),"\n")
cat("The mean of anchor-first UI: ",mean(people_first_UI$DUR_AND), "and sd: ",sd(people_first_UI$DUR_AND),"\n")

AND_anchor_person_RP_mean <- mean(people_first_RP$DUR_AND)
AND_anchor_person_UP_mean <- mean(people_first_UP$DUR_AND)
AND_anchor_person_RI_mean <- mean(people_first_RI$DUR_AND)
AND_anchor_person_UI_mean <- mean(people_first_UI$DUR_AND)

AND_related_person_RP_mean <- mean(item_first_RP$DUR_AND)
AND_unrelated_person_UP_mean <- mean(item_first_UP$DUR_AND)
AND_related_item_RI_mean <- mean(item_first_RI$DUR_AND)
AND_unrelated_item_UI_mean <- mean(item_first_UI$DUR_AND)

cat("The mean of anchor-first RP DUR_NP3: ",mean(people_first_RP$DUR_NP3), "and sd: ",sd(people_first_RP$DUR_NP3),"\n")
cat("The mean of anchor-first UP DUR_NP3: ",mean(people_first_UP$DUR_NP3), "and sd: ",sd(people_first_UP$DUR_NP3),"\n")
cat("The mean of anchor-first RI DUR_NP3: ",mean(people_first_RI$DUR_NP3), "and sd: ",sd(people_first_RI$DUR_NP3),"\n")
cat("The mean of anchor-first UI DUR_NP3: ",mean(people_first_UI$DUR_NP3), "and sd: ",sd(people_first_UI$DUR_NP3),"\n")

NP3_anchor_person_RP_mean <- mean(people_first_RP$DUR_NP3)
NP3_anchor_person_UP_mean <- mean(people_first_UP$DUR_NP3)
NP3_anchor_person_RI_mean <- mean(people_first_RI$DUR_NP3)
NP3_anchor_person_UI_mean <- mean(people_first_UI$DUR_NP3)

NP3_related_person_RP_mean <- mean(item_first_RP$DUR_NP3)
NP3_unrelated_person_UP_mean <- mean(item_first_UP$DUR_NP3)
NP3_related_item_RI_mean <- mean(item_first_RI$DUR_NP3)
NP3_unrelated_item_UI_mean <- mean(item_first_UI$DUR_NP3)

NP1_anchor_first <- c(NP1_anchor_person_RP_mean,NP1_anchor_person_UP_mean,NP1_anchor_person_RI_mean,NP1_anchor_person_UI_mean)
NP1_other_first <- c(NP1_related_person_RP_mean,NP1_unrelated_person_UP_mean,NP1_related_item_RI_mean,NP1_unrelated_item_UI_mean)

NP2_anchor_first <- c(NP2_anchor_person_RP_mean,NP2_anchor_person_UP_mean,NP2_anchor_person_RI_mean,NP2_anchor_person_UI_mean)
NP2_other_first <- c(NP2_related_person_RP_mean,NP2_unrelated_person_UP_mean,NP2_related_item_RI_mean,NP2_unrelated_item_UI_mean)

AND_anchor_first <- c(AND_anchor_person_RP_mean,AND_anchor_person_UP_mean,AND_anchor_person_RI_mean,AND_anchor_person_UI_mean)
AND_other_first <- c(AND_related_person_RP_mean,AND_unrelated_person_UP_mean,AND_related_item_RI_mean,AND_unrelated_item_UI_mean)

NP3_anchor_first <- c(NP3_anchor_person_RP_mean,NP3_anchor_person_UP_mean,NP3_anchor_person_RI_mean,NP3_anchor_person_UI_mean)
NP3_other_first <- c(NP3_related_person_RP_mean,NP3_unrelated_person_UP_mean,NP3_related_item_RI_mean,NP3_unrelated_item_UI_mean)

row_names <- c("Related Person", "Unrelated Person", "Related Item", "Unrelated Item")
blanks <- c(" ", " ", " ", " ")
library(rempsyc)
means_table <- nice_table(data.frame(row_names, NP1_anchor_first,NP1_other_first, NP2_anchor_first, NP2_other_first,AND_anchor_first, AND_other_first, NP3_anchor_first, NP3_other_first));means_table
library(dplyr)
library(flextable)
means_table %>%
  align(i = 1:4, j = 1, align = "left", part = "body") %>%
  align(j = 1, align = "left", part = "header") %>%
  set_table_properties(width = .7, layout = "autofit") %>%
  autofit(add_w = -1, add_h = -0.1, part = c("body", "header"), unit = "in") %>%
  bold(bold = TRUE, part = "header") %>%
  fontsize(size = 12, part = "body") %>%
  fontsize(size = 12, part = "header") %>%
  italic(italic = FALSE, part = "header") %>%
  set_header_labels(row_names = " ",
                    NP1_anchor_first = "Duration NP1 \n anchor first",
                    NP1_other_first = "Duration NP1 \n second first",
                    NP2_anchor_first = "Duration NP2 \n anchor first",
                    NP2_other_first = "Duration NP2 \n second first",
                    AND_anchor_first = "Duration AND \n anchor first",
                    AND_other_first = "Duration AND \n second first",
                    NP3_anchor_first = "Duration NP3 \n anchor first",
                    NP3_other_first = "Duration NP3 \n second first")

#basic t-tests NP1 - all NS which is good
print("anchor person first RP vs UP \n")
t.test(people_first_RP$DUR_NP1, people_first_UP$DUR_NP1) #NS
print("anchor first RI vs UI \n")
t.test(people_first_RI$DUR_NP1, people_first_UI$DUR_NP1) #NS
#basic t-tests AND
print("anchor person first RP vs UP \n")
t.test(people_first_RP$DUR_NP2, people_first_UP$DUR_NP2) #NS
print("anchor first RI vs UI \n")
t.test(people_first_RI$DUR_NP2, people_first_UI$DUR_NP2) #NS
#basic t-tests NP2
print("anchor person first RP vs UP \n")
t.test(people_first_RP$DUR_AND, people_first_UP$DUR_AND) #NS
print("anchor first RI vs UI \n")
t.test(people_first_RI$DUR_AND, people_first_UI$DUR_AND) #NS
#basic t-tests NP3
print("anchor person first RP vs UP \n")
t.test(people_first_RP$DUR_NP3, people_first_UP$DUR_NP3) #SIG
print("anchor first RI vs UI \n")
t.test(people_first_RI$DUR_NP3, people_first_UI$DUR_NP3) #NS

cat("The mean of other-first RP DUR_NP1: ",mean(item_first_RP$DUR_NP1), "and sd: ",sd(item_first_RP$DUR_NP1),"\n")
cat("The mean of other-first UP DUR_NP1: ",mean(item_first_UP$DUR_NP1), "and sd: ",sd(item_first_UP$DUR_NP1),"\n")
cat("The mean of other-first RI DUR_NP1: ",mean(item_first_RI$DUR_NP1), "and sd: ",sd(item_first_RI$DUR_NP1),"\n")
cat("The mean of other-first UI DUR_NP1: ",mean(item_first_UI$DUR_NP1), "and sd: ",sd(item_first_UI$DUR_NP1),"\n")

cat("The mean of other-first RP DUR_NP2: ",mean(item_first_RP$DUR_NP2), "and sd: ",sd(item_first_RP$DUR_NP2),"\n")
cat("The mean of other-first UP DUR_NP2: ",mean(item_first_UP$DUR_NP2), "and sd: ",sd(item_first_UP$DUR_NP2),"\n")
cat("The mean of other-first RI DUR_NP2: ",mean(item_first_RI$DUR_NP2), "and sd: ",sd(item_first_RI$DUR_NP2),"\n")
cat("The mean of other-first UI DUR_NP2: ",mean(item_first_UI$DUR_NP2), "and sd: ",sd(item_first_UI$DUR_NP2),"\n")

cat("The mean of other-first RP DUR_AND: ",mean(item_first_RP$DUR_AND), "and sd: ",sd(item_first_RP$DUR_AND),"\n")
cat("The mean of other-first UP DUR_AND: ",mean(item_first_UP$DUR_AND), "and sd: ",sd(item_first_UP$DUR_AND),"\n")
cat("The mean of other-first RI DUR_AND: ",mean(item_first_RI$DUR_AND), "and sd: ",sd(item_first_RI$DUR_AND),"\n")
cat("The mean of other-first UI DUR_AND: ",mean(item_first_UI$DUR_AND), "and sd: ",sd(item_first_UI$DUR_AND),"\n")

cat("The mean of other-first RP DUR_NP3: ",mean(item_first_RP$DUR_NP3), "and sd: ",sd(item_first_RP$DUR_NP3),"\n")
cat("The mean of other-first UP DUR_NP3: ",mean(item_first_UP$DUR_NP3), "and sd: ",sd(item_first_UP$DUR_NP3),"\n")
cat("The mean of other-first RI DUR_NP3: ",mean(item_first_RI$DUR_NP3), "and sd: ",sd(item_first_RI$DUR_NP3),"\n")
cat("The mean of other-first UI DUR_NP3: ",mean(item_first_UI$DUR_NP3), "and sd: ",sd(item_first_UI$DUR_NP3),"\n")

#basic t-tests NP1 - all NS which is good
print("non-anchor person first RP vs UP \n")
t.test(item_first_RP$DUR_NP1, item_first_UP$DUR_NP1) #NS
print("item first RI vs UI \n")
t.test(item_first_RI$DUR_NP1, item_first_UI$DUR_NP1) #NS
#basic t-tests AND
print("non-anchor person first RP vs UP \n")
t.test(item_first_RP$DUR_NP2, item_first_UP$DUR_NP2) #NS
print("item first RI vs UI \n")
t.test(item_first_RI$DUR_NP2, item_first_UI$DUR_NP2) #NS
#basic t-tests NP2
print("non-anchor person first RP vs UP \n")
t.test(item_first_RP$DUR_AND, item_first_UP$DUR_AND) #NS
print("item first RI vs UI \n")
t.test(item_first_RI$DUR_AND, item_first_UI$DUR_AND) #NS
#basic t-tests NP3
print("non-anchor person first RP vs UP \n")
t.test(item_first_RP$DUR_NP3, item_first_UP$DUR_NP3) #NS
print("item first RI vs UI \n")
t.test(item_first_RI$DUR_NP3, item_first_UI$DUR_NP3) #NS

cat("The mean of anchor-first RP DUR_NP2: ",mean(people_first_RP$DUR_NP2), "and sd: ",sd(people_first_RP$DUR_NP2),"\n")
cat("The mean of anchor-first UP DUR_NP2: ",mean(people_first_UP$DUR_NP2), "and sd: ",sd(people_first_UP$DUR_NP2),"\n")
cat("The mean of related-person-first RP DUR_NP2: ",mean(item_first_RP$DUR_NP2), "and sd: ",sd(item_first_RP$DUR_NP2),"\n")
cat("The mean of unrelated-person-first UP DUR_NP2: ",mean(item_first_UP$DUR_NP2), "and sd: ",sd(item_first_UP$DUR_NP2),"\n")

cat("The mean of anchor-first RI DUR_NP2: ",mean(people_first_RI$DUR_NP2), "and sd: ",sd(people_first_RI$DUR_NP2),"\n")
cat("The mean of anchor-first UI DUR_NP2: ",mean(people_first_UI$DUR_NP2), "and sd: ",sd(people_first_UI$DUR_NP2),"\n")
cat("The mean of item-first RI DUR_NP2: ",mean(item_first_RI$DUR_NP2), "and sd: ",sd(item_first_RI$DUR_NP2),"\n")
cat("The mean of item-first UI DUR_NP2: ",mean(item_first_UI$DUR_NP2), "and sd: ",sd(item_first_UI$DUR_NP2),"\n")

t.test(people_first_RP$DUR_NP2,item_first_RP$DUR_NP2) #NS
t.test(people_first_UP$DUR_NP2,item_first_UP$DUR_NP2) #NS

t.test(people_first_RI$DUR_NP2,item_first_RI$DUR_NP2) #SIG
t.test(people_first_UI$DUR_NP2,item_first_UI$DUR_NP2) #SIG - items are quicker in both cases when they come first

cat("The mean of anchor-first RP DUR_NP3: ",mean(people_first_RP$DUR_NP3), "and sd: ",sd(people_first_RP$DUR_NP3),"\n")
cat("The mean of anchor-first UP DUR_NP3: ",mean(people_first_UP$DUR_NP3), "and sd: ",sd(people_first_UP$DUR_NP3),"\n")
cat("The mean of related-person-first RP DUR_NP3: ",mean(item_first_RP$DUR_NP3), "and sd: ",sd(item_first_RP$DUR_NP3),"\n")
cat("The mean of unrelated-person-first UP DUR_NP3: ",mean(item_first_UP$DUR_NP3), "and sd: ",sd(item_first_UP$DUR_NP3),"\n")

cat("The mean of anchor-first RI DUR_NP3: ",mean(people_first_RI$DUR_NP3), "and sd: ",sd(people_first_RI$DUR_NP3),"\n")
cat("The mean of anchor-first UI DUR_NP3: ",mean(people_first_UI$DUR_NP3), "and sd: ",sd(people_first_UI$DUR_NP3),"\n")
cat("The mean of item-first RI DUR_NP3: ",mean(item_first_RI$DUR_NP3), "and sd: ",sd(item_first_RI$DUR_NP3),"\n")
cat("The mean of item-first UI DUR_NP3: ",mean(item_first_UI$DUR_NP3), "and sd: ",sd(item_first_UI$DUR_NP3),"\n")

t.test(people_first_RP$DUR_NP3,item_first_RP$DUR_NP3) #NS
t.test(people_first_UP$DUR_NP3,item_first_UP$DUR_NP3) #NS

t.test(people_first_RI$DUR_NP3,item_first_RI$DUR_NP3) #SIG
t.test(people_first_UI$DUR_NP3,item_first_UI$DUR_NP3) #SIG - items are quicker in both cases

t.test(item_first_RI$DUR_NP3,item_first_UI$DUR_NP3) #NS
```

Looking at syllables

```{r}
#subset data for RP and UP separately
Data_useable_peopleAB_RP <- Data_useable_peopleAB %>% filter(Data_useable_peopleAB$Condition == "RP") 
Data_useable_peopleAB_UP <- Data_useable_peopleAB %>% filter(Data_useable_peopleAB$Condition == "UP") 

Data_useable_peopleAB_withsyls <- Data_useable_peopleAB %>% mutate(Syllables_other_person = ifelse( 
  ((Data_useable_peopleAB$item_order == .5 & Data_useable_peopleAB$Nsyl_P3 == 1) | #if anchor came first, check 3rd person for 1 syl (that would be the RP)
    (Data_useable_peopleAB$item_order == -.5 & Data_useable_peopleAB$Nsyl_P2 == 1)), 1, ifelse(
  ((Data_useable_peopleAB$item_order == .5 & Data_useable_peopleAB$Nsyl_P3 == 2) |  
    (Data_useable_peopleAB$item_order == -.5 & Data_useable_peopleAB$Nsyl_P2 == 2)), 2, ifelse(
  ((Data_useable_peopleAB$item_order == .5 & Data_useable_peopleAB$Nsyl_P3 == 3) |  
    (Data_useable_peopleAB$item_order == -.5 & Data_useable_peopleAB$Nsyl_P2 == 3)),3, 4)
    )
    ))

#filter by cases where the Related person was 1 syllable
RP_nsyl1 <- Data_useable_peopleAB_RP %>% filter(
  (Data_useable_peopleAB_RP$item_order == .5 & Data_useable_peopleAB_RP$Nsyl_P3 == 1) | #if anchor came first, check 3rd person for 1 syl (that would be the RP)
    (Data_useable_peopleAB_RP$item_order == -.5 & Data_useable_peopleAB_RP$Nsyl_P2 == 1))#if anchor came last, check 2nd person for 1 syl (that would be the RP)
#filter by cases where the Related person was 2 syllables
RP_nsyl2 <- Data_useable_peopleAB_RP %>% filter(
  (Data_useable_peopleAB_RP$item_order == .5 & Data_useable_peopleAB_RP$Nsyl_P3 == 2) |  
    (Data_useable_peopleAB_RP$item_order == -.5 & Data_useable_peopleAB_RP$Nsyl_P2 == 2))
#filter by cases where the Related person was 3 syllables
RP_nsyl3 <- Data_useable_peopleAB_RP %>% filter(
  (Data_useable_peopleAB_RP$item_order == .5 & Data_useable_peopleAB_RP$Nsyl_P3 == 3) | 
    (Data_useable_peopleAB_RP$item_order == -.5 & Data_useable_peopleAB_RP$Nsyl_P2 == 3))
#filter by cases where the Related person was 4 syllables
RP_nsyl4 <- Data_useable_peopleAB_RP %>% filter(
  (Data_useable_peopleAB_RP$item_order == .5 & Data_useable_peopleAB_RP$Nsyl_P3 == 4) | 
    (Data_useable_peopleAB_RP$item_order == -.5 & Data_useable_peopleAB_RP$Nsyl_P2 == 4))

#now do UPs

#filter by cases where the UP was 1 syllable
UP_nsyl1 <- Data_useable_peopleAB_UP %>% filter(
  (Data_useable_peopleAB_UP$item_order == .5 & Data_useable_peopleAB_UP$Nsyl_P3 == 1) | #if anchor came first, check 3rd person for 1 syl (that would be the UP)
    (Data_useable_peopleAB_UP$item_order == -.5 & Data_useable_peopleAB_UP$Nsyl_P2 == 1))#if anchor came last, check 2nd person for 1 syl (that would be the UP)
#filter by cases where the UP was 2 syllables
UP_nsyl2 <- Data_useable_peopleAB_UP %>% filter(
  (Data_useable_peopleAB_UP$item_order == .5 & Data_useable_peopleAB_UP$Nsyl_P3 == 2) |  
    (Data_useable_peopleAB_UP$item_order == -.5 & Data_useable_peopleAB_UP$Nsyl_P2 == 2))
#filter by cases where the UP was 3 syllables
UP_nsyl3 <- Data_useable_peopleAB_UP %>% filter(
  (Data_useable_peopleAB_UP$item_order == .5 & Data_useable_peopleAB_UP$Nsyl_P3 == 3) | 
    (Data_useable_peopleAB_UP$item_order == -.5 & Data_useable_peopleAB_UP$Nsyl_P2 == 3))
#filter by cases where the UP was 4 syllables
UP_nsyl4 <- Data_useable_peopleAB_UP %>% filter(
  (Data_useable_peopleAB_UP$item_order == .5 & Data_useable_peopleAB_UP$Nsyl_P3 == 4) | 
    (Data_useable_peopleAB_UP$item_order == -.5 & Data_useable_peopleAB_UP$Nsyl_P2 == 4))

c1 <- rgb(173,216,230,max = 255, alpha = 80, names = "lt.blue")
c2 <- rgb(144,238,144, max = 255, alpha = 90, names = "lt.green")

histplotter <- function(Dist1, Dist2, color_dist1, color_dist2, TITLE, X_LAB, Y_LAB){
  histmin <- min(c(Dist1,Dist2)) - 0.1 # Set the minimum for the breakpoints
  histmax <- max(c(Dist1,Dist2)) + .10 # Set the maximum for the breakpoints
  histbreaks <- seq(from = histmin, to = histmax, by = .1) # Make a neat vector for the breakpoints

  hgRP <- hist(Dist1, breaks = histbreaks, plot = FALSE) # Save first histogram data
  hgUP <- hist(Dist2, breaks = histbreaks, plot = FALSE) # Save 2nd histogram data

  plot(hgRP, col = c1,main = TITLE,xlab = X_LAB,ylab = Y_LAB) # Plot 1st histogram using a transparent color
  plot(hgUP, col = c2, add = TRUE) # Add 2nd histogram using different color
  legend("topright", c("Related People", "Unrelated People"), fill=c(c1, c2))
}



histplotter(RP_nsyl1$DUR_X_to_Y, UP_nsyl1$DUR_X_to_Y, c1, c2, TITLE = "Duration of NP2 to end", Y_LAB = "Frequency", X_LAB = "Duration (s)")
histplotter(RP_nsyl2$DUR_X_to_Y, UP_nsyl2$DUR_X_to_Y, c1, c2, TITLE = "Duration of NP2 to end", Y_LAB = "Frequency", X_LAB = "Duration (s)")
histplotter(RP_nsyl3$DUR_X_to_Y, UP_nsyl3$DUR_X_to_Y, c1, c2, TITLE = "Duration of NP2 to end", Y_LAB = "Frequency", X_LAB = "Duration (s)")
histplotter(RP_nsyl4$DUR_X_to_Y, UP_nsyl4$DUR_X_to_Y, c1, c2, TITLE = "Duration of NP2 to end", Y_LAB = "Frequency", X_LAB = "Duration (s)")

scatterplotter <- function(Dist1, Dist2, color_dist1, color_dist2, TITLE, X_LAB, Y_LAB){
  plotRP <- plot(Dist1, col = color_dist1,main = TITLE,ylab = Y_LAB) 
  plotUP <- points(Dist2, col=color_dist2)
  legend("topright", c("Related People", "Unrelated People"), fill=c(color_dist1, color_dist2))
}

scatterplotter(RP_nsyl1$DUR_X_to_Y, UP_nsyl1$DUR_X_to_Y, 'black', 'pink', TITLE = "Duration of NP2 to end", Y_LAB = "Duration")
scatterplotter(RP_nsyl2$DUR_X_to_Y, UP_nsyl2$DUR_X_to_Y, 'black', 'pink', TITLE = "Duration of NP2 to end", Y_LAB = "Duration")
scatterplotter(RP_nsyl3$DUR_X_to_Y, UP_nsyl3$DUR_X_to_Y, 'black', 'pink', TITLE = "Duration of NP2 to end", Y_LAB = "Duration")
scatterplotter(RP_nsyl4$DUR_X_to_Y, UP_nsyl4$DUR_X_to_Y, 'black', 'pink', TITLE = "Duration of NP2 to end", Y_LAB = "Duration")

#name agreement for 1 syllable RPs 
mean(RP_nsyl1$NA1)
mean(RP_nsyl1$NA2)

LookupTableNsyl1_RP <- LookupTable %>% filter(LookupTable$NsylRP == 1)
mean(LookupTableNsyl1_RP$NameAgreeRP)
LookupTableNsyl2_RP <- LookupTable %>% filter(LookupTable$NsylRP == 2)
mean(LookupTableNsyl2_RP$NameAgreeRP)
LookupTableNsyl3_RP <- LookupTable %>% filter(LookupTable$NsylRP == 3)
mean(LookupTableNsyl3_RP$NameAgreeRP)
LookupTableNsyl4_RP <- LookupTable %>% filter(LookupTable$NsylRP == 4)
mean(LookupTableNsyl4_RP$NameAgreeRP)

LookupTableNsyl1_UP <- LookupTable %>% filter(LookupTable$NsylUP == 1)
mean(LookupTableNsyl1_UP$NameAgreeUP)
LookupTableNsyl2_UP <- LookupTable %>% filter(LookupTable$NsylUP == 2)
mean(LookupTableNsyl2_UP$NameAgreeUP)
LookupTableNsyl3_UP <- LookupTable %>% filter(LookupTable$NsylUP == 3)
mean(LookupTableNsyl3_UP$NameAgreeUP)

#might be name agreement, average name agreement goes down as syllables go up for RP, but up as syllables go up for UP

t.test(LookupTable$NsylRI, LookupTable$NsylUI)
t.test(LookupTable$NsylRP, LookupTable$NsylUP)
t.test(c(LookupTable$NsylRP, LookupTable$NsylRI), c(LookupTable$NsylUP, LookupTable$NyslUI))

mean(LookupTable$NsylRP)
mean(LookupTable$NsylUP)

mean(LookupTable$NsylRI)
mean(LookupTable$NsylUI)

relateds <- c(LookupTable$NsylRP, LookupTable$NsylRI)
unrelateds <- c(LookupTable$NsylUP, LookupTable$NsylUI)
peeps <- c(LookupTable$NsylRP, LookupTable$NsylUP)
its <- c(LookupTable$NsylRI, LookupTable$NsylUI)

mean(relateds)
mean(unrelateds)
mean(peeps)
mean(its)

t.test(relateds, unrelateds)
t.test(peeps, its)
```

Rain cloud plots

```{r, eval = FALSE}
#durs_df <- data.frame(RP_nsyl1$DUR_X_to_Y, UP_nsyl1$DUR_X_to_Y,RP_nsyl2$DUR_X_to_Y, UP_nsyl2$DUR_X_to_Y,RP_nsyl3$DUR_X_to_Y, UP_nsyl3$DUR_X_to_Y, RP_nsyl4$DUR_X_to_Y, UP_nsyl4$DUR_X_to_Y)

library(raincloudplots)
library(ggplot2)
library(ggforce)
library(ggdist)
library(gghalves)

theme_set(theme_light(base_size = 16))
Data_useable_peopleAB_withsyls_RP <- Data_useable_peopleAB_withsyls %>% filter(Data_useable_peopleAB_withsyls$Condition == "RP")
Data_useable_peopleAB_withsyls_UP <- Data_useable_peopleAB_withsyls %>% filter(Data_useable_peopleAB_withsyls$Condition == "UP")

rp_plot<-ggplot(Data_useable_peopleAB_withsyls_small, aes(Syl, Duration, fill = Cond)) + scale_y_continuous(limits = c(1,6), breaks = c(1,2,3,4,5,6))+ tidyquant::theme_tq() +
  ggdist::stat_halfeye(adjust = .5, width = .3, .width = c(0.5, 1))  + labs(x = "Syllables RP", y = "Duration (s)")
  ggdist::stat_dots(side = "left", dotsize = .1, justification = 1.05, binwidth = .05)
rp_plot
up_plot<-ggplot(Data_useable_peopleAB_withsyls_UP, aes(Syllables_other_person, DUR_X_to_Y)) + scale_y_continuous(limits = c(1,6), breaks = c(1,2,3,4,5,6)) + labs(y = " ", x = "Syllables UP") + tidyquant::theme_tq()+
  ggdist::stat_halfeye(adjust = .5, width = .3, .width = c(0.5, 1)) + 
  ggdist::stat_dots(side = "left", dotsize = .1, justification = 1.05, binwidth = .05)
gridExtra::grid.arrange(rp_plot, up_plot, ncol = 2)

source("R_rainclouds.R")
RPplot <- ggplot(Data_useable_peopleAB_withsyls_small, aes(x = Syl, y = Duration, fill = Cond)) + geom_flat_violin(alpha = .5) +
  geom_point(position = position_jitter(width = .15), size = .25, col = Cond) +
  ylab('Duration (s)')+ xlab('Number of Syllables for RP')+ theme_cowplot()
RPplot

UPplot <- ggplot(Data_useable_peopleAB_withsyls_UP, aes(x = Syllables_other_person, y = DUR_X_to_Y)) + #geom_flat_violin() +
  geom_point(position = position_jitter(width = .15), size = .25) +
  ylab('Duration (s)')+ xlab('Number of Syllables for RP')+ theme_cowplot()
RPplot

gridExtra::grid.arrange(RPplot, RPplot, ncol = 2)


ap2 <- ggplot(Data_useable_peopleAB_withsyls_small,aes(x=Syl,y=Duration,fill=Cond,col=Cond))+
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha =.4,adjust =4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.7) +
  ylab('Duration(s)')+scale_fill_brewer(palette = "Dark2")+scale_colour_brewer(palette = "Dark2")+ggtitle('Durations by Syllables')

ap2
all_plot <- plot_grid(ap1, ap2, labels="AUTO")

Duration <- Data_useable_peopleAB_withsyls$DUR_X_to_Y
Cond <- Data_useable_peopleAB_withsyls$Condition
Syl <- as.factor(Data_useable_peopleAB_withsyls$Syllables_XY)
Data_useable_peopleAB_withsyls_small <- data.frame(Cond, Syl, Duration)

#Added jitter helps
ap2 <- ggplot(Data_useable_peopleAB_withsyls_small,aes(x=Syl,y=Duration,fill=Cond,col=Cond))+
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha =.4,adjust =4)+
  geom_point(position=position_jitter(width = .15),size = 1, alpha = 0.7) +
  ylab('Duration(s)') + xlab('Syllables')+scale_fill_brewer(palette = "Dark2")+scale_colour_brewer(palette = "Dark2")+ggtitle('                      Durations by Syllables')

ap2

p12 <- ggplot(Data_useable_peopleAB_withsyls_small, aes(x = Syl, y = Duration, fill = Cond)) +
  geom_flat_violin(aes(fill = Cond),position = position_nudge(x = .1, y = 0), adjust = 1.5, trim = FALSE, alpha = .5, colour = NA)+
  geom_point(aes(x = Syl, y = Duration, colour = Cond),position = position_jitter(width = .05), size = .25, shape = 20)+
  geom_boxplot(aes(x = Syl, y = Duration, fill = Cond),outlier.shape = NA, alpha = .5, width = .1, colour = "black")+
  scale_colour_brewer(palette = "Dark2")+
  scale_fill_brewer(palette = "Dark2")+
  ggtitle("                      Duration by Syllables") + xlab('Syllables of both people') + ylab('Duration (s)')

p12
```

Raincloud plots by condition
```{r}
Data_useable_with_animacyAB <- Data_useable_with_animacyAB %>% mutate(DUR_AND_plus_NP3 = NP3_end-NP2_End)
colorz <- c("#7a7a7a", "#404f86", "#a6a6a6", "#3e1451")
colorz <- c("#80CDC1","#35978F","#01665E","#003C30")
colorz <- c("#83A270","#5A2F32","#3D8A8F","#B9B587")

ggplot(Data_useable_with_animacyAB, aes(Condition, DUR_NP1, fill = Condition)) + 
  ggdist::stat_halfeye(adjust = .5, width = .3, .width = 0, justification = -.3, point_colour = NA) + 
  geom_boxplot(width = .1, outlier.shape = NA) +
  gghalves::geom_half_point(side = "l", range_scale = .4, alpha = .5) +
  stat_summary(fun.y=mean, colour="black", geom="point", shape=16, size=1.7,show.legend = FALSE) +
  theme(plot.title = element_text(hjust = 0.5, size = 24), axis.text.x = element_text(size = 16), axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) + ylim(c(0,5)) +
  labs(title = "Duration of NP1 by condition", y = "Duration (s)", x = "Condition") +
  scale_colour_manual(values=colorz) +
  scale_fill_manual(values=colorz) +
  scale_x_discrete(name="Condition", labels=c("RI" = "Related \nItem", "RP" = "Related \nPerson",  "UI" = "Unrelated \nItem", "UP" = "Unrelated \nPerson"))
```

```{r}
rcp_NP2 <-ggplot(Data_useable_with_animacyAB, aes(Condition, DUR_NP2, fill = Condition)) + 
  ggdist::stat_halfeye(adjust = .5, width = .3, .width = 0, justification = -.3, point_colour = NA) + 
  geom_boxplot(width = .1, outlier.shape = NA) +
  gghalves::geom_half_point(side = "l", range_scale = .4, alpha = .5) +
  labs(title = "Duration of NP2 by condition", y = "Duration (s)", x = "Condition") +
  theme(plot.title = element_text(hjust = 0.5, size = 24), axis.text.x = element_text(size = 16), axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  ylim(c(0,5)) +
  scale_colour_manual(values=colorz) +
  scale_fill_manual(values=colorz)

rcp_AND<- ggplot(Data_useable_with_animacyAB, aes(Condition, DUR_AND, fill = Condition)) + 
  ggdist::stat_halfeye(adjust = .5, width = .3, .width = 0, justification = -.3, point_colour = NA) + 
  geom_boxplot(width = .1, outlier.shape = NA) +
  gghalves::geom_half_point(side = "l", range_scale = .4, alpha = .5) +
  labs(title = "Duration of AND by condition", y = "Duration (s)", x = "Condition") +
  theme(plot.title = element_text(hjust = 0.5, size = 24), axis.text.x = element_text(size = 16), axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  ylim(c(0,5)) +
  scale_colour_manual(values=colorz) +
  scale_fill_manual(values=colorz)

rcp_NP3 <-ggplot(Data_useable_with_animacyAB, aes(Condition, DUR_NP3, fill = Condition)) + 
  ggdist::stat_halfeye(adjust = .5, width = .3, .width = 0, justification = -.3, point_colour = NA) + 
  geom_boxplot(width = .1, outlier.shape = NA) +
  gghalves::geom_half_point(side = "l", range_scale = .4, alpha = .5) +
  labs(title = "Duration of NP3 by condition", y = "Duration (s)", x = "Condition") +
  theme(plot.title = element_text(hjust = 0.5, size = 24), axis.text.x = element_text(size = 16), axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  ylim(c(0,5)) +
  scale_colour_manual(values=colorz) +
  scale_fill_manual(values=colorz)

rcp_ANDNP3 <- ggplot(Data_useable_with_animacyAB, aes(Condition, DUR_AND_plus_NP3, fill = Condition)) + 
  ggdist::stat_halfeye(adjust = .5, width = .3, .width = 0, justification = -.3, point_colour = NA) + 
  geom_boxplot(width = .1, outlier.shape = NA) +
  gghalves::geom_half_point(side = "l", range_scale = .4, alpha = .5) +
  labs(title = "Duration of AND + NP3 by condition", y = "Duration (s)", x = "Condition") +
  theme(plot.title = element_text(hjust = 0.5, size = 24), axis.text.x = element_text(size = 16), axis.title.y = element_text(size = 20), axis.title.x = element_text(size = 20)) +
  ylim(c(0,5)) +
  scale_colour_manual(values=colorz) +
  scale_fill_manual(values=colorz)

pdf("rcp_NP2.pdf",  width = 10, height = 10) 
rcp_NP2
dev.off()
pdf("rcp_AND.pdf",  width = 10, height = 10) 
rcp_AND
dev.off()
pdf("rcp_NP3.pdf",  width = 10, height = 10) 
rcp_NP3
dev.off()
pdf("rcp_ANDNP3.pdf",  width = 10, height = 10) 
rcp_ANDNP3
dev.off()
```

```{r}
library(ggpubr)
ggarrange(rcp_NP2, rcp_AND, rcp_NP3 ,rcp_ANDNP3 + rremove("x.text"), 
          labels = c("NP2", "AND", "NP3", "ANDNP3"),
          ncol = 2, nrow = 2)
```

T-tests for DUR_NP2

```{r}
t.test(Data_usable_with_animacyAB_P$DUR_NP2,Data_usable_with_animacyAB_I$DUR_NP2) #SIG
t.test(Data_usable_with_animacyAB_R$DUR_NP2,Data_usable_with_animacyAB_U$DUR_NP2) #NS

#t-tests for related vs unrelated people and then related vs unrelated items: DUR_NP2
t.test(Data_usable_with_animacyAB_RP$DUR_NP2,Data_usable_with_animacyAB_UP$DUR_NP2) #NS
t.test(Data_usable_with_animacyAB_RI$DUR_NP2,Data_usable_with_animacyAB_UI$DUR_NP2) #NS

#t-test for animacy (ie comparing related people to related items, unrelated people vs unrelated items)
t.test(Data_usable_with_animacyAB_RP$DUR_NP2,Data_usable_with_animacyAB_RI$DUR_NP2) #SIG
t.test(Data_usable_with_animacyAB_UP$DUR_NP2,Data_usable_with_animacyAB_UI$DUR_NP2) #NS
```

T tests for DUR_AND

```{r}
t.test(Data_usable_with_animacyAB_R$DUR_AND,Data_usable_with_animacyAB_U$DUR_AND) #NS
t.test(Data_usable_with_animacyAB_P$DUR_AND,Data_usable_with_animacyAB_I$DUR_AND) #SIG

#NO DIFFERENCE OVERALL IN RELATED VS UNRELATED, SIGNIFICANT FOR ANIMACY THOUGH (PEOPLE VS ITEMS)

#t-tests for related vs unrelated people and then related vs unrelated items: DUR_AND
t.test(Data_usable_with_animacyAB_RP$DUR_AND,Data_usable_with_animacyAB_UP$DUR_AND) #NS
t.test(Data_usable_with_animacyAB_RI$DUR_AND,Data_usable_with_animacyAB_UI$DUR_AND) #NS

#t-test for animacy (ie comparing related people to related items, unrelated people vs unrelated items)
t.test(Data_usable_with_animacyAB_RP$DUR_AND,Data_usable_with_animacyAB_RI$DUR_AND) #NS
t.test(Data_usable_with_animacyAB_UP$DUR_AND,Data_usable_with_animacyAB_UI$DUR_AND) #SIG

mean(Data_usable_with_animacyAB_UP$DUR_AND)
mean(Data_usable_with_animacyAB_UI$DUR_AND)
```

T tests for DUR_NP3

```{r}
#t-tests for related vs unrelated people and then related vs unrelated items: DUR_NP3
t.test(Data_usable_with_animacyAB_P$DUR_NP3,Data_usable_with_animacyAB_I$DUR_NP3) #NS
t.test(Data_usable_with_animacyAB_R$DUR_NP3,Data_usable_with_animacyAB_U$DUR_NP3) #sig

t.test(Data_usable_with_animacyAB_RP$DUR_NP3,Data_usable_with_animacyAB_UP$DUR_NP3) #sig
t.test(Data_usable_with_animacyAB_RI$DUR_NP3,Data_usable_with_animacyAB_UI$DUR_NP3) #NS

t.test(Data_usable_with_animacyAB_RP$DUR_NP3,Data_usable_with_animacyAB_RI$DUR_NP3) #NS
t.test(Data_usable_with_animacyAB_UP$DUR_NP3,Data_usable_with_animacyAB_UI$DUR_NP3) #NS
```

T tests for DUR_NP1 (all NS)

```{r}
#t-tests for related vs unrelated people and then related vs unrelated items: DUR_NP1
t.test(Data_usable_with_animacyAB_RP$DUR_NP1,Data_usable_with_animacyAB_UP$DUR_NP1) #NS
t.test(Data_usable_with_animacyAB_RI$DUR_NP1,Data_usable_with_animacyAB_UI$DUR_NP1) #NS

t.test(Data_usable_with_animacyAB_RP$DUR_NP1,Data_usable_with_animacyAB_RI$DUR_NP1) #NS
t.test(Data_usable_with_animacyAB_UP$DUR_NP1,Data_usable_with_animacyAB_UI$DUR_NP1) #NS

t.test(Data_usable_with_animacyAB_R$DUR_NP1,Data_usable_with_animacyAB_U$DUR_NP1) #NS
t.test(Data_usable_with_animacyAB_P$DUR_NP1,Data_usable_with_animacyAB_I$DUR_NP1) #NS
```

item averages as a scatterplot for pmi-duration and cos-duration sets

```{r}
Data_useable_peopleAB <- Data_useable_peopleAB %>% mutate(Anchor_Other = paste(Anchor, SecondThing, sep = '_'))
Data_useable_itemsAB <- Data_useable_itemsAB %>% mutate(Anchor_Other = paste(Anchor, SecondThing, sep = '_'))
Data_useable_with_animacyAB <- Data_useable_with_animacyAB %>% mutate(Anchor_Other = paste(Anchor, SecondThing, sep = '_'))

item_means_all_but_no_Cos <-
  Data_useable_with_animacyAB %>%
  group_by(Anchor_Other, Cos, Cooc, PMI, Condition) %>%
  summarise_at(.vars = vars(DUR_NP1,DUR_NP2,DUR_AND,DUR_NP3),
               .funs = c(Mean="mean", Sd="sd"),
               na.rm = TRUE)
item_means_all_but_no_Cos

item_means_people_only <-
  Data_useable_peopleAB %>%
  group_by(Anchor_Other, Cos, Cooc, PMI, Condition) %>%
  summarise_at(.vars = vars(DUR_NP1,DUR_NP2,DUR_AND,DUR_NP3),
               .funs = c(Mean="mean", Sd="sd"),
               na.rm = TRUE)
item_means_people_only

item_means_items_only <-
  Data_useable_itemsAB %>%
  group_by(Anchor_Other, Cooc, PMI, Condition) %>%
  summarise_at(.vars = vars(DUR_NP1,DUR_NP2,DUR_AND,DUR_NP3),
               .funs = c(Mean="mean", Sd="sd"),
               na.rm = TRUE)
item_means_items_only
```

plotting duration by item means for various variables - function to make plots
```{r}
plot_dur_item_means <- function(your_data, x_data, y_data, color_points_by, point_label, v, plotxlab, plotylab, plottitle, legendtitle, ylims, xlims, scale_y_by, scale_x_by){
  the_plot =
  ggplot(your_data, aes(x = x_data, y = y_data, color = color_points_by)) +
  #geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  scale_color_manual(values = v) +
  geom_point(size = 2) +
  theme_classic() +
  geom_text_repel(aes(label = point_label), max.overlaps = Inf) +
  coord_cartesian(ylim=ylims) + 
  coord_cartesian(xlim=xlims) + 
  scale_y_continuous(breaks=scale_y_by) +
  scale_x_continuous(breaks=scale_x_by) +
  labs(x = plotxlab, y = plotylab, title = plottitle, color = legendtitle)  +
  ggeasy::easy_center_title()
the_plot
}
```

plotting pmi and saving as pdf

```{r, eval = FALSE}
#Pmis for all items
pdf(file = "DURNP1_PMI.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_all_but_no_Cos, item_means_all_but_no_Cos$PMI, item_means_all_but_no_Cos$DUR_NP1_Mean, item_means_all_but_no_Cos$Condition, item_means_all_but_no_Cos$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033", "RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average NP1 Duration (s)","PMI & Duration 1", "Condition", c(1.25, 2.75),c(.5, 5.5),seq(1.1,2.8,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURNP2_PMI.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_all_but_no_Cos, item_means_all_but_no_Cos$PMI, item_means_all_but_no_Cos$DUR_NP2_Mean, item_means_all_but_no_Cos$Condition, item_means_all_but_no_Cos$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033", "RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average NP2 Duration (s)","PMI & Duration 2", "Condition", c(0, 1.75),c(.5, 5.5),seq(.5,1.7,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURAND_PMI.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_all_but_no_Cos, item_means_all_but_no_Cos$PMI, item_means_all_but_no_Cos$DUR_AND_Mean, item_means_all_but_no_Cos$Condition, item_means_all_but_no_Cos$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033", "RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average And Duration (s)","PMI & Duration AND", "Condition", c(0, .75),c(.5, 5.5),seq(0,.8,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURNP3_PMI.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_all_but_no_Cos, item_means_all_but_no_Cos$PMI, item_means_all_but_no_Cos$DUR_NP3_Mean, item_means_all_but_no_Cos$Condition, item_means_all_but_no_Cos$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033", "RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average NP3 Duration (s)","PMI & Duration 3", "Condition", c(0, 1.75),c(.5, 5.5),seq(.5,1.7,.1), seq(.5,5.5,.5))
dev.off()

#cosine for anchor-second person pairs
pdf(file = "DURNP1_Cos.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$Cos, item_means_people_only$DUR_NP1_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Cosine", "Average NP1 Duration (s)","Cosine & Duration 1", "Condition", c(0, 1.75),c(0, 1),seq(.5,1.7,.1), seq(0,1,.1))
dev.off()

pdf(file = "DURNP2_Cos.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$Cos, item_means_people_only$DUR_NP2_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Cosine", "Average NP2 Duration (s)","Cosine & Duration 2", "Condition", c(0, 1.75),c(0, 1),seq(.5,1.7,.1), seq(0,1,.1))
dev.off()

pdf(file = "DURAND_Cos.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$Cos, item_means_people_only$DUR_AND_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Cosine", "Average AND Duration (s)","Cosine & Duration AND", "Condition", c(0, 1.75),c(0, 1),seq(.5,1.7,.1), seq(0,1,.1))
dev.off()

pdf(file = "DURNP3_Cos.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$Cos, item_means_people_only$DUR_NP3_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Cosine", "Average NP3 Duration (s)","Cosine & Duration 3", "Condition", c(0, 1.75),c(0, 1),seq(.5,1.7,.1), seq(0,1,.1))
dev.off()

#pmi for anchor-item pairs only
pdf(file = "DURNP1_PMIpeopleitem.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, item_means_items_only$PMI, item_means_items_only$DUR_NP1_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average NP1 Duration (s)","PMI & Duration 1", "Condition", c(1.25, 2.75),c(.5, 5.5),seq(1.1,2.8,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURNP2_PMIpeopleitem.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, item_means_items_only$PMI, item_means_items_only$DUR_NP2_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average NP2 Duration (s)","PMI & Duration 2", "Condition", c(0, 1.75),c(.5, 5.5),seq(.5,1.7,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURAND_PMIpeopleitem.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, item_means_items_only$PMI, item_means_items_only$DUR_AND_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average And Duration (s)","PMI & Duration AND", "Condition", c(0, .75),c(.5, 5.5),seq(0,.8,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURNP3_PMIpeopleitems.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, item_means_items_only$PMI, item_means_items_only$DUR_NP3_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "PMI", "Average NP3 Duration (s)","PMI & Duration 3", "Condition", c(0, 1.75),c(.5, 5.5),seq(.5,1.7,.1), seq(.5,5.5,.5))
dev.off()

#pmi for anchor-second person pairs only
pdf(file = "DURNP1_PMIpeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$PMI, item_means_people_only$DUR_NP1_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "PMI", "Average NP1 Duration (s)","PMI & Duration 1", "Condition", c(1.25, 2.75),c(.5, 5.5),seq(1.1,2.8,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURNP2_PMIpeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$PMI, item_means_people_only$DUR_NP2_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "PMI", "Average NP2 Duration (s)","PMI & Duration 2", "Condition", c(0, 1.75),c(.5, 5.5),seq(.5,1.7,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURAND_PMIpeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$PMI, item_means_people_only$DUR_AND_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "PMI", "Average And Duration (s)","PMI & Duration AND", "Condition", c(0, .75),c(.5, 5.5),seq(0,.8,.1), seq(.5,5.5,.5))
dev.off()

pdf(file = "DURNP3_PMIpeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, item_means_people_only$PMI, item_means_people_only$DUR_NP3_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "PMI", "Average NP3 Duration (s)","PMI & Duration 3", "Condition", c(0, 1.75),c(.5, 5.5),seq(.5,1.7,.1), seq(.5,5.5,.5))
dev.off()
```

Co-occurrence graphs, have to do x axis in log space

```{r, eval = FALSE}
#cooccurrence for anchor-item pairs only
#pdf(file = "DURNP1_Co-occurrencepeopleitem.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, log(item_means_people_only$Cooc), item_means_items_only$DUR_NP1_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "Co-occurrence", "Average NP1 Duration (s)","Co-occurrence & Duration 1", "Condition", c(1.25, 2.75),c(-2,10),seq(1.1,2.8,.1), seq(-2,10,1))
#dev.off()

#pdf(file = "DURNP2_Co-occurrencepeopleitem.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, log(item_means_people_only$Cooc), item_means_items_only$DUR_NP2_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "Co-occurrence", "Average NP2 Duration (s)","Co-occurrence & Duration 2", "Condition", c(-15, 1.75),c(-20,10),seq(.5,1.7,.1), seq(-20,10,1))
#dev.off()

#pdf(file = "DURAND_Co-occurrencepeopleitem.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, log(item_means_people_only$Cooc), item_means_items_only$DUR_AND_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "Co-occurrence", "Average And Duration (s)","PMI & Duration AND", "Condition", c(0, .75),c(-2,10),seq(0,.8,.1), seq(-2,10,1))
#dev.off()

#pdf(file = "DURNP3_Co-occurrencepeopleitems.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_items_only, log(item_means_people_only$Cooc), item_means_items_only$DUR_NP3_Mean, item_means_items_only$Condition, item_means_items_only$Anchor_Other, c("RI"="#6699FF", "UI" = "#FF9966"), "Co-occurrence", "Average NP3 Duration (s)","PMI & Duration 3", "Condition", c(0, 1.75),c(-2,10),seq(.5,1.7,.1), seq(-2,10,1))
#dev.off()

#cooccurrence for anchor-second person pairs only
#pdf(file = "DURNP1_Co-occurrencepeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, log(item_means_people_only$Cooc), item_means_people_only$DUR_NP1_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Co-occurrence", "Average NP1 Duration (s)","Co-occurrence & Duration 1", "Condition", c(1.25, 2.75),c(-2,10),seq(1.1,2.8,.1), seq(-2,10,1))
#dev.off()

#pdf(file = "DURNP2_Co-occurrencepeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, log(item_means_people_only$Cooc), item_means_people_only$DUR_NP2_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Co-occurrence", "Average NP2 Duration (s)","Co-occurrence & Duration 2", "Condition", c(0, 1.75),c(-2,10),seq(.5,1.7,.1), seq(-2,10,1))
#dev.off()

#pdf(file = "DURAND_Co-occurrencepeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, log(item_means_people_only$Cooc), item_means_people_only$DUR_AND_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Co-occurrence", "Average And Duration (s)","Co-occurrence & Duration AND", "Condition", c(0, .75),c(-2,10),seq(0,.8,.1), seq(-2,10,1))
#dev.off()

#pdf(file = "DURNP3_Co-occurrencepeoplepeople.pdf", width = 15, height = 10) 
plot_dur_item_means(item_means_people_only, log(item_means_people_only$Cooc), item_means_people_only$DUR_NP3_Mean, item_means_people_only$Condition, item_means_people_only$Anchor_Other, c("RP" = "#3300CC", "UP"="#CC0033"), "Co-occurrence", "Average NP3 Duration (s)","Co-occurrence & Duration 3", "Condition", c(0, 1.75),c(-2,10),seq(.5,1.7,.1), seq(-2,10,1))
#dev.off()
```

Exclusions by condition

```{r}
#Total proportion excluded
Total_excludedAB <- nrow(DataAB) - nrow(Data_useable_with_animacyAB)
Total_excluded_propAB <- Total_excludedAB/nrow(DataAB); Total_excluded_propAB #30.49% of all trials excluded

#By relatedness
Excluded_RelatedAB <- length(which(DataAB$Condition == "RI" | DataAB$Condition == "RP")) - length(which(Data_useable_with_animacyAB$Condition == "RI" | Data_useable_with_animacyAB$Condition == "RP"))
Excluded_UnrelatedAB <- length(which(DataAB$Condition == "UI" | DataAB$Condition == "UP")) - length(which(Data_useable_with_animacyAB$Condition == "UI" | Data_useable_with_animacyAB$Condition == "UP"))

Excluded_Related_propAB <- Excluded_RelatedAB / length(which(DataAB$Condition == "RI" | DataAB$Condition == "RP")) ; Excluded_Related_propAB #0.3137
Excluded_Unrelated_propAB <- Excluded_UnrelatedAB / length(which(DataAB$Condition == "UI" | DataAB$Condition == "UP")) ; Excluded_Unrelated_propAB #0.2967

#Exclusions by people and items
Excluded_ItemsAB <- length(which(DataAB$Condition == "RI" | DataAB$Condition == "UI")) - length(which(Data_useable_with_animacyAB$Condition == "RI" | Data_useable_with_animacyAB$Condition == "UI"))
Excluded_PeopleAB <- length(which(DataAB$Condition == "RP" | DataAB$Condition == "UP")) - length(which(Data_useable_with_animacyAB$Condition == "RP" | Data_useable_with_animacyAB$Condition == "UP"))
Excluded_Items_propAB <- Excluded_ItemsAB / length(which(DataAB$Condition == "RI" | DataAB$Condition == "UI")) ; Excluded_Items_propAB #27.98
Excluded_People_propAB <- Excluded_PeopleAB / length(which(DataAB$Condition == "RP" | DataAB$Condition == "UP")) ; Excluded_People_propAB #33.01

#Excluded trials by condition - should be the difference between original trials in data and trials in filtered data
Excluded_RIAB <- length(which(DataAB$Condition == "RI")) - length(which(Data_useable_with_animacyAB$Condition == "RI")); Excluded_RIAB #74
Excluded_RPAB <- length(which(DataAB$Condition == "RP")) - length(which(Data_useable_with_animacyAB$Condition == "RP")); Excluded_RPAB #86
Excluded_UIAB <- length(which(DataAB$Condition == "UI")) - length(which(Data_useable_with_animacyAB$Condition == "UI")); Excluded_UIAB #69
Excluded_UPAB <- length(which(DataAB$Condition == "UP")) - length(which(Data_useable_with_animacyAB$Condition == "UP")); Excluded_UPAB #82

#Interesting- relatedness does not seem to matter, but people excluded more than items
#Pretty typical exclusion proportions for psycholinguistics, especially relative clauses
Excluded_RI_propAB <- Excluded_RIAB/length(which(DataAB$Condition == "RI"));Excluded_RI_propAB #0.2884615 for RC, 0.2901961 here
Excluded_RP_propAB <- Excluded_RPAB/length(which(DataAB$Condition == "RP"));Excluded_RP_propAB #0.3515625 for RC, 0.3372549 here
Excluded_UI_propAB <- Excluded_UIAB/length(which(DataAB$Condition == "UI"));Excluded_UI_propAB #0.2834646 for RC, 0.2695312 here
Excluded_UP_propAB <- Excluded_UPAB/length(which(DataAB$Condition == "UP"));Excluded_UP_propAB #0.384 for RC, 0.3228346 here

test_people_itemsAB <- (Excluded_Items_propAB - Excluded_People_propAB )/
  sqrt( (Total_excluded_propAB * (1-Total_excluded_propAB) * ( (1/length(which(DataAB$Condition == "RI" | DataAB$Condition == "UI")) + 1/length(which(DataAB$Condition == "RP" | DataAB$Condition == "UP"))))) )
test_people_itemsAB # - 1.741822

test_related_unrelatedAB <- (Excluded_Related_propAB - Excluded_Unrelated_propAB )/
  sqrt( (Total_excluded_propAB * (1-Total_excluded_propAB) * ( (1/length(which(DataAB$Condition == "RI" | DataAB$Condition == "RP")) + 1/length(which(DataAB$Condition == "UI" | DataAB$Condition == "UP"))))) )
test_related_unrelatedAB # 0.6121238

test_related_person_related_itemsAB <- (Excluded_RI_propAB - Excluded_RP_propAB )/
  sqrt( (Excluded_Related_propAB * (1-Excluded_Related_propAB) * ( (1/length(which(DataAB$Condition == "RI")) + 1/length(which(DataAB$Condition == "RP"))))) )
test_related_person_related_itemsAB # -1.145176

test_unrelated_person_unrelated_itemsAB <- (Excluded_UI_propAB - Excluded_UP_propAB )/
  sqrt( (Excluded_Unrelated_propAB * (1-Excluded_Unrelated_propAB) * ( (1/length(which(DataAB$Condition == "UI")) + 1/length(which(DataAB$Condition == "UP"))))) )
test_unrelated_person_unrelated_itemsAB # -1.318382
```


using Boyce, Futrell, Levy 2020 log transformation of DV - only model specification that will converge

```{r}
Data_useable_peopleAB <- Data_useable_peopleAB %>% mutate(Syllables_XY = Data_useable_peopleAB$Nsyl_P2 + Data_useable_peopleAB$Nsyl_P3)
Data_useable_itemsAB <- Data_useable_itemsAB %>% mutate(Syllables_XY = Data_useable_itemsAB$Nsyl_P2 + Data_useable_itemsAB$Nsyl_P3)
Data_useable_with_animacyAB <- Data_useable_with_animacyAB %>% mutate(Syllables_XY = Data_useable_with_animacyAB$Nsyl_P2 + Data_useable_with_animacyAB$Nsyl_P3)

Data_useable_peopleAB$cSyllables_XY <- Data_useable_peopleAB$Syllables_XY - mean(Data_useable_peopleAB$Syllables_XY)
Data_useable_itemsAB$cSyllables_XY <- Data_useable_itemsAB$Syllables_XY - mean(Data_useable_peopleAB$Syllables_XY)
Data_useable_with_animacyAB$cSyllables_XY <- Data_useable_with_animacyAB$Syllables_XY - mean(Data_useable_with_animacyAB$Syllables_XY)

Data_useable_peopleAB$xcSyllables_XY <- Data_useable_peopleAB$cSyllables_XY / sd(Data_useable_peopleAB$Syllables_XY)
Data_useable_itemsAB$xcSyllables_XY <- Data_useable_itemsAB$cSyllables_XY / sd(Data_useable_peopleAB$Syllables_XY)
Data_useable_with_animacyAB$xcSyllables_XY <- Data_useable_with_animacyAB$cSyllables_XY / sd(Data_useable_with_animacyAB$Syllables_XY)

Data_useable_peopleABRP <- Data_useable_peopleAB %>% filter(Data_useable_peopleAB$Condition == "RP")
Data_useable_peopleABUP <- Data_useable_peopleAB %>% filter(Data_useable_peopleAB$Condition == "UP")

Data_useable_peopleAB_no_gymnast <- Data_useable_peopleAB %>% filter(Anchor != "gymnast")
Data_useable_peopleABRP_no_gymnast <- Data_useable_peopleABRP %>% filter(Anchor != "gymnast")

Data_useable_peopleAB_short_syls <- Data_useable_peopleAB %>% filter(Syllables_XY < 4)
Data_useable_peopleAB_long_syls <- Data_useable_peopleAB_no_gymnast %>% filter(Syllables_XY >= 4)

DUR_X_to_Y_modPPL_logDV <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB, REML = FALSE)
DUR_X_to_Y_modPPL_logDV2 <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * item_order + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB, REML = FALSE)

plot_model(DUR_X_to_Y_modPPL_logDV, type = "int")
make_nice_table(DUR_X_to_Y_modPPL_logDV, "DUR_X_to_Y_modPPL_logDV.docx")
make_nice_table(DUR_X_to_Y_modPPLquant_logDV, "DUR_X_to_Y_modPPLquant_logDV.docx")

DUR_X_to_Y_modPPLquant_logDV <- 
  lmer(log(DUR_X_to_Y) ~ xcPMI * xcCos * xcSyllables_XY  + (1+xcCos|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB, REML = FALSE)
DUR_X_to_Y_modPPLquant_logDV2 <- 
  lmer(log(DUR_X_to_Y) ~ xcPMI * xcCos * xcSyllables_XY * item_order  + (1+xcCos|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB, REML = FALSE)

DUR_X_to_Y_modItems_logDV <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY  + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE)
DUR_X_to_Y_modItems_logDV2 <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE)

DUR_X_to_Y_modItemsquant_logDV <- 
  lmer(log(DUR_X_to_Y) ~ xcPMI * xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing significant with or without item order
DUR_X_to_Y_modItemsquant_logDV2 <- 
  lmer(log(DUR_X_to_Y) ~ xcPMI * xcSyllables_XY * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing significant with or without item order

#make_nice_table(DUR_X_to_Y_modItems_logDV, "DUR_X_to_Y_modItems_logDV.docx")
#make_nice_table(DUR_X_to_Y_modItemsquant_logDV, "DUR_X_to_Y_modItemsquant_logDV.docx")

summary(DUR_X_to_Y_modItems_logDV)
summary(DUR_X_to_Y_modItemsquant_logDV)

summary(DUR_X_to_Y_modPPL_logDV)
summary(DUR_X_to_Y_modPPL_logDV2)

summary(DUR_X_to_Y_modPPLquant_logDV)
summary(DUR_X_to_Y_modPPLquant_logDV2)

summary(DUR_X_to_Y_modItemsquant_logDV)
summary(DUR_X_to_Y_modItemsquant_logDV2)
summary(DUR_X_to_Y_modItems_logDV)
summary(DUR_X_to_Y_modItems_logDV2)

DUR_X_to_Y_modPPL_logDV_no_item_order_NA <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * xcNA1 * xcNA2 + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB, REML = FALSE)
DUR_X_to_Y_modItems_logDV_no_item_order_NA <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * xcNA1 * xcNA2 + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE)

summary(DUR_X_to_Y_modPPL_logDV_no_item_order_NA)
summary(DUR_X_to_Y_modItems_logDV_no_item_order_NA)


DUR_X_to_Y_modPPL_logDV_no_item_order_no_gymnast <- 
  lmer(log(DUR_X_to_Y) ~ related_yes *  xcSyllables_XY + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_no_gymnast, REML = FALSE)
summary(DUR_X_to_Y_modPPL_logDV_no_item_order_no_gymnast)

#subsetting by 2-3 vs 4+ syllables
DUR_X_to_Y_modPPL_logDV_no_item_order_shortsyl <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_short_syls, REML = FALSE)
DUR_X_to_Y_modPPL_logDV_no_item_order_longsyl <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_long_syls, REML = FALSE)
DUR_X_to_Y_modPPL_logDV_no_item_order_shortsyl2 <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_short_syls, REML = FALSE)
DUR_X_to_Y_modPPL_logDV_no_item_order_longsyl2 <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_long_syls, REML = FALSE)


summary(DUR_X_to_Y_modPPL_logDV_no_item_order_shortsyl)
summary(DUR_X_to_Y_modPPL_logDV_no_item_order_longsyl)
summary(DUR_X_to_Y_modPPL_logDV_no_item_order_shortsyl2)
summary(DUR_X_to_Y_modPPL_logDV_no_item_order_longsyl2)

#subsetting by RP vs UP to see where the difference is
DUR_X_to_Y_modPPL_logDV_no_item_orderRP<- 
  lmer(log(DUR_X_to_Y) ~ xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleABRP, REML = FALSE) #here
DUR_X_to_Y_modPPL_logDV_no_item_orderUP <- 
  lmer(log(DUR_X_to_Y) ~ xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleABUP, REML = FALSE)

summary(DUR_X_to_Y_modPPL_logDV_no_item_orderRP)
summary(DUR_X_to_Y_modPPL_logDV_no_item_orderUP)

#what if you remove ballerina from RP only model?
DUR_X_to_Y_modPPL_logDV_no_item_orderRP_noballerina<- 
  lmer(log(DUR_X_to_Y) ~ xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleABRP_no_gymnast, REML = FALSE) 
summary(DUR_X_to_Y_modPPL_logDV_no_item_orderRP_noballerina)

mean(Data_useable_peopleAB$Nsyl_P2)
mean(Data_useable_peopleAB$Nsyl_P3)
t.test(Data_useable_peopleAB$Nsyl_P2,Data_useable_peopleAB$Nsyl_P3)

mean(LookupTable$NsylRP)
mean(LookupTable$NsylUP)



summary(DUR_X_to_Y_modPPL_logDV)
summary(DUR_X_to_Y_modItems_logDV)
summary(DUR_X_to_Y_modPPLquant_logDV)
summary(DUR_X_to_Y_modItemsquant_logDV)

DUR_X_to_Y_modPPL_logDV_no_item_order <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB, REML = FALSE)
DUR_X_to_Y_modItems_logDV_no_item_order <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE)

summary(DUR_X_to_Y_modPPL_logDV_no_item_order)
summary(DUR_X_to_Y_modItems_logDV_no_item_order)

#Nothing - just a bunch of different models that have no effects
DUR_X_to_Y_modPPL_logDV_no_item_order_NA <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * xcNA1 * xcNA2 + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB, REML = FALSE)
DUR_X_to_Y_modItems_logDV_no_item_order_NA <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY * xcNA1 * xcNA2 + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE)


summary(DUR_X_to_Y_modPPL_logDV_no_item_order_NA)
summary(DUR_X_to_Y_modItems_logDV_no_item_order_NA)


DUR_X_to_Y_modPPL_logDV_no_item_order_no_gymnast <- 
  lmer(log(DUR_X_to_Y) ~ related_yes *  xcSyllables_XY + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_no_gymnast, REML = FALSE)
summary(DUR_X_to_Y_modPPL_logDV_no_item_order_no_gymnast)

#subsetting by 2-3 vs 4+ syllables
DUR_X_to_Y_modPPL_logDV_no_item_order_shortsyl <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_short_syls, REML = FALSE)
DUR_X_to_Y_modPPL_logDV_no_item_order_longsyl <- 
  lmer(log(DUR_X_to_Y) ~ related_yes * xcSyllables_XY + (1+related_yes|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleAB_long_syls, REML = FALSE)

summary(DUR_X_to_Y_modPPL_logDV_no_item_order_shortsyl)
summary(DUR_X_to_Y_modPPL_logDV_no_item_order_longsyl)

#subsetting by RP vs UP to see where the difference is
DUR_X_to_Y_modPPL_logDV_no_item_orderRP<- 
  lmer(log(DUR_X_to_Y) ~ xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleABRP, REML = FALSE) #here
DUR_X_to_Y_modPPL_logDV_no_item_orderUP <- 
  lmer(log(DUR_X_to_Y) ~ xcSyllables_XY + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_peopleABUP, REML = FALSE)

```

```{r}
#subsetting by RP vs UP to see where the difference is
DURNP1<- 
  lmer(log(DUR_NP1) ~ Condition + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE) #here
summary(DURNP1)

summary(lm(log(DUR_NP1) ~ Condition, data = Data_useable_with_animacyAB))

mean(Data_useable_with_animacyAB$DUR_NP1[which(Data_useable_with_animacyAB$Condition == "RP")])
mean(Data_useable_with_animacyAB$DUR_NP1[which(Data_useable_with_animacyAB$Condition == "RI")])
mean(Data_useable_with_animacyAB$DUR_NP1[which(Data_useable_with_animacyAB$Condition == "UP")])
mean(Data_useable_with_animacyAB$DUR_NP1[which(Data_useable_with_animacyAB$Condition == "UI")])
```

\~\~~~Simple models looking at only syllables vs only relatedness~~\~\~

SYLLABLE LENGTH

#models for just syllable length (centered and scaled) in people

```{r}
Data_useable_peopleAB <- Data_useable_peopleAB %>% mutate(DUR_AND_plus_NP3 = NP3_end-NP2_End)
Data_useable_itemsAB <- Data_useable_itemsAB %>% mutate(DUR_AND_plus_NP3 = NP3_end-NP2_End)
Data_useable_with_animacyAB <- Data_useable_with_animacyAB %>% mutate(DUR_AND_plus_NP3 = NP3_end - NP2_End)

DURNP2_modPPL_xcsyl <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG

DURAND_modPPL_xcsyl <- lmer(log(DUR_AND) ~
                     xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURNP3_modPPL_xcsyl <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG

DURANDNP3_modPPL_xcsyl <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG

DURNP2_modPPL_xcsyl2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG

DURAND_modPPL_xcsyl2 <- lmer(log(DUR_AND) ~
                     xcNsyl_P3*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURNP3_modPPL_xcsyl2 <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG

DURANDNP3_modPPL_xcsyl2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG
```

#models for just syllable length (centered & scaled) in items

```{r}
#singular even with simplest random effects structure
DURNP2_modITEMS_xcsyl <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURAND_modITEMS_xcsyl <- lmer(log(DUR_AND) ~
                     xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURNP3_modITEMS_xcsyl <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURANDNP3_modITEMS_xcsyl <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

# summary(DURNP2_modITEMS_xcsyl)
# summary(DURAND_modITEMS_xcsyl)
# summary(DURNP3_modITEMS_xcsyl)
# summary(DURANDNP3_modITEMS_xcsyl)

#singular even with simplest random effects structure
DURNP2_modITEMS_xcsyl2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURAND_modITEMS_xcsyl2 <- lmer(log(DUR_AND) ~
                     xcNsyl_P3*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURNP3_modITEMS_xcsyl2 <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURANDNP3_modITEMS_xcsyl2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

# summary(DURNP2_modITEMS_xcsyl2)
# summary(DURAND_modITEMS_xcsyl2)
# summary(DURNP3_modITEMS_xcsyl2)
# summary(DURANDNP3_modITEMS_xcsyl2)
```

COSINE PEOPLE #models for quantitative relatedness predictors (only cos) in people

```{r}
DURNP2_modPPL_xcCos <- lmer(log(DUR_NP2) ~ 
                     xcCos + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURAND_modPPL_xcCos <- lmer(log(DUR_AND) ~
                     xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURNP3_modPPL_xcCos <- lmer(log(DUR_NP3) ~
                     xcCos + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction

DURANDNP3_modPPL_xcCos <- lmer(log(DUR_AND_plus_NP3) ~
                     xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

# summary(DURNP2_modPPL_xcCos)
# summary(DURAND_modPPL_xcCos)
# summary(DURNP3_modPPL_xcCos)
# summary(DURANDNP3_modPPL_xcCos)

DURNP2_modPPL_xcCos2 <- lmer(log(DUR_NP2) ~ 
                     xcCos*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURAND_modPPL_xcCos2 <- lmer(log(DUR_AND) ~
                     xcCos*item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURNP3_modPPL_xcCos2 <- lmer(log(DUR_NP3) ~
                     xcCos*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction

DURANDNP3_modPPL_xcCos2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcCos*item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

# summary(DURNP2_modPPL_xcCos2)
# summary(DURAND_modPPL_xcCos2)
# summary(DURNP3_modPPL_xcCos2)
# summary(DURANDNP3_modPPL_xcCos2)
```

PMI PEOPLE AND ITEMS

#models for quantitative relatedness predictors (PMI only) in people

```{r}
DURNP2_modPPL_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURAND_modPPL_xcPMI <- lmer(log(DUR_AND) ~
                     xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURNP3_modPPL_xcPMI <- lmer(log(DUR_NP3) ~
                     xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction

DURANDNP3_modPPL_xcPMI <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

# summary(DURNP2_modPPL_xcPMI)
# summary(DURAND_modPPL_xcPMI)
# summary(DURNP3_modPPL_xcPMI)
# summary(DURANDNP3_modPPL_xcPMI)

DURNP2_modPPL_xcPMI2 <- lmer(log(DUR_NP2) ~ 
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURAND_modPPL_xcPMI2 <- lmer(log(DUR_AND) ~
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURNP3_modPPL_xcPMI2 <- lmer(log(DUR_NP3) ~
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction

DURANDNP3_modPPL_xcPMI2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

# summary(DURNP2_modPPL_xcPMI2)
# summary(DURAND_modPPL_xcPMI2)
# summary(DURNP3_modPPL_xcPMI2)
# summary(DURANDNP3_modPPL_xcPMI2)
```

#models for quantitiative relatedness predictors in items (PMI only b/c items)

```{r}
DURNP2_modITEMS_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcPMI + (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #xcPMI sig

DURAND_modITEMS_xcPMI <- lmer(log(DUR_AND) ~
                     xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI sig

DURNP3_modITEMS_xcPMI <- lmer(log(DUR_NP3) ~
                     xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURANDNP3_modITEMS_xcPMI <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

# summary(DURNP2_modITEMS_xcPMI)
# summary(DURAND_modITEMS_xcPMI)
# summary(DURNP3_modITEMS_xcPMI)
# summary(DURANDNP3_modITEMS_xcPMI)

DURNP2_modITEMS_xcPMI2 <- lmer(log(DUR_NP2) ~ 
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI sig

DURAND_modITEMS_xcPMI2 <- lmer(log(DUR_AND) ~
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI sig

DURNP3_modITEMS_xcPMI2 <- lmer(log(DUR_NP3) ~
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURANDNP3_modITEMS_xcPMI2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

# summary(DURNP2_modITEMS_xcPMI2)
# summary(DURAND_modITEMS_xcPMI2)
# summary(DURNP3_modITEMS_xcPMI2)
# summary(DURANDNP3_modITEMS_xcPMI2)
```

COSINE AND PMI IN PEOPLE

#models for quantitative relatedness predictors (PMI, cosine) in people

```{r}
DURNP2_modPPL_xcPMI_xcCos <- lmer(log(DUR_NP2) ~ 
                     xcPMI * xcCos + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURAND_modPPL_xcPMI_xcCos  <- lmer(log(DUR_AND) ~
                     xcPMI * xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURNP3_modPPL_xcPMI_xcCos <- lmer(log(DUR_NP3) ~
                     xcPMI*xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction

DURANDNP3_modPPL_xcPMI_xcCos <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI*xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

# summary(DURNP2_modPPL_xcPMI_xcCos)
# summary(DURAND_modPPL_xcPMI_xcCos)
# summary(DURNP3_modPPL_xcPMI_xcCos)
# summary(DURANDNP3_modPPL_xcPMI_xcCos)

DURNP2_modPPL_xcPMI_xcCos2 <- lmer(log(DUR_NP2) ~ 
                     xcPMI * xcCos *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURAND_modPPL_xcPMI_xcCos2 <- lmer(log(DUR_AND) ~
                     xcPMI * xcCos * item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

DURNP3_modPPL_xcPMI_xcCos2 <- lmer(log(DUR_NP3) ~
                     xcPMI*xcCos * item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction

DURANDNP3_modPPL_xcPMI_xcCos2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI*xcCos* item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig

# summary(DURNP2_modPPL_xcPMI_xcCos2)
# summary(DURAND_modPPL_xcPMI_xcCos2)
# summary(DURNP3_modPPL_xcPMI_xcCos2)
# summary(DURANDNP3_modPPL_xcPMI_xcCos2)
```

RELATEDNESS CONTRAST CODED

#models for contrast coded relatedness in people

```{r}
DURNP2_modPPL_contrast_relatedness <- lmer(log(DUR_NP2) ~ 
                    related_yes + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

#needed rs removed to converge
DURAND_modPPL_contrast_relatedness <- lmer(log(DUR_AND) ~
                     related_yes + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS, singular

DURNP3_modPPL_contrast_relatedness <- lmer(log(DUR_NP3) ~
                     related_yes + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #sig

DURANDNP3_modPPL_contrast_relatedness <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #sig

# summary(DURNP2_modPPL_contrast_relatedness)
# summary(DURAND_modPPL_contrast_relatedness)
# summary(DURNP3_modPPL_contrast_relatedness)
# summary(DURANDNP3_modPPL_contrast_relatedness)

DURNP2_modPPL_contrast_relatedness2 <- lmer(log(DUR_NP2) ~ 
                    related_yes*item_order + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

#needed RS removed to converge
DURAND_modPPL_contrast_relatedness2 <- lmer(log(DUR_AND) ~
                     related_yes*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS, singular

DURNP3_modPPL_contrast_relatedness2 <- lmer(log(DUR_NP3) ~
                     related_yes*item_order + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #sig

DURANDNP3_modPPL_contrast_relatedness2 <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*item_order + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #sig

# summary(DURNP2_modPPL_contrast_relatedness2)
# summary(DURAND_modPPL_contrast_relatedness2)
# summary(DURNP3_modPPL_contrast_relatedness2)
# summary(DURANDNP3_modPPL_contrast_relatedness2)
```

#models for contrast coded relatedness in items with and without item order

```{r}
#singular with even the simplest random effects structure
DURNP2_modITEMS_contrast_relatedness <- lmer(log(DUR_NP2) ~ 
                    related_yes + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURAND_modITEMS_contrast_relatedness <- lmer(log(DUR_AND) ~
                     related_yes + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURNP3_modITEMS_contrast_relatedness <- lmer(log(DUR_NP3) ~
                     related_yes + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURANDNP3_modITEMS_contrast_relatedness <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

#summary(DURNP2_modITEMS_contrast_relatedness)
#summary(DURAND_modITEMS_contrast_relatedness)
#summary(DURNP3_modITEMS_contrast_relatedness)
#summary(DURANDNP3_modITEMS_contrast_relatedness)

#singular with even the simplest random effects structre
DURNP2_modITEMS_contrast_relatedness2 <- lmer(log(DUR_NP2) ~ 
                    related_yes*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURAND_modITEMS_contrast_relatedness2 <- lmer(log(DUR_AND) ~
                     related_yes*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURNP3_modITEMS_contrast_relatedness2 <- lmer(log(DUR_NP3) ~
                     related_yes*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

DURANDNP3_modITEMS_contrast_relatedness2 <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #nothing sig

#summary(DURNP2_modITEMS_contrast_relatedness2)
#summary(DURAND_modITEMS_contrast_relatedness2)
#summary(DURNP3_modITEMS_contrast_relatedness2)
#summary(DURANDNP3_modITEMS_contrast_relatedness2)
```

NAME AGREEMENT

#models for just Name Agreement in People and then with item order

```{r}
#Name agreement never sig on its own
#adding in item order, no sig effects no interxns
DURNP2_modPPL_xcNA <- lmer(log(DUR_NP2) ~ 
                    xcNA1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURAND_modPPL_xcNA <- lmer(log(DUR_AND) ~
                     xcNA2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURNP3_modPPL_xcNA <- lmer(log(DUR_NP3) ~
                     xcNA2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURANDNP3_modPPL_xcNA <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNA2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURNP2_modPPL_xcNA2 <- lmer(log(DUR_NP2) ~ 
                    xcNA1*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURAND_modPPL_xcNA2 <- lmer(log(DUR_AND) ~
                     xcNA2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURNP3_modPPL_xcNA2 <- lmer(log(DUR_NP3) ~
                     xcNA2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURANDNP3_modPPL_xcNA2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNA2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

```

#models for just Name Agreement in items and then with item order

```{r}
#NA never sig on its own
#item order always sig when added, NA still never sig, no interxns
DURNP2_modITEMS_xcNA <- lmer(log(DUR_NP2) ~ 
                     xcNA1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

DURAND_modITEMS_xcNA <- lmer(log(DUR_AND) ~
                     xcNA2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

DURNP3_modITEMS_xcNA <- lmer(log(DUR_NP3) ~
                     xcNA2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

DURANDNP3_modITEMS_xcNA<- lmer(log(DUR_AND_plus_NP3) ~
                     xcNA2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

DURNP2_modITEMS_xcNA2 <- lmer(log(DUR_NP2) ~ 
                     xcNA1*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

DURAND_modITEMS_xcNA2 <- lmer(log(DUR_AND) ~
                     xcNA2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

DURNP3_modITEMS_xcNA2<- lmer(log(DUR_NP3) ~
                     xcNA2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

DURANDNP3_modITEMS_xcNA2<- lmer(log(DUR_AND_plus_NP3) ~
                     xcNA2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #NS

#summary(DURNP2_modITEMS_xcNA)
#summary(DURAND_modITEMS_xcNA)
#summary(DURNP3_modITEMS_xcNA)
#summary(DURANDNP3_modITEMS_xcNA)
#summary(DURNP2_modITEMS_xcNA2)
#summary(DURAND_modITEMS_xcNA2)
#summary(DURNP3_modITEMS_xcNA2)
#summary(DURANDNP3_modITEMS_xcNA2)
```

FREQUENCY

#models for just Frequency in People and then with item order

```{r}
#only dur2 sig when jsut frequency
#add in item order and you get interactions all over (except dur3, and still only dur 2 sig on freq)
#item order alone never sig
DURNP2_modPPL_xcFreq <- lmer(log(DUR_NP2) ~ 
                    xcFreq1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG

DURAND_modPPL_xcFreq <- lmer(log(DUR_AND) ~
                     xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURNP3_modPPL_xcFreq <- lmer(log(DUR_NP3) ~
                     xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURANDNP3_modPPL_xcFreq <- lmer(log(DUR_AND_plus_NP3) ~
                     xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

#summary(DURNP2_modPPL_xcFreq)
#summary(DURAND_modPPL_xcFreq)
#summary(DURNP3_modPPL_xcFreq)
#summary(DURANDNP3_modPPL_xcFreq)

DURNP2_modPPL_xcFreq2 <- lmer(log(DUR_NP2) ~ 
                    xcFreq1*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #SIG

DURAND_modPPL_xcFreq2 <- lmer(log(DUR_AND) ~
                     xcFreq2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURNP3_modPPL_xcFreq2 <- lmer(log(DUR_NP3) ~
                     xcFreq2 *item_order+ (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

DURANDNP3_modPPL_xcFreq2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcFreq2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #NS

#summary(DURNP2_modPPL_xcFreq2)
#summary(DURAND_modPPL_xcFreq2)
#summary(DURNP3_modPPL_xcFreq2)
#summary(DURANDNP3_modPPL_xcFreq2)
```

#models for just Frequency in in items and then with item order

```{r}
#Frequency never significant on its own
#Doesn't matter if random slope included or not
#Item order always significant when added
#No interactions

#singular with even the simplest random effects structure
DURNP2_modITEMS_xcFreq <- lmer(log(DUR_NP2) ~ 
                     xcFreq1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURAND_modITEMS_xcFreq <- lmer(log(DUR_AND) ~
                     xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURNP3_modITEMS_xcFreq <- lmer(log(DUR_NP3) ~
                     xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURANDNP3_modITEMS_xcFreq<- lmer(log(DUR_AND_plus_NP3) ~
                     xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

#summary(DURNP2_modITEMS_xcFreq)
#summary(DURAND_modITEMS_xcFreq)
#summary(DURNP3_modITEMS_xcFreq)
#summary(DURANDNP3_modITEMS_xcFreq)

#singular with even the simplest random effects structure
DURNP2_modITEMS_xcFreq2 <- lmer(log(DUR_NP2) ~ 
                     xcFreq1*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURAND_modITEMS_xcFreq2 <- lmer(log(DUR_AND) ~
                     xcFreq2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURNP3_modITEMS_xcFreq2 <- lmer(log(DUR_NP3) ~
                     xcFreq2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

DURANDNP3_modITEMS_xcFreq2<- lmer(log(DUR_AND_plus_NP3) ~
                     xcFreq2*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #SIG

#summary(DURNP2_modITEMS_xcFreq2)
#summary(DURAND_modITEMS_xcFreq2)
#summary(DURNP3_modITEMS_xcFreq2)
#summary(DURANDNP3_modITEMS_xcFreq2)
```

\~\~\~\~\~\~\~\~\~~~MORE COMPLEX MODELS~~\~\~\~\~\~\~\~\~

#xcCos & syllables centered & scaled - people

```{r}
DURNP2_modPPL_xcsyl_xcCos <- lmer(log(DUR_NP2) ~ 
                     xcCos*xcNsyl_P2+ (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modPPL_xcsyl_xcCos <- lmer(log(DUR_AND) ~
                     xcCos*xcNsyl_P3 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modPPL_xcsyl_xcCos <- lmer(log(DUR_NP3) ~
                     xcCos*xcNsyl_P3 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

#Needed RS removed to converge
DURANDNP3_modPPL_xcsyl_xcCos <- lmer(log(DUR_AND_plus_NP3) ~
                     xcCos*xcNsyl_P3  + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> nothing sig

#with item order
DURNP2_modPPL_xcsyl_xcCos2 <- lmer(log(DUR_NP2) ~ 
                     xcCos *item_order*xcNsyl_P2 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modPPL_xcsyl_xcCos2 <- lmer(log(DUR_AND) ~
                     xcCos *item_order*xcNsyl_P3 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modPPL_xcsyl_xcCos2 <- lmer(log(DUR_NP3) ~
                     xcCos *item_order *xcNsyl_P3+ (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modPPL_xcsyl_xcCos2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcCos *item_order*xcNsyl_P3 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> nothing sig
```

#xcPMI & syllables centered & scaled - people

```{r}
DURNP2_modPPL_xcsyl_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcPMI*xcNsyl_P2+ (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modPPL_xcsyl_xcPMI <- lmer(log(DUR_AND) ~
                     xcPMI*xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modPPL_xcsyl_xcPMI <- lmer(log(DUR_NP3) ~
                     xcPMI*xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modPPL_xcsyl_xcPMI <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI*xcNsyl_P3  + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> nothing sig

#with item order
DURNP2_modPPL_xcsyl_xcPMI2 <- lmer(log(DUR_NP2) ~ 
                     xcPMI*xcNsyl_P2 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modPPL_xcsyl_xcPMI2 <- lmer(log(DUR_AND) ~
                     xcPMI*xcNsyl_P3 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modPPL_xcsyl_xcPMI2 <- lmer(log(DUR_NP3) ~
                     xcPMI*xcNsyl_P3 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modPPL_xcsyl_xcPMI2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcPMI*xcNsyl_P3 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> nothing sig
```

#contrast coded relatedness & syllables centered & scaled - people

```{r}
DURNP2_modPPL_xcsyl_ryes <- lmer(log(DUR_NP2) ~ 
                     related_yes*xcNsyl_P2+ (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modPPL_xcsyl_ryes <- lmer(log(DUR_AND) ~
                     related_yes*xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modPPL_xcsyl_ryes <- lmer(log(DUR_NP3) ~
                     related_yes*xcNsyl_P3 + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modPPL_xcsyl_ryes <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*xcNsyl_P3  + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> nothing sig

#with item order
DURNP2_modPPL_xcsyl_ryes2 <- lmer(log(DUR_NP2) ~ 
                     related_yes*xcNsyl_P2 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modPPL_xcsyl_ryes2 <- lmer(log(DUR_AND) ~
                     related_yes*xcNsyl_P3 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modPPL_xcsyl_ryes2 <- lmer(log(DUR_NP3) ~
                     related_yes*xcNsyl_P3 *item_order + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modPPL_xcsyl_ryes2 <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*xcNsyl_P3 *item_order + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #Nothing sig -> nothing sig

summary(DURNP2_modPPL_xcsyl_ryes2)
summary(DURNP2_modPPL_xcsyl_ryes)
```

#xcPMI, xcCos, syllables centered & scaled - people

```{r}
DURNP2_modPPL_xcsyl_xcPMI_xcCos <- lmer(log(DUR_NP2) ~ 
                    xcNsyl_P2*xcPMI*xcCos + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #syl, PMI syl*PMI interxn sig

DURAND_modPPL_xcsyl_xcPMI_xcCos <- lmer(log(DUR_AND) ~
                    xcNsyl_P3*xcPMI*xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #cos, syl*Cos interxn sig *SAME*

DURNP3_modPPL_xcsyl_xcPMI_xcCos <- lmer(log(DUR_NP3) ~
                    xcNsyl_P3*xcPMI*xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only syllables, pmi*item_order sig *DIFF*

DURANDNP3_modPPL_xcsyl_xcPMI_xcCos <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcPMI*xcCos + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only cosine, pmi*item_order sig *DIFF*

#with item order
DURNP2_modPPL_xcsyl_xcPMI_xcCos2 <- lmer(log(DUR_NP2) ~ 
                    xcNsyl_P2*xcPMI*xcCos*item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #syl, PMI syl*PMI interxn sig

DURAND_modPPL_xcsyl_xcPMI_xcCos2 <- lmer(log(DUR_AND) ~
                    xcNsyl_P3*xcPMI*xcCos*item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #cos, syl*Cos interxn sig *SAME*

DURNP3_modPPL_xcsyl_xcPMI_xcCos2 <- lmer(log(DUR_NP3) ~
                    xcNsyl_P3*xcPMI*xcCos*item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only syllables, pmi*item_order sig *DIFF*

DURANDNP3_modPPL_xcsyl_xcPMI_xcCos2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcPMI*xcCos*item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only cosine, pmi*item_order sig *DIFF*


summary(DURNP2_modPPL_xcsyl_xcPMI_xcCos)
summary(DURNP2_modPPL_xcsyl_xcPMI_xcCos2)
summary(DURAND_modPPL_xcsyl_xcPMI_xcCos2)
```

#xcPMI, xcCos, syllables centered & scaled and frequency - people

```{r}
#centered & scaled
DURNP2_modPPL_xcsyl_xcFreq_xcPMI_xcCos <- lmer(log(DUR_NP2) ~ 
                    xcNsyl_P2*xcPMI*xcCos*xcFreq1 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #syl, PMI syl*PMI interxn sig

DURAND_modPPL_xcsyl_xcFreq_xcPMI_xcCos <- lmer(log(DUR_AND) ~
                    xcNsyl_P3*xcPMI*xcCos*xcFreq2 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #cos, syl*Cos interxn sig *SAME*

#Singular at even most simple random effects structure
DURNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos <- lmer(log(DUR_NP3) ~
                    xcNsyl_P3*xcPMI*xcCos*xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only syllables, pmi*item_order sig *DIFF*

DURANDNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcPMI*xcCos*xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only cosine, pmi*item_order sig *DIFF*

#with item order
DURNP2_modPPL_xcsyl_xcFreq_xcPMI_xcCos2 <- lmer(log(DUR_NP2) ~ 
                    xcNsyl_P2*xcPMI*xcCos*item_order*xcFreq1 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #syl, PMI syl*PMI interxn sig

DURAND_modPPL_xcsyl_xcFreq_xcPMI_xcCos2 <- lmer(log(DUR_AND) ~
                    xcNsyl_P3*xcPMI*xcCos*item_order*xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #cos, syl*Cos interxn sig *SAME*

#SINGULAR AT ANY RANDOM EFFECTS STRUCTURE
DURNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos2 <- lmer(log(DUR_NP3) ~
                    xcNsyl_P3*xcPMI*xcCos*item_order*xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only syllables, pmi*item_order sig *DIFF*
#SINGULAR AT ANY RANDOM EFFECTS STRUCTURE
DURANDNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcPMI*xcCos*item_order*xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB, REML = FALSE) #only cosine, pmi*item_order sig *DIFF*
```

#relatedness as contrast coded, xcNsyl, Frequency, with & without Item order - p3opl3

```{r}
DURNP2_modPPL_xcSyl_xcFreq_ryes <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes * xcFreq1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURAND_modPPL_xcSyl_xcFreq_ryes <- lmer(log(DUR_AND) ~ 
                     xcNsyl_P3 * related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURNP3_modPPL_xcSyl_xcFreq_ryes <- lmer(log(DUR_NP3) ~ 
                     xcNsyl_P3 * related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURANDNP3_modPPL_xcSyl_xcFreq_ryes <- lmer(log(DUR_AND_plus_NP3) ~ 
                     xcNsyl_P3 * related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 


DURNP2_modPPL_xcSyl_xcFreq_ryes2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes * xcFreq1 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURAND_modPPL_xcSyl_xcFreq_ryes2 <- lmer(log(DUR_AND) ~ 
                     xcNsyl_P3 * related_yes * xcFreq2 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURNP3_modPPL_xcSyl_xcFreq_ryes2 <- lmer(log(DUR_NP3) ~ 
                     xcNsyl_P3 * related_yes * xcFreq2 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURANDNP3_modPPL_xcSyl_xcFreq_ryes2 <- lmer(log(DUR_AND_plus_NP3) ~ 
                     xcNsyl_P3 * related_yes * xcFreq2 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

# summary(DURNP2_modPPL_xcSyl_xcFreq) 
# summary(DURAND_modPPL_xcSyl_xcFreq) 
# summary(DURNP3_modPPL_xcSyl_xcFreq) 
# summary(DURANDNP3_modPPL_xcSyl_xcFreq)

# summary(DURNP2_modPPL_xcSyl_xcFreq2)
# summary(DURAND_modPPL_xcSyl_xcFreq2) 
# summary(DURNP3_modPPL_xcSyl_xcFreq2) 
# summary(DURANDNP3_modPPL_xcSyl_xcFreq2)
```

#relatedness as contrast coded, Frequency, with & without Item order - p3opl3

```{r}
DURNP2_modPPL_xcFreq_ryes <- lmer(log(DUR_NP2) ~ 
                     related_yes * xcFreq1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURAND_modPPL_xcFreq_ryes <- lmer(log(DUR_AND) ~ 
                     related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURNP3_modPPL_xcFreq_ryes <- lmer(log(DUR_NP3) ~ 
                    related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURANDNP3_modPPL_xcFreq_ryes <- lmer(log(DUR_AND_plus_NP3) ~ 
                     related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 


DURNP2_modPPL_xcFreq_ryes2 <- lmer(log(DUR_NP2) ~ 
                     related_yes * xcFreq1 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURAND_modPPL_xcFreq_ryes2 <- lmer(log(DUR_AND) ~ 
                    related_yes * xcFreq2 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURNP3_modPPL_xcFreq_ryes2 <- lmer(log(DUR_NP3) ~ 
                    related_yes * xcFreq2 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

DURANDNP3_modPPL_xcFreq_ryes2 <- lmer(log(DUR_AND_plus_NP3) ~ 
                    related_yes * xcFreq2 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

# summary(DURNP2_modPPL_xcFreq) 
# summary(DURAND_modPPL_xcFreq) 
# summary(DURNP3_modPPL_xcFreq) 
# summary(DURANDNP3_modPPL_xcFreq)

# summary(DURNP2_modPPL_xcFreq2)
# summary(DURAND_modPPL_xcFreq2) 
# summary(DURNP3_modPPL_xcFreq2) 
# summary(DURANDNP3_modPPL_xcFreq2)
```

### Items

#contrast relatedness

## Syllables and related_yes in items with and without item order. 

```{r}
DURNP2_modITEMS_xcsyl_ryes <- lmer(log(DUR_NP2) ~ 
                     related_yes*xcNsyl_P2+ (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modITEMS_xcsyl_ryes <- lmer(log(DUR_AND) ~
                     related_yes*xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modITEMS_xcsyl_ryes <- lmer(log(DUR_NP3) ~
                     related_yes*xcNsyl_P3 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modITEMS_xcsyl_ryes <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*xcNsyl_P3  + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> nothing sig

#with item order
DURNP2_modITEMS_xcsyl_ryes2 <- lmer(log(DUR_NP2) ~ 
                     related_yes*xcNsyl_P2 *item_order + (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modITEMS_xcsyl_ryes2 <- lmer(log(DUR_AND) ~
                     related_yes*xcNsyl_P3 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modITEMS_xcsyl_ryes2 <- lmer(log(DUR_NP3) ~
                     related_yes*xcNsyl_P3 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modITEMS_xcsyl_ryes2 <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*xcNsyl_P3 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> nothing sig

summary(DURNP2_modITEMS_xcsyl_ryes)
```

## Frequency and related_yes in items with and without item order. 

```{r}
DURNP2_modITEMS_xcFreq_ryes <- lmer(log(DUR_NP2) ~ 
                     related_yes*xcFreq1+ (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modITEMS_xcFreq_ryes  <- lmer(log(DUR_AND) ~
                     related_yes*xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modITEMS_xcFreq_ryes  <- lmer(log(DUR_NP3) ~
                     related_yes*xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modITEMS_xcFreq_ryes  <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*xcFreq2  + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> nothing sig

#with item order
DURNP2_modITEMS_xcFreq_ryes2  <- lmer(log(DUR_NP2) ~ 
                     related_yes*xcFreq1 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURAND_modITEMS_xcFreq_ryes2  <- lmer(log(DUR_AND) ~
                     related_yes*xcFreq2 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> Nothing sig

DURNP3_modITEMS_xcFreq_ryes2  <- lmer(log(DUR_NP3) ~
                     related_yes*xcFreq2 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcCos sig negative direction -> cosine sig neg direction

DURANDNP3_modITEMS_xcFreq_ryes2 <- lmer(log(DUR_AND_plus_NP3) ~
                     related_yes*xcFreq2 *item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #Nothing sig -> nothing sig
```

#relatedness contrast coded, syllables, frequency with and without item order - ITEMS #Models for duration NP2 always singular fit

```{r}
DURNP2_modITEMS_xcsyl_xcFreq_ryes <- lmer(log(DUR_NP2) ~ 
                    xcNsyl_P2 * related_yes * xcFreq1 + (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig

DURAND_modITEMS_xcsyl_xcFreq_ryes <- lmer(log(DUR_AND) ~
                     xcNsyl_P3 * related_yes * xcFreq2 + (1|ParticipantNum)+(1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig

DURNP3_modITEMS_xcsyl_xcFreq_ryes <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3 * related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig

DURANDNP3_modITEMS_xcsyl_xcFreq_ryes <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3 * related_yes * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig

DURNP2_modITEMS_xcsyl_xcFreq_ryes2 <- lmer(log(DUR_NP2) ~ 
                    xcNsyl_P2 * related_yes * item_order * xcFreq1 + (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig

DURAND_modITEMS_xcsyl_xcFreq_ryes2 <- lmer(log(DUR_AND) ~
                     xcNsyl_P3 * related_yes * item_order * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig

DURNP3_modITEMS_xcsyl_xcFreq_ryes2 <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3 * related_yes * item_order * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig

DURANDNP3_modITEMS_xcsyl_xcFreq_ryes2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3 * related_yes * item_order * xcFreq2 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllables sig
```

#quant relatedness

#PMI & Syllables in ITEMS. Models for NP2 always singular fit

```{r}
DURNP2_modITEMS_xcsyl_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2*xcPMI + (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig, singular fit

DURAND_modITEMS_xcsyl_xcPMI <- lmer(log(DUR_AND) ~
                     xcNsyl_P3*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI and syllable sig, not interaction *** DIFF ***

DURNP3_modITEMS_xcsyl_xcPMI <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURANDNP3_modITEMS_xcsyl_xcPMI <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig


DURNP2_modITEMS_xcsyl_xcPMI2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2*xcPMI* item_order + (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig, singular fit

DURAND_modITEMS_xcsyl_xcPMI2 <- lmer(log(DUR_AND) ~
                     xcNsyl_P3*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI and syllable sig, not interaction *** DIFF ***

DURNP3_modITEMS_xcsyl_xcPMI2 <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURANDNP3_modITEMS_xcsyl_xcPMI2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

summary(DURNP2_modITEMS_xcsyl_xcPMI2)
```

#PMI & frequqncy in ITEMS. Models for NP2 singular fit when item order not included in the model

```{r}
DURNP2_modITEMS_xcFreq_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcFreq1*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig, singular fit

DURAND_modITEMS_xcFreq_xcPMI <- lmer(log(DUR_AND) ~
                     xcFreq2*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI and syllable sig, not interaction *** DIFF ***

DURNP3_modITEMS_xcFreq_xcPMI <- lmer(log(DUR_NP3) ~
                     xcFreq2*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURANDNP3_modITEMS_xcFreq_xcPMI <- lmer(log(DUR_AND_plus_NP3) ~
                     xcFreq2*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURNP2_modITEMS_xcFreq_xcPMI2 <- lmer(log(DUR_NP2) ~ 
                     xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig, singular fit

DURAND_modITEMS_xcFreq_xcPMI2 <- lmer(log(DUR_AND) ~
                     xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI and syllable sig, not interaction *** DIFF ***

DURNP3_modITEMS_xcFreq_xcPMI2 <- lmer(log(DUR_NP3) ~
                     xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURANDNP3_modITEMS_xcFreq_xcPMI2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig
```

#PMI & frequqncy & syllables in ITEMS. Models for NP2 singular fitalways
 
```{r}
DURNP2_modITEMS_xcsyl_xcFreq_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2*xcFreq1*xcPMI + (1|ParticipantNum), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig, singular fit

DURAND_modITEMS_xcsyl_xcFreq_xcPMI <- lmer(log(DUR_AND) ~
                     xcNsyl_P3*xcFreq2*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI and syllable sig, not interaction *** DIFF ***

DURNP3_modITEMS_xcsyl_xcFreq_xcPMI <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3*xcFreq2*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURANDNP3_modITEMS_xcsyl_xcFreq_xcPMI <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcFreq2*xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURNP2_modITEMS_xcsyl_xcFreq_xcPMI2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2*xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig, singular fit

DURAND_modITEMS_xcsyl_xcFreq_xcPMI2 <- lmer(log(DUR_AND) ~
                     xcNsyl_P3*xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #xcPMI and syllable sig, not interaction *** DIFF ***

DURNP3_modITEMS_xcsyl_xcFreq_xcPMI2 <- lmer(log(DUR_NP3) ~
                     xcNsyl_P3*xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig

DURANDNP3_modITEMS_xcsyl_xcFreq_xcPMI2 <- lmer(log(DUR_AND_plus_NP3) ~
                     xcNsyl_P3*xcFreq2*xcPMI* item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE) #only syllable sig
```

#People-people models with name agreement, frequency, syllable length, contrast-coded relatedness and then frequency removed for durnp2 because it didn't matter - slopes led to singular fits
```{r}
DURNP2_modPPL_xcSyl_xcFreq_xcNA_ryes <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes * xcFreq1 * xcNA1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 
DURNP2_modPPL_xcSyl_xcFreq_xcNA_ryes2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes * xcFreq1 * xcNA1 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

summary(DURNP2_modPPL_xcSyl_xcFreq_xcNA_ryes)
summary(DURNP2_modPPL_xcSyl_xcFreq_xcNA_ryes2)

#Just name agreement and syl and relatedness no freq
DURNP2_modPPL_xcSyl_xcNA_ryes <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes  * xcNA1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 
DURNP2_modPPL_xcSyl_xcNA_ryes2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes  * xcNA1 * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

summary(DURNP2_modPPL_xcSyl_xcNA_ryes)
summary(DURNP2_modPPL_xcSyl_xcNA_ryes2)

make_nice_table(DURNP2_modPPL_xcSyl_xcNA_ryes,"DURNP2_modPPL_xcSyl_xcNA_ryes.docx")
```

# DURNP2 People-people models with name agreement, frequency, syllable length, cosine and PMI relatedness and then frequency removed for durnp2 because it didn't matter
```{r}
DURNP2_modPPL_xcSyl_xcFreq_xcNA_xcPMI_xcCos <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * xcPMI*xcCos * xcFreq1 * xcNA1 + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 
DURNP2_modPPL_xcSyl_xcFreq_xcNA_xcPMI_xcCos2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * xcPMI*xcCos * xcFreq1 * xcNA1 * item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 

summary(DURNP2_modPPL_xcSyl_xcFreq_xcNA_xcPMI_xcCos)
summary(DURNP2_modPPL_xcSyl_xcFreq_xcNA_xcPMI_xcCos2)

DURNP2_modPPL_xcSyl_xcNA_xcPMI_xcCos <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * xcPMI*xcCos  * xcNA1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 
DURNP2_modPPL_xcSyl_xcNA_xcPMI_xcCos2 <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * xcPMI*xcCos  * xcNA1 * item_order + (1+xcCos|ParticipantNum) + (1|Anchor), data = Data_useable_peopleAB) 
summary(DURNP2_modPPL_xcSyl_xcNA_xcPMI_xcCos)
summary(DURNP2_modPPL_xcSyl_xcNA_xcPMI_xcCos2)

make_nice_table(DURNP2_modPPL_xcSyl_xcNA_xcPMI_xcCos,"DURNP2_modPPL_xcSyl_xcNA_xcPMI_xcCos.docx")

```

#MODEL OUTPUT SUMMARY TABLES:
**For all model names, 2 indicates the model is the same as the previous model but with item order added. Ryes is related_yes, or the contrast coding**

#PEOPLE SIMPLE

## DURNP2 simple models for people, with and without item order

```{r}
library(texreg)
screenreg(list(DURNP2_modPPL_xcsyl,
               DURNP2_modPPL_xcsyl2,
               DURNP2_modPPL_xcFreq,
               DURNP2_modPPL_xcFreq2,
               DURNP2_modPPL_xcNA,
               DURNP2_modPPL_xcNA2,
               DURNP2_modPPL_xcCos,
               DURNP2_modPPL_xcCos2,
               DURNP2_modPPL_xcPMI,
               DURNP2_modPPL_xcPMI2,
               DURNP2_modPPL_xcPMI_xcCos,
               DURNP2_modPPL_xcPMI_xcCos2,
               DURNP2_modPPL_contrast_relatedness,
               DURNP2_modPPL_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcFreq","xcFreq2", "xcNA", "xcNA2", "xcCos", "xcCos2","xcPMI", "xcPMI2", "xcPMI&xcCos", "xcPMI&xcCos2","Ryes","Ryes2"))
```

## DURAND simple models for people, with and without item order

```{r}
screenreg(list(DURAND_modPPL_xcsyl,
               DURAND_modPPL_xcsyl2,
               DURAND_modPPL_xcFreq,
               DURAND_modPPL_xcFreq2,
               DURAND_modPPL_xcNA,
               DURAND_modPPL_xcNA2,
               DURAND_modPPL_xcCos,
               DURAND_modPPL_xcCos2,
               DURAND_modPPL_xcPMI,
               DURAND_modPPL_xcPMI2,
               DURAND_modPPL_xcPMI_xcCos,
               DURAND_modPPL_xcPMI_xcCos2,
               DURAND_modPPL_contrast_relatedness,
               DURAND_modPPL_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcFreq","xcFreq2", "xcNA", "xcNA2", "xcCos", "xcCos2","xcPMI", "xcPMI2", "xcPMI&xcCos", "xcPMI&xcCos2","Ryes","Ryes2"))
```

## DURNP3 simple models for people, with and without item order

```{r}
screenreg(list(DURNP3_modPPL_xcsyl,
               DURNP3_modPPL_xcsyl2,
               DURNP3_modPPL_xcFreq,
               DURNP3_modPPL_xcFreq2,
               DURNP3_modPPL_xcNA,
               DURNP3_modPPL_xcNA2,
               DURNP3_modPPL_xcCos,
               DURNP3_modPPL_xcCos2,
               DURNP3_modPPL_xcPMI,
               DURNP3_modPPL_xcPMI2,
               DURNP3_modPPL_xcPMI_xcCos,
               DURNP3_modPPL_xcPMI_xcCos2,
               DURNP3_modPPL_contrast_relatedness,
               DURNP3_modPPL_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcFreq","xcFreq2", "xcNA", "xcNA2", "xcCos", "xcCos2","xcPMI", "xcPMI2", "xcPMI&xcCos", "xcPMI&xcCos2","Ryes","Ryes2"))
```

Only relatedness when contrast coded (and with item order there), relatedness when defined by Cosine (not PMI alone), and syllable length. Interaction btw frequency and item order but frequency was never sig on its own.

## DURANDNP3 simple models for people, with and without item order

```{r}
screenreg(list(DURANDNP3_modPPL_xcsyl,
               DURANDNP3_modPPL_xcsyl2,
               DURANDNP3_modPPL_xcFreq,
               DURANDNP3_modPPL_xcFreq2,
               DURANDNP3_modPPL_xcNA,
               DURANDNP3_modPPL_xcNA2,
               DURANDNP3_modPPL_xcCos,
               DURANDNP3_modPPL_xcCos2,
               DURANDNP3_modPPL_xcPMI,
               DURANDNP3_modPPL_xcPMI2,
               DURANDNP3_modPPL_xcPMI_xcCos,
               DURANDNP3_modPPL_xcPMI_xcCos2,
               DURANDNP3_modPPL_contrast_relatedness,
               DURANDNP3_modPPL_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcFreq","xcFreq2", "xcNA", "xcNA2", "xcCos", "xcCos2","xcPMI", "xcPMI2", "xcPMI&xcCos", "xcPMI&xcCos2","Ryes","Ryes2"))
```

Cos and PMI still matter here in the negative direction. Contrast coded relatedness too. NA, Freq never sig on their own. Syllable length is sig on its own.

## DURNP2 simple models for items, with and without item order

```{r}
screenreg(list(DURNP2_modITEMS_xcsyl,
               DURNP2_modITEMS_xcsyl2,
               DURNP2_modITEMS_xcPMI,
               DURNP2_modITEMS_xcPMI2,
               DURNP2_modITEMS_xcNA,
               DURNP2_modITEMS_xcNA2,
               DURNP2_modITEMS_xcFreq,
               DURNP2_modITEMS_xcFreq2,
               DURNP2_modITEMS_contrast_relatedness,
               DURNP2_modITEMS_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcPMI","xcPMI2", "xcNA", "xcNA2", "xcFreq", "xcFreq2","Ryes", "Ryes2"))
```

Syllables and item order

## DURAND simple models for items, with and without item order

```{r}
screenreg(list(DURAND_modITEMS_xcsyl,
               DURAND_modITEMS_xcsyl2,
               DURAND_modITEMS_xcPMI,
               DURAND_modITEMS_xcPMI2,
               DURAND_modITEMS_xcNA,
               DURAND_modITEMS_xcNA2,
               DURAND_modITEMS_xcFreq,
               DURAND_modITEMS_xcFreq2,
               DURAND_modITEMS_contrast_relatedness,
               DURAND_modITEMS_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcPMI","xcPMI2", "xcNA", "xcNA2", "xcFreq", "xcFreq2","Ryes", "Ryes2"))
```

Syllables, item order, PMI (longer durations??) and related contrast coded (shorter durations)

## DURNP3 simple models for items, with and without item order

```{r}
#Duration 2 simple models
screenreg(list(DURNP3_modITEMS_xcsyl,
               DURNP3_modITEMS_xcsyl2,
               DURNP3_modITEMS_xcPMI,
               DURNP3_modITEMS_xcPMI2,
               DURNP3_modITEMS_xcNA,
               DURNP3_modITEMS_xcNA2,
               DURNP3_modITEMS_xcFreq,
               DURNP3_modITEMS_xcFreq2,
               DURNP3_modITEMS_contrast_relatedness,
               DURNP3_modITEMS_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcPMI","xcPMI2", "xcNA", "xcNA2", "xcFreq", "xcFreq2","Ryes", "Ryes2"))
```

Syllables and item order only

## DURANDNP3 simple models for items, with and without item order

```{r}
#Duration 2 simple models
screenreg(list(DURANDNP3_modITEMS_xcsyl,
               DURANDNP3_modITEMS_xcsyl2,
               DURANDNP3_modITEMS_xcPMI,
               DURANDNP3_modITEMS_xcPMI2,
               DURANDNP3_modITEMS_xcNA,
               DURANDNP3_modITEMS_xcNA2,
               DURANDNP3_modITEMS_xcFreq,
               DURANDNP3_modITEMS_xcFreq2,
               DURANDNP3_modITEMS_contrast_relatedness,
               DURANDNP3_modITEMS_contrast_relatedness2),
          single.row=FALSE,
          custom.model.names=c("xcSyl", "xcSyl2","xcPMI","xcPMI2", "xcNA", "xcNA2", "xcFreq", "xcFreq2","Ryes", "Ryes2"))
```

Syllables and item order only

#MORE COMPLEX MODELS

## DURNP2 Complex models for people with and without item order

```{r}
screenreg(list(DURNP2_modPPL_xcsyl_xcCos,
               DURNP2_modPPL_xcsyl_xcCos2,
               DURNP2_modPPL_xcsyl_xcPMI,
               DURNP2_modPPL_xcsyl_xcPMI2,
               DURNP2_modPPL_xcsyl_xcPMI_xcCos,
               DURNP2_modPPL_xcsyl_xcPMI_xcCos2,
               DURNP2_modPPL_xcsyl_xcFreq_xcPMI_xcCos,
               DURNP2_modPPL_xcsyl_xcFreq_xcPMI_xcCos2,
               DURNP2_modPPL_xcsyl_ryes,
               DURNP2_modPPL_xcsyl_ryes2,
               DURNP2_modPPL_xcFreq_ryes,
               DURNP2_modPPL_xcFreq_ryes2,
               DURNP2_modPPL_xcSyl_xcFreq_ryes,
               DURNP2_modPPL_xcSyl_xcFreq_ryes2),
          single.row=FALSE,custom.model.names=c(
            "cos&syl", 
            "cos&syl2", 
            "PMI&syl", 
            "PMI&syl2", 
            "BothR&syl",
            "BothR&syl2", 
            "BothR&syl&F", 
            "BothR&syl&F2", 
            "Ryes&syl",
            "Ryes&syl2",
            "Ryes&F",
            "Ryes&F2",
            "Ryes&syl&F",
            "Ryes&syl&F2"))

make_nice_table(DURNP2_modPPL_xcsyl_xcPMI,"DURNP2_modPPL_xcsyl_xcPMI.docx")
make_nice_table(DURNP2_modPPL_xcsyl_xcCos,"DURNP2_modPPL_xcsyl_xcCos.docx")
plot_model(DURNP2_modPPL_xcsyl_xcPMI,type = 'int')

summary(DURNP2_modPPL_xcsyl_xcCos)

cor.test(Data_useable_with_animacyAB$PMI, Data_useable_with_animacyAB$Cos)

#Trying to graph
library(dplyr)
DurationNP2_PMI <- Data_useable_peopleAB %>% 
  group_by(PMI) %>% 
  select(PMI, Nsyl_P2, DUR_NP2) %>%
  summarize(mean_DURNP2 = mean(DUR_NP2))

#summarize over items by means across participants
```

## DURAND Complex models for people with and without item order

```{r}
#Duration 2 more complex models
screenreg(list(DURAND_modPPL_xcsyl_xcCos,
               DURAND_modPPL_xcsyl_xcCos2,
               DURAND_modPPL_xcsyl_xcPMI,
               DURAND_modPPL_xcsyl_xcPMI2,
               DURAND_modPPL_xcsyl_xcPMI_xcCos,
               DURAND_modPPL_xcsyl_xcPMI_xcCos2,
               DURAND_modPPL_xcsyl_xcFreq_xcPMI_xcCos,
               DURAND_modPPL_xcsyl_xcFreq_xcPMI_xcCos2,
               DURAND_modPPL_xcsyl_ryes,
               DURAND_modPPL_xcsyl_ryes2,
               DURAND_modPPL_xcFreq_ryes,
               DURAND_modPPL_xcFreq_ryes2,
               DURAND_modPPL_xcSyl_xcFreq_ryes,
               DURAND_modPPL_xcSyl_xcFreq_ryes2),
          single.row=FALSE,custom.model.names=c(
            "cos&syl", 
            "cos&syl2", 
            "PMI&syl", 
            "PMI&syl2", 
            "BothR&syl",
            "BothR&syl2", 
            "BothR&syl&F", 
            "BothR&syl&F2", 
            "Ryes&syl",
            "Ryes&syl2",
            "Ryes&F",
            "Ryes&F2",
            "Ryes&syl&F",
            "Ryes&syl&F2"))

make_nice_table(DURAND_modPPL_xcsyl_xcPMI2,"DURAND_modPPL_xcsyl_xcPMI2.docx")
make_nice_table(DURAND_modPPL_xcsyl_xcCos2,"DURAND_modPPL_xcsyl_xcCos2.docx")
make_nice_table(DURAND_modPPL_xcsyl_xcPMI_xcCos,"DURAND_modPPL_xcsyl_xcPMI_xcCos.docx")
make_nice_table(DURAND_modPPL_xcsyl_ryes,"DURAND_modPPL_xcsyl_ryes.docx")



summary(DURAND_modPPL_xcsyl_ryes)
summary(DURAND_modPPL_xcsyl_ryes2)
summary(DURAND_modPPL_xcsyl_xcCos2) #slope cos
summary(DURAND_modPPL_xcsyl_xcPMI_xcCos) #slope cos

summary(DURAND_modPPL_xcsyl_xcPMI2)

plot_model(DURAND_modPPL_xcsyl_xcPMI2, type = "int")
plot_model(DURAND_modPPL_xcsyl_ryes, type = "int")

View(Data_useable_peopleAB)
```

## DURNP3 Complex models for people with and without item order

```{r}
#Duration 3 more complex models
screenreg(list(DURNP3_modPPL_xcsyl_xcCos,
               DURNP3_modPPL_xcsyl_xcCos2,
               DURNP3_modPPL_xcsyl_xcPMI,
               DURNP3_modPPL_xcsyl_xcPMI2,
               DURNP3_modPPL_xcsyl_xcPMI_xcCos,
               DURNP3_modPPL_xcsyl_xcPMI_xcCos2,
               DURNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos,
               DURNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos2,
               DURNP3_modPPL_xcsyl_ryes,
               DURNP3_modPPL_xcsyl_ryes2,
               DURNP3_modPPL_xcFreq_ryes,
               DURNP3_modPPL_xcFreq_ryes2,
               DURNP3_modPPL_xcSyl_xcFreq_ryes,
               DURNP3_modPPL_xcSyl_xcFreq_ryes2),
          single.row=FALSE,custom.model.names=c(
            "cos&syl", 
            "cos&syl2", 
            "PMI&syl", 
            "PMI&syl2", 
            "BothR&syl",
            "BothR&syl2", 
            "BothR&syl&F", 
            "BothR&syl&F2", 
            "Ryes&syl",
            "Ryes&syl2",
            "Ryes&F",
            "Ryes&F2",
            "Ryes&syl&F",
            "Ryes&syl&F2"))

make_nice_table(DURNP3_modPPL_xcsyl_xcCos, "DURNP3_modPPL_xcsyl_xcCos.docx")
make_nice_table(DURNP3_modPPL_xcsyl_xcPMI,"DURNP3_modPPL_xcsyl_xcPMI.docx")
```


## DURANDNP3 complex models for people with and without item order

```{r}
#Duration 3 more complex models
screenreg(list(DURANDNP3_modPPL_xcsyl_xcCos,
               DURANDNP3_modPPL_xcsyl_xcCos2,
               DURANDNP3_modPPL_xcsyl_xcPMI,
               DURANDNP3_modPPL_xcsyl_xcPMI2,
               DURANDNP3_modPPL_xcsyl_xcPMI_xcCos,
               DURANDNP3_modPPL_xcsyl_xcPMI_xcCos2,
               DURANDNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos,
               DURANDNP3_modPPL_xcsyl_xcFreq_xcPMI_xcCos2,
               DURANDNP3_modPPL_xcsyl_ryes,
               DURANDNP3_modPPL_xcsyl_ryes2,
               DURANDNP3_modPPL_xcFreq_ryes,
               DURANDNP3_modPPL_xcFreq_ryes2,
               DURANDNP3_modPPL_xcSyl_xcFreq_ryes,
               DURANDNP3_modPPL_xcSyl_xcFreq_ryes2),
          single.row=FALSE,custom.model.names=c(
            "cos&syl", 
            "cos&syl2", 
            "PMI&syl", 
            "PMI&syl2", 
            "BothR&syl",
            "BothR&syl2", 
            "BothR&syl&F", 
            "BothR&syl&F2", 
            "Ryes&syl",
            "Ryes&syl2",
            "Ryes&F",
            "Ryes&F2",
            "Ryes&syl&F",
            "Ryes&syl&F2"))

summary(DURANDNP3_modPPL_xcsyl_xcPMI_xcCos)
summary(DURANDNP3_modPPL_xcsyl_xcPMI_xcCos2)
summary(DURANDNP3_modPPL_xcsyl_ryes2)
```

#Items Complex Models

## DURNP2 Items Complex
```{r}
screenreg(list(DURNP2_modITEMS_xcsyl_xcPMI,
               DURNP2_modITEMS_xcsyl_xcPMI2,
               DURNP2_modITEMS_xcFreq_xcPMI,
               DURNP2_modITEMS_xcFreq_xcPMI2,
               DURNP2_modITEMS_xcsyl_xcFreq_xcPMI,
               DURNP2_modITEMS_xcsyl_xcFreq_xcPMI2,
               DURNP2_modITEMS_xcsyl_ryes,
               DURNP2_modITEMS_xcsyl_ryes2),
          single.row=FALSE,
          custom.model.names=c("xcSylxcPMI","xcSylxcPMI2","xcFreqxcPMI", "xcFreqxcPMI2","xcSylxcPMIXcFreq", "xcSylxcPMIxcFreq2", "xcsylRyes", "xcsylRyes2"))



```

## DURAND Items Complex
```{r}
screenreg(list(DURAND_modITEMS_xcsyl_xcPMI,
               DURAND_modITEMS_xcsyl_xcPMI2,
               DURAND_modITEMS_xcFreq_xcPMI,
               DURAND_modITEMS_xcFreq_xcPMI2,
               DURAND_modITEMS_xcsyl_xcFreq_xcPMI,
               DURAND_modITEMS_xcsyl_xcFreq_xcPMI2,
               DURAND_modITEMS_xcsyl_ryes,
               DURAND_modITEMS_xcsyl_ryes2),
          single.row=FALSE,
          custom.model.names=c("xcSylxcPMI","xcSylxcPMI2","xcFreqxcPMI", "xcFreqxcPMI2","xcSylxcPMIXcFreq", "xcSylxcPMIxcFreq2", "xcsylRyes", "xcsylRyes2"))
```

## DURNP3 Items Complex - Done using. Only syllables and item order ever mattered
```{r}
screenreg(list(DURNP3_modITEMS_xcsyl_xcPMI,
               DURNP3_modITEMS_xcsyl_xcPMI2,
               DURNP3_modITEMS_xcFreq_xcPMI,
               DURNP3_modITEMS_xcFreq_xcPMI2,
               DURNP3_modITEMS_xcsyl_xcFreq_xcPMI,
               DURNP3_modITEMS_xcsyl_xcFreq_xcPMI2,
               DURNP3_modITEMS_xcsyl_ryes,
               DURNP3_modITEMS_xcsyl_ryes2),
          single.row=FALSE,
          custom.model.names=c("xcSylxcPMI","xcSylxcPMI2","xcFreqxcPMI", "xcFreqxcPMI2","xcSylxcPMIXcFreq", "xcSylxcPMIxcFreq2", "xcsylRyes", "xcsylRyes2"))
```

## DURANDNP3 Items Complex - Done 
```{r}
screenreg(list(DURANDNP3_modITEMS_xcsyl_xcPMI,
               DURANDNP3_modITEMS_xcsyl_xcPMI2,
               DURANDNP3_modITEMS_xcFreq_xcPMI,
               DURANDNP3_modITEMS_xcFreq_xcPMI2,
               DURANDNP3_modITEMS_xcsyl_xcFreq_xcPMI,
               DURANDNP3_modITEMS_xcsyl_xcFreq_xcPMI2,
               DURANDNP3_modITEMS_xcsyl_ryes,
               DURANDNP3_modITEMS_xcsyl_ryes2),
          single.row=FALSE,
          custom.model.names=c("xcSylxcPMI","xcSylxcPMI2","xcFreqxcPMI", "xcFreqxcPMI2","xcSylxcPMIXcFreq", "xcSylxcPMIxcFreq2", "xcsylRyes", "xcsylRyes2"))

summary(DURANDNP3_modITEMS_xcsyl_xcPMI2)
summary(DURANDNP3_modITEMS_xcsyl_ryes2)
```


Tables for the 4 DURNP2 Models
```{r T1}

summary(DURNP2_modPPL_xcsyl_xcPMI_xcCos) #DURNP2 people-people quant
summary(DURNP2_modPPL_xcsyl_ryes) #DURNP2 people-people contrast
summary(DURNP2_modITEMS_xcsyl_xcPMI2) #DURNP2 people-items quant
summary(DURNP2_modITEMS_xcsyl_ryes2) #DURNP2 people-item contrast

make_nice_table(DURNP2_modPPL_xcsyl_xcPMI_xcCos,"DURNP2_modPPL_xcsyl_xcPMI_xcCos.docx") #DURNP2 people-people quant
make_nice_table(DURNP2_modPPL_xcsyl_ryes,"DURNP2_modPPL_xcsyl_ryes.docx") #DURNP2 people-people contrast
make_nice_table(DURNP2_modITEMS_xcsyl_xcPMI2,"DURNP2_modITEMS_xcsyl_xcPMI2.docx") #DURNP2 people-items quant
make_nice_table(DURNP2_modITEMS_xcsyl_ryes2,"DURNP2_modITEMS_xcsyl_ryes2.docx") #DURNP2 people-item contrast
```

DurAND Tables and some plots
```{r}
make_nice_table(DURAND_modPPL_xcsyl_xcPMI_xcCos,"DURAND_modPPL_xcsyl_xcPMI_xcCos.docx") #DURNP2 people-people quant
make_nice_table(DURAND_modPPL_xcsyl_xcPMI_xcCos2,"DURAND_modPPL_xcsyl_xcPMI_xcCos2.docx") #DURNP2 people-people quant

make_nice_table(DURAND_modPPL_xcsyl_ryes,"DURAND_modPPL_xcsyl_ryes.docx") #DURNP2 people-people quant
make_nice_table(DURAND_modPPL_xcsyl_ryes2,"DURAND_modPPL_xcsyl_ryes2.docx") #DURNP2 people-people quant


make_nice_table(DURAND_modPPL_xcsyl_ryes,"DURAND_modPPL_xcsyl_ryes.docx") #DURNP2 people-people contrast
make_nice_table(DURAND_modITEMS_xcsyl_xcPMI2,"DURAND_modITEMS_xcsyl_xcPMI2.docx") #DURNP2 people-items quant
make_nice_table(DURAND_modITEMS_xcsyl_ryes2,"DURAND_modITEMS_xcsyl_ryes2.docx") #DURNP2 people-item contrast

summary(DURAND_modPPL_xcsyl_xcPMI_xcCos)
summary(DURAND_modPPL_xcsyl_xcPMI_xcCos2)
summary(DURAND_modPPL_xcsyl_ryes)
summary(DURAND_modPPL_xcsyl_ryes2)

make_nice_table(DURAND_modITEMS_xcsyl_xcPMI,"DURAND_modITEMS_xcsyl_xcPMI.docx")

summary(DURAND_modITEMS_xcsyl_xcPMI)
summary(DURAND_modITEMS_xcsyl_xcPMI2)

summary(DURAND_modITEMS_xcsyl_ryes)
make_nice_table(DURAND_modITEMS_xcsyl_ryes, 
                "DURAND_modITEMS_xcsyl_ryes.docx")
summary(DURAND_modITEMS_xcsyl_ryes2)

make_nice_table(DURAND_modITEMS_xcsyl_xcPMI2,"DURAND_modITEMS_xcsyl_xcPMI2.docx")

ggplot(Data_useable_peopleAB, aes(x=xcNsyl_P2, y =log(DUR_AND), col=xcCos)) + geom_point() + geom_jitter()
ggplot(Data_useable_peopleAB, aes(x=xcPMI, y =log(DUR_AND), col=xcCos)) + geom_point() + geom_jitter()

ggplot(Data_useable_peopleAB, aes(x=as.factor(item_order), y = log(DUR_AND), col = related_yes)) + geom_line()
library(sjPlot)
library(sjmisc)
library(ggplot2)
plot_model(DURAND_modPPL_xcsyl_ryes, type = "int")
plot_model(DURAND_modPPL_xcsyl_ryes2, type = "int")
plot_model(DURNP2_modPPL_xcsyl_xcFreq_xcPMI_xcCos, type = "int")
```


DURNP3 tables
```{r T3}
make_nice_table(DURNP3_modPPL_xcsyl_xcPMI_xcCos,"DURNP3_modPPL_xcsyl_xcPMI_xcCos.docx") #DURNP2 people-people quant
make_nice_table(DURNP3_modPPL_xcsyl_ryes,"DURNP3_modPPL_xcsyl_ryes.docx") #DURNP2 people-people contrast
make_nice_table(DURNP3_modITEMS_xcsyl_xcPMI2,"DURNP3_modITEMS_xcsyl_xcPMI2.docx") #DURNP2 people-items quant
make_nice_table(DURNP3_modITEMS_xcsyl_ryes2,"DURNP3_modITEMS_xcsyl_ryes2.docx") #DURNP2 people-item contrast

summary(DURNP3_modPPL_xcsyl_ryes)
summary(DURNP3_modPPL_xcsyl_ryes2) #no change in pattern
summary(DURNP3_modITEMS_xcsyl_xcPMI)
summary(DURNP3_modITEMS_xcsyl_xcPMI2) #no change in pattern
```

DURANDNP3 tables
```{r Ta3}
DURANDNP3_modPPL_xcsyl_xcPMI_xcCos
make_nice_table(DURANDNP3_modPPL_xcsyl_xcPMI_xcCos,"DURANDNP3_modPPL_xcsyl_xcPMI_xcCos.docx") #DURNP2 people-people quant
make_nice_table(DURANDNP3_modPPL_xcsyl_ryes2,"DURANDNP3_modPPL_xcsyl_ryes2.docx") #DURNP2 people-people contrast
make_nice_table(DURANDNP3_modITEMS_xcsyl_xcPMI2,"DURANDNP3_modITEMS_xcsyl_xcPMI2.docx") #DURNP2 people-items quant
make_nice_table(DURANDNP3_modITEMS_xcsyl_ryes2,"DURANDNP3_modITEMS_xcsyl_ryes2.docx") #DURNP2 people-item contrast

summary(DURANDNP3_modPPL_xcsyl_ryes2)
summary(DURANDNP3_modITEMS_xcsyl_xcPMI2)

plot_model(DURANDNP3_modPPL_xcsyl_ryes2, type = "int")
summary(DURAND_modPPL_xcsyl_ryes2, type = "int")
```

DURNP1 stuff
```{r}
summary(lmer(log(DUR_NP1) ~ xcPMI * xcCos * xcNsyl_P2 + (1|ParticipantNum), data = Data_useable_peopleAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcPMI * xcCos * xcSyllables_XY+ (1|ParticipantNum), data = Data_useable_peopleAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcPMI * xcCos * xcNsyl_P2 * item_order + (1|ParticipantNum), data = Data_useable_peopleAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcPMI * xcCos * xcSyllables_XY * item_order+ (1|ParticipantNum), data = Data_useable_peopleAB, REML = FALSE))

summary(lmer(log(DUR_NP1) ~ xcPMI * xcSyllables_XY +  (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemsAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcPMI * xcNsyl_P2 + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcPMI * xcSyllables_XY * item_order+ (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcPMI * xcNsyl_P2 * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemsAB, REML = FALSE))

summary(lmer(log(DUR_NP1) ~ Condition * xcSyllables_XY +  (1|ParticipantNum) + (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ Condition * xcNsyl_P2 + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ Condition * xcSyllables_XY  * item_order + (1|ParticipantNum) + (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ Condition * xcNsyl_P2 * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))

summary(lmer(log(DUR_NP1) ~ xcNA1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcNA1 * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcFreq1 + (1|ParticipantNum) + (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))
summary(lmer(log(DUR_NP1) ~ xcFreq1 * item_order + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_with_animacyAB, REML = FALSE))

Data_useable_with_animacyAB <- Data_useable_with_animacyAB %>% mutate(people_people = ifelse(Data_useable_with_animacyAB$Condition == "RP"|Data_useable_with_animacyAB$Condition=="UP",1,0))

Data_useable_with_animacyAB_peoplepeople <- Data_useable_with_animacyAB[which(Data_useable_with_animacyAB$people_people == 1),]
Data_useable_with_animacyAB_peopleitem <- Data_useable_with_animacyAB[which(Data_useable_with_animacyAB$people_people == 0),]
Data_useable_with_animacyAB_related <- Data_useable_with_animacyAB[which(Data_useable_with_animacyAB$SecondRelated == 1),]
Data_useable_with_animacyAB_unrelated <- Data_useable_with_animacyAB[which(Data_useable_with_animacyAB$SecondRelated == 0),]

t.test(Data_useable_with_animacyAB_peoplepeople$DUR_NP1,Data_useable_with_animacyAB_peopleitem$DUR_NP1)
t.test(Data_useable_with_animacyAB_related$DUR_NP1,Data_useable_with_animacyAB_unrelated$DUR_NP1)

library(dplyr)
DURNP1_table <- Data_useable_with_animacyAB %>%
  group_by(Condition) %>%
  summarize(mean_DURNP1 = mean(DUR_NP1, na.rm = TRUE), sd_DURNP1 = sd(DUR_NP1))

DURNP1_table <- as.data.frame(DURNP1_table)
DURNP1_table <- nice_table(DURNP1_table)
DURNP1_table<- DURNP1_table %>%
    align(i = 1:3, j = 1, align = "left", part = "body") %>%
    align(j = 1, align = "left", part = "header") %>%
    set_table_properties(width = 1, layout = "autofit") %>%
    autofit(add_w = -1, add_h = 0, part = c("body", "header"), unit = "in") %>%
    bold(bold = TRUE, part = "header") %>%
    fontsize(size = 12, part = "body") %>%
    fontsize(size = 12, part = "header") %>%
    italic(italic = FALSE, part = "header")
print(DURNP1_table)
save_as_docx(DURNP1_table, path = "DUR_NP1_stats.docx")
```

Subsetting people-item models and refitting those analyses
```{r}
Data_useable_itemAB_personfirst <- Data_useable_itemsAB %>% filter(item_order == 0.5)
Data_useable_itemAB_itemfirst <- Data_useable_itemsAB %>% filter(item_order == -0.5)

#people first quant
DURNP2_modITEM_PPLFIRST_xcSyl_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * xcPMI + (1+xcPMI|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_personfirst) 
DURNP3_modITEM_PPLFIRST_xcSyl_xcPMI <- lmer(log(DUR_NP3) ~ 
                     xcNsyl_P3 * xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_personfirst) 

#item first quant
DURNP2_modITEM_ITEMFIRST_xcSyl_xcPMI <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_itemfirst) 
DURNP3_modITEM_ITEMFIRST_xcSyl_xcPMI <- lmer(log(DUR_NP3) ~ 
                     xcNsyl_P3 * xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_itemfirst) 

#people first contrast
DURNP2_modITEM_PPLFIRST_xcSyl_ryes <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemAB_personfirst) 
DURNP3_modITEM_PPLFIRST_xcSyl_ryes <- lmer(log(DUR_NP3) ~ 
                     xcNsyl_P3 * related_yes + (1+related_yes|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_personfirst) 

#item first contrast
DURNP2_modITEM_ITEMFIRST_xcSyl_ryes <- lmer(log(DUR_NP2) ~ 
                     xcNsyl_P2 * related_yes + (1|ParticipantNum), data = Data_useable_itemAB_itemfirst) 
DURNP3_modITEM_ITEMFIRST_xcSyl_ryes <- lmer(log(DUR_NP3) ~ 
                     xcNsyl_P3 * related_yes + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_itemfirst) 


#and contrast
DURAND_modITEM_PPLFIRST_xcSyl_ryes <- lmer(log(DUR_AND) ~ 
                     xcNsyl_P3 * related_yes + (1|ParticipantNum)+ (1|Anchor), data = Data_useable_itemAB_personfirst) 
DURAND_modITEM_ITEMFIRST_xcSyl_ryes <- lmer(log(DUR_AND) ~ 
                     xcNsyl_P3 * related_yes + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_itemfirst) 

#and quant
DURAND_modITEM_PPLFIRST_xcSyl_xcPMI <- lmer(log(DUR_AND) ~ 
                     xcNsyl_P3 * xcPMI + (1|ParticipantNum), data = Data_useable_itemAB_personfirst) 
DURAND_modITEM_ITEMFIRST_xcSyl_xcPMI <- lmer(log(DUR_AND) ~ 
                     xcNsyl_P3 * xcPMI + (1|ParticipantNum) + (1|Anchor), data = Data_useable_itemAB_itemfirst) 

summary(DURNP2_modITEM_PPLFIRST_xcSyl_xcPMI)
summary(DURNP3_modITEM_PPLFIRST_xcSyl_xcPMI)
summary(DURNP2_modITEM_ITEMFIRST_xcSyl_xcPMI)
summary(DURNP3_modITEM_ITEMFIRST_xcSyl_xcPMI)

summary(DURNP2_modITEM_PPLFIRST_xcSyl_ryes)
summary(DURNP3_modITEM_PPLFIRST_xcSyl_ryes)
summary(DURNP2_modITEM_ITEMFIRST_xcSyl_ryes)
summary(DURNP3_modITEM_ITEMFIRST_xcSyl_ryes)

summary(DURAND_modITEM_PPLFIRST_xcSyl_xcPMI)
summary(DURAND_modITEM_ITEMFIRST_xcSyl_xcPMI)
summary(DURAND_modITEM_PPLFIRST_xcSyl_ryes)
summary(DURAND_modITEM_ITEMFIRST_xcSyl_ryes)

make_nice_table(DURNP2_modITEM_PPLFIRST_xcSyl_xcPMI,"DURNP2_modITEM_PPLFIRST_xcSyl_xcPMI.docx")
make_nice_table(DURNP3_modITEM_PPLFIRST_xcSyl_xcPMI,"DURNP3_modITEM_PPLFIRST_xcSyl_xcPMI.docx")
make_nice_table(DURNP2_modITEM_ITEMFIRST_xcSyl_xcPMI,"DURNP2_modITEM_ITEMFIRST_xcSyl_xcPMI.docx")
make_nice_table(DURNP3_modITEM_ITEMFIRST_xcSyl_xcPMI,"DURNP3_modITEM_ITEMFIRST_xcSyl_xcPMI.docx")

make_nice_table(DURNP2_modITEM_PPLFIRST_xcSyl_ryes,"DURNP2_modITEM_PPLFIRST_xcSyl_ryes.docx")
make_nice_table(DURNP3_modITEM_PPLFIRST_xcSyl_ryes,"DURNP3_modITEM_PPLFIRST_xcSyl_ryes.docx")
make_nice_table(DURNP2_modITEM_ITEMFIRST_xcSyl_ryes,"DURNP2_modITEM_ITEMFIRST_xcSyl_ryes.docx")
make_nice_table(DURNP3_modITEM_ITEMFIRST_xcSyl_ryes,"DURNP3_modITEM_ITEMFIRST_xcSyl_ryes.docx")

make_nice_table(DURAND_modITEM_PPLFIRST_xcSyl_xcPMI,"DURAND_modITEM_PPLFIRST_xcSyl_xcPMI.docx")
make_nice_table(DURAND_modITEM_ITEMFIRST_xcSyl_xcPMI,"DURAND_modITEM_ITEMFIRST_xcSyl_xcPMI.docx")
make_nice_table(DURAND_modITEM_PPLFIRST_xcSyl_ryes,"DURAND_modITEM_PPLFIRST_xcSyl_ryes.docx")
make_nice_table(DURAND_modITEM_ITEMFIRST_xcSyl_ryes,"DURAND_modITEM_ITEMFIRST_xcSyl_ryes.docx")
```

Graphing participant means for items, split by short half of syllables and long half - PMI, DurNP2
```{r}
library(tidyverse)
library(dplyr)
Data_useable_peopleAB$Anchor <- as.factor(Data_useable_peopleAB$Anchor)
Data_useable_peopleAB$SecondThing <- as.factor(Data_useable_peopleAB$SecondThing)
Data_useable_peopleAB$Nsyl_P2 <- as.numeric(Data_useable_peopleAB$Nsyl_P2)
Data_useable_peopleAB_tibble <- as_tibble(Data_useable_peopleAB)

Data_useable_peopleAB_tibblePMINP2 <- Data_useable_peopleAB_tibble %>% group_by(Anchor, SecondThing, Nsyl_P2, PMI) %>% dplyr::summarise(Mean_DURNP2 = mean(DUR_NP2))

Data_useable_peopleAB_tibble_shortPMI <- Data_useable_peopleAB_tibblePMINP2 %>% filter(Nsyl_P2 == 1) 
Data_useable_peopleAB_tibble_medPMI <- Data_useable_peopleAB_tibblePMINP2 %>% filter(Nsyl_P2 == 2)  
Data_useable_peopleAB_tibble_longPMI <- Data_useable_peopleAB_tibblePMINP2 %>% filter(Nsyl_P2 > 2) 
Data_useable_peopleAB_tibble_medlongPMI <- Data_useable_peopleAB_tibblePMINP2 %>% filter(Nsyl_P2 >= 2)  
Data_useable_peopleAB_tibble_shortmedPMI <- Data_useable_peopleAB_tibblePMINP2 %>% filter(Nsyl_P2 <=2 )  

lower_syl_plot_PMI = ggplot(Data_useable_peopleAB_tibble_shortPMI, aes(x = PMI, y = Mean_DURNP2)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 5.5), breaks = seq(0.5, 5.5, by = 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, by = 0.25)) +
  labs(x = "PMI", y = "Mean NP2 Duration (S)", title = "1 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

med_syl_plot_PMI = ggplot(Data_useable_peopleAB_tibble_medPMI, aes(x = PMI, y = Mean_DURNP2)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 5.5), breaks = seq(0.5, 5.5, by = 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, by = 0.25)) +
  labs(x = "PMI", y = "Mean NP2 Duration (S)", title = "2 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

higher_syl_plot_PMI = ggplot(Data_useable_peopleAB_tibble_longPMI, aes(x = PMI, y = Mean_DURNP2)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 5.5), breaks = seq(0.5, 5.5, by = 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, by = 0.25)) +
  labs(x = "PMI", y = "Mean NP2 Duration (S)", title = "3+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

highest_syl_plot_PMI = ggplot(Data_useable_peopleAB_tibble_medlongPMI, aes(x = PMI, y = Mean_DURNP2)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 5.5), breaks = seq(0.5, 5.5, by = 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, by = 0.25)) +
  labs(x = "PMI", y = "Mean NP2 Duration (S)", title = "2+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

lowest_syl_plot_PMI = ggplot(Data_useable_peopleAB_tibble_shortmedPMI, aes(x = PMI, y = Mean_DURNP2)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5, 5.5), breaks = seq(0.5, 5.5, by = 0.5)) +
  scale_y_continuous(limits = c(0, 2), breaks = seq(0, 2, by = 0.25)) +
  labs(x = "PMI", y = "Mean NP2 Duration (S)", title = "2 or less Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

lower_syl_plot_PMI
med_syl_plot_PMI
higher_syl_plot_PMI
highest_syl_plot_PMI
lowest_syl_plot_PMI

png(filename = "1 vs 2 vs 3 PMI NP2.png",
    width = 30, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(lower_syl_plot_PMI,med_syl_plot_PMI,higher_syl_plot_PMI, ncol=3)
dev.off()
```

Graphing participant means for items, split by short half of syllables and long half - PMI, DurAND
```{r}
library(tidyverse)
library(dplyr)
Data_useable_peopleAB$Anchor <- as.factor(Data_useable_peopleAB$Anchor)
Data_useable_peopleAB$SecondThing <- as.factor(Data_useable_peopleAB$SecondThing)
Data_useable_peopleAB$Nsyl_P3 <- as.numeric(Data_useable_peopleAB$Nsyl_P3)
Data_useable_peopleAB_tibble <- as_tibble(Data_useable_peopleAB)

Data_useable_peopleAB_tibblePMIAND <- Data_useable_peopleAB_tibble %>% group_by(Anchor, SecondThing, Nsyl_P3, PMI) %>% dplyr::summarise(Mean_DURAND = mean(DUR_AND))

Data_useable_peopleAB_tibble_shortestPMI_AND <- Data_useable_peopleAB_tibblePMIAND %>% filter(Nsyl_P3 <= 2) 
Data_useable_peopleAB_tibble_shortPMI_AND <- Data_useable_peopleAB_tibblePMIAND %>% filter(Nsyl_P3 == 1) 
Data_useable_peopleAB_tibble_medPMI_AND <- Data_useable_peopleAB_tibblePMIAND %>% filter(Nsyl_P3 == 2)  
Data_useable_peopleAB_tibble_longPMI_AND <- Data_useable_peopleAB_tibblePMIAND %>% filter(Nsyl_P3 > 2) 
Data_useable_peopleAB_tibble_medlongPMI_AND <- Data_useable_peopleAB_tibblePMIAND %>% filter(Nsyl_P3 >= 2)  

lower_syl_plot_PMI_AND = ggplot(Data_useable_peopleAB_tibble_shortPMI_AND, aes(x = PMI, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0.5,5.5),breaks=seq(0.5,5.5,0.5)) +
    labs(x = "PMI", y = "Mean 'and' Duration (S)", title = "1 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

med_syl_plot_PMI_AND = ggplot(Data_useable_peopleAB_tibble_medPMI_AND, aes(x = PMI, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0.5,5.5),breaks=seq(0.5,5.5,0.5)) +
    labs(x = "PMI", y = "Mean 'and' Duration (S)", title = "2 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

higher_syl_plot_PMI_AND = ggplot(Data_useable_peopleAB_tibble_longPMI_AND, aes(x = PMI, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0.5,5.5),breaks=seq(0.5,5.5,0.5)) +
    labs(x = "PMI", y = "Mean 'and' Duration (S)", title = "3+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

highest_syl_plot_PMI_AND = ggplot(Data_useable_peopleAB_tibble_medlongPMI_AND, aes(x = PMI, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0.5,5.5),breaks=seq(0.5,5.5,0.5)) +
  labs(x = "PMI", y = "Mean 'and' Duration (S)", title = "2+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

lowest_syl_plot_PMI_AND = ggplot(Data_useable_peopleAB_tibble_shortestPMI_AND, aes(x = PMI, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0.5,5.5),breaks=seq(0.5,5.5,0.5)) +
    labs(x = "PMI", y = "Mean 'and' Duration (S)", title = "2 or less Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

lower_syl_plot_PMI_AND
med_syl_plot_PMI_AND
higher_syl_plot_PMI_AND
highest_syl_plot_PMI_AND
lowest_syl_plot_PMI_AND

png(filename = "1 vs 2 plus PMI AND.png",
    width = 18, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(lower_syl_plot_PMI_AND,highest_syl_plot_PMI_AND,ncol=2)
dev.off()

png(filename = "1 2 3 PMI AND2.png",
    width = 30, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(lower_syl_plot_PMI_AND,med_syl_plot_PMI_AND,higher_syl_plot_PMI_AND,ncol=3)
dev.off()

png(filename = "THISONETHISPLOT2.png",
    width = 18, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(lower_syl_plot_PMI_AND,highest_syl_plot_PMI_AND,ncol=2)
dev.off()

png(filename = "THISONETHISPLOT2.png",
    width = 18, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(lower_syl_plot_PMI_AND,highest_syl_plot_PMI_AND,ncol=2)
dev.off()
```

Graphing participant means for items, split by short half of syllables and long half - Cosine, DurAND
```{r}
library(tidyverse)
library(dplyr)
Data_useable_peopleAB$Anchor <- as.factor(Data_useable_peopleAB$Anchor)
Data_useable_peopleAB$SecondThing <- as.factor(Data_useable_peopleAB$SecondThing)
Data_useable_peopleAB$Nsyl_P3 <- as.numeric(Data_useable_peopleAB$Nsyl_P3)
Data_useable_peopleAB_tibble <- as_tibble(Data_useable_peopleAB)

#anchor first
Data_useable_peopleAB_tibbleCosAND <- Data_useable_peopleAB_tibble %>% group_by(Anchor, SecondThing, Nsyl_P3, Cos) %>% dplyr::summarise(Mean_DURAND = mean(DUR_AND))

Data_useable_peopleAB_tibble_shortCos <- Data_useable_peopleAB_tibbleCosAND %>% filter(Nsyl_P3 == 1) 
Data_useable_peopleAB_tibble_medCos <- Data_useable_peopleAB_tibbleCosAND %>% filter(Nsyl_P3 == 2)  
Data_useable_peopleAB_tibble_longCos <- Data_useable_peopleAB_tibbleCosAND %>% filter(Nsyl_P3 > 2) 
Data_useable_peopleAB_tibble_medlongCos <- Data_useable_peopleAB_tibbleCosAND %>% filter(Nsyl_P3 >= 2)  
Data_useable_peopleAB_tibble_shortmedCos <- Data_useable_peopleAB_tibbleCosAND %>% filter(Nsyl_P3 <= 2)  

lower_syl_plot_cos = ggplot(Data_useable_peopleAB_tibble_shortCos, aes(x = Cos, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 4) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0,0.9),breaks=seq(0,0.9,.1)) +
    labs(x = "Cosine", y = "Mean 'and' Duration (S)", title = "1 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

med_syl_plot_cos = ggplot(Data_useable_peopleAB_tibble_medCos, aes(x = Cos, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 4) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0,0.9),breaks=seq(0,0.9,.1)) +
  labs(x = "Cosine", y = "Mean 'and' Duration (S)", title = "2 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

higher_syl_plot_cos = ggplot(Data_useable_peopleAB_tibble_longCos, aes(x = Cos, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 4) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0,0.9),breaks=seq(0,0.9,.1)) +
    labs(x = "Cosine", y = "Mean 'and' Duration (S)", title = "3+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

highest_syl_plot_cos = ggplot(Data_useable_peopleAB_tibble_medlongCos, aes(x = Cos, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0,0.9),breaks=seq(0,0.9,.1)) +
  labs(x = "Cosine", y = "Mean 'and' Duration (S)", title = "2+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

lowest_syl_plot_cos = ggplot(Data_useable_peopleAB_tibble_shortmedCos, aes(x = Cos, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(0,0.9),breaks=seq(0,0.9,.1)) +
    labs(x = "Cosine", y = "Mean 'and' Duration (S)", title = "1-2 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))


lower_syl_plot_cos
highest_syl_plot_cos
med_syl_plot_cos
lowest_syl_plot_cos
higher_syl_plot_cos

png(filename = "1 vs 2+ syllables cosine.png",
    width = 18, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(lower_syl_plot_cos,highest_syl_plot_cos,ncol=2)
dev.off()
```

Graphing participant means for items split by syllables for contrast coded relatedness, DurAND
```{r}
Data_useable_peopleAB_tibbleRYAND <- Data_useable_peopleAB_tibble %>% group_by(Anchor, SecondThing, Nsyl_P3, related_yes) %>% dplyr::summarise(Mean_DURAND = mean(DUR_AND))

Data_useable_peopleAB_tibble_shortRY <- Data_useable_peopleAB_tibbleRYAND %>% filter(Nsyl_P3 == 1) 
Data_useable_peopleAB_tibble_medRY <- Data_useable_peopleAB_tibbleRYAND %>% filter(Nsyl_P3 == 2)  
Data_useable_peopleAB_tibble_longRY <- Data_useable_peopleAB_tibbleRYAND %>% filter(Nsyl_P3 > 2) 
Data_useable_peopleAB_tibble_longestRY <- Data_useable_peopleAB_tibbleRYAND %>% filter(Nsyl_P3 >= 2 ) 
Data_useable_peopleAB_tibble_shortestRY <- Data_useable_peopleAB_tibbleRYAND %>% filter(Nsyl_P3 <= 2 ) 

lower_syl_plot_RY = ggplot(Data_useable_peopleAB_tibble_shortRY, aes(x = related_yes, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(-.5,0.5),breaks=seq(-0.5,0.5,.1)) +
  labs(x = "Related Yes (0.5) vs No (-0.5)", y = "Mean 'and' Duration (S)", title = "1 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

med_syl_plot_RY = ggplot(Data_useable_peopleAB_tibble_medRY, aes(x = related_yes, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(-.5,0.5),breaks=seq(-0.5,0.5,.1)) +
    labs(x = "Related Yes (0.5) vs No (-0.5)", y = "Mean 'and' Duration (S)", title = "2 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

higher_syl_plot_RY = ggplot(Data_useable_peopleAB_tibble_longRY, aes(x = related_yes, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(-.5,0.5),breaks=seq(-0.5,0.5,.1)) +
    labs(x = "Related Yes (0.5) vs No (-0.5)", y = "Mean 'and' Duration (S)", title = "3+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

highest_syl_plot_RY = ggplot(Data_useable_peopleAB_tibble_longestRY, aes(x = related_yes, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(-.5,0.5),breaks=seq(-0.5,0.5,.1)) +
    labs(x = "Related Yes (0.5) vs No (-0.5)", y = "Mean 'and' Duration (S)", title = "2+ Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

shortest_syl_plot_RY = ggplot(Data_useable_peopleAB_tibble_shortestRY, aes(x = related_yes, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  scale_x_continuous(limits = c(-.5,0.5),breaks=seq(-0.5,0.5,.1)) +
    labs(x = "Related Yes (0.5) vs No (-0.5)", y = "Mean 'and' Duration (S)", title = "1-2 Syllable Words")  +
  theme(axis.text = element_text(size = rel(2), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

lower_syl_plot_RY
highest_syl_plot_RY
med_syl_plot_RY
higher_syl_plot_RY
shortest_syl_plot_RY

png(filename = "1 vs 2+ syllables RYES.png",
    width = 18, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(lower_syl_plot_RY,highest_syl_plot_RY,ncol=2)
dev.off()
```

PMI by item order interaction plots for durnp2
```{r}
library(tidyverse)
library(dplyr)
Data_useable_peopleAB$Anchor <- as.factor(Data_useable_peopleAB$Anchor)
Data_useable_peopleAB$SecondThing <- as.factor(Data_useable_peopleAB$SecondThing)
Data_useable_peopleAB$Nsyl_P2 <- as.numeric(Data_useable_peopleAB$Nsyl_P2)
Data_useable_peopleAB_tibble <- as_tibble(Data_useable_peopleAB)

Data_useable_peopleAB_tibblePMIIONP2 <- Data_useable_peopleAB_tibble %>% group_by(Anchor,item_order, PMI) %>% dplyr::summarise(Mean_DURAND = mean(DUR_AND))

Data_useable_peopleAB_tibble_AnchorFirstPMI <- Data_useable_peopleAB_tibblePMIIONP2 %>% filter(item_order == 0.5) 
Data_useable_peopleAB_tibble_ItemFirstPMI <- Data_useable_peopleAB_tibblePMIIONP2 %>% filter(item_order == - 0.5)  

AnchorFirst_plot_PMI = ggplot(Data_useable_peopleAB_tibble_AnchorFirstPMI, aes(x = PMI, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5,5.5),breaks=seq(0.5,5.5,0.5)) +
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
    labs(x = "PMI", y = "Mean 'and' Duration (S)", title = "Anchor First")  +
  theme(axis.text = element_text(size = rel(1.5), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))

ItemFirst_plot_PMI = ggplot(Data_useable_peopleAB_tibble_ItemFirstPMI, aes(x = PMI, y = Mean_DURAND)) +
  geom_smooth(method = lm, se = TRUE, color = "black", fill = "gray") +
  geom_point(size = 3) +
  theme_classic() + 
  scale_x_continuous(limits = c(0.5,5.5),breaks=seq(0.5,5.5,0.5)) +
  scale_y_continuous(limits = c(0,0.8),breaks=seq(0,0.8,0.1)) +
  labs(x = "PMI", y = "Mean 'and' Duration (S)", title = "Other Person First")  +
  theme(axis.text = element_text(size = rel(1.5), color = "black"),
        axis.title = element_text(size = rel(2), color = "black"),
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0)), 
        axis.title.x = element_text(margin = margin(t = 10, r = 0, b = 0, l = 0)),
        plot.title = element_text(size = rel(3.2), hjust = 0.5, margin = margin(t = 10, r = 0, b = 30, l = 0)))


png(filename = "PMI And item order interaciton.png",
    width = 18, height = 6, units = "in", res = 100)
gridExtra::grid.arrange(AnchorFirst_plot_PMI,ItemFirst_plot_PMI, ncol=2)
dev.off()
AnchorFirst_plot_PMI
ItemFirst_plot_PMI
```